### 2019-07-06 draft.tex
Initial Overleaf Import

\documentclass[12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Force pdflatex processing even with "$ latex" (required by arXiv)
\pdfoutput=1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage[usenames,dvipsnames,svgnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.1,0.3} % dark blue
\definecolor{darkgreen}{rgb}{0,0.65,0}
\definecolor{dblue4}{rgb}{0.06,0.31,0.55} % DodgerBlue4
\definecolor{nicered}{rgb}{0.7,0.1,0.1}
\definecolor{nicegreen}{rgb}{0.1,0.5,0.1}

\usepackage[numbers,sort&compress]{natbib}
%\usepackage{cite}

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{siunitx} 
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{dsfont}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

\usepackage{xcolor}
\usepackage[colorlinks=true,citecolor= nicegreen,linkcolor=nicered]{hyperref}

\usepackage{verbatim} 
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{cancel}

\usepackage[colorinlistoftodos]{todonotes}

\usepackage{comment}
\includecomment{details}
\specialcomment{details}
{\begingroup}{\endgroup}
\excludecomment{details}
%\PreviewEnvironment{details}
%%%%%%
%Custom definitions
\usepackage{tikz}
\newcommand{\ReportNumbers}[1]{%
\begin{tikzpicture}[overlay, remember picture]
\path (current page.north east) ++(-1,-1) node[below left] {#1};
\end{tikzpicture}
}
%%%%%%%%%%%%%%%TITLE PAGE

\title{Dirac neutrino mass generation from Majorana messenger}

\author{First Author\footnote{\href{mailto:first@author}{first@author}},
Second Author\footnote{\href{mailto:second@author}{second@author}}\\
\textit{\small  First Institute}\\
[4mm]
Third Author\footnote{\href{mailto:third@author }{third@author}}\\
\textit{\small Second Institute}
}
\date{\small Month NN, YYYY}
\begin{document}
%\maketitle
\ReportNumbers{XXX-XXX}

\begin{abstract}

We propose two Higgs doublets model based on the scotogenic model. In this model neutrino masses are radiative and we assume that neutrinos are Dirac fermion. Viable candidates for dark matter are the mediators in the loop. In addition, we propose that the fermionic mediator in the loop be Majorana fermion. This model is restricted by observables of neutrino physics,  lepton flavor violation and cosmological constrain in the number of relativistic degrees of freedom for neutrinos. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$..
\end{abstract}

\section{Introduction}
\label{sec:intro}

The standard model (SM) does not explain the neutrinos mass predicted by the neutrino oscillation experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}. From neutrino oscillation experiments, we know that at least two neutrinos must be massive and their respective mixing angles~\cite{deSalas:2017kay}. The experiments still do not determine if the neutrinos are Dirac or Majorana particles, since the double beta decays are not yet conclusive~\cite{Arnold:2016bed, Albert:2017owj, Alduino:2017ehq, Aalseth:2017btx, Agostini:2018tnm, KamLAND-Zen:2016pfg}.

In the SM all fermions acquire masses through a Dirac term, it is natural to believe that neutrinos acquire masses in this way, so there are some studies that develop this hypothesis~\cite{Branco:1978bz}. If the neutrinos are  Dirac, this establishes a physics beyond SM (BSM), this predicts the existence of at least two right-handed neutrinos. If neutrino mass is generated at tree level, establishes that Yukawas must be very small ($\lesssim 10^{-10}$) to explain tiny neutrino masses~\cite{deSalas:2017kay}. So it is preferred to generate the masses through mechanisms that develop in a loop~\cite{Branco:1978bz, Zee:1980ai, Ma:2006km}.

In some models to forbidden terms of Dirac at tree level and Majorana terms, discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}. In recent works, using symmetry ($B-L$) to forbid these terms without resorting to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}. In these cases, it is necessary to introduce new scalars and new dirac or vector-like fermions, that are used for to close the loop.

Another evidence that SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM). The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}. We will make use of the scotogenic model~\cite{Ma:2006km}. In scotogenic model the neutrino masses and the DM have common explanation. The mass of the neutrinos is generated to one-loop, where the mediators in the loop are viable candidates for DM.

In this work we propose a model with Dirac neutrinos at one-loop, in which the mediators are Majorana fermion and one singlet scalar and one doublet scalar. This mediators can to be dark matter candidates. Additionally, for generated neutrino mass is necessary to add a second Higgs doublet. The rest of the paper is organized as follows. In the next section we present the model and the particle content. In the section~\ref{sec:ScaMassSpect} we study the scale mass spectrum after spontaneous symmetry breaking. In section~\ref{sec:Neutrinos} we present the mechanism that generates the neutrino masses. In section~\ref{sec:LFV} we show the experimental lepton flavor violation (LFV) constrains. Finally, in the section~\ref{sec:DM} we present the viable DM candidates.

\section{The model}
\label{sec:Model}
As a preliminary model, we propose a model that includes an additional Higgs doublet with $ Y = -1/2 $. The two doublets are coupling differently to the fermions, the first doublet is coupled to quarks up-type and the charged leptons, while the second doublet is coupled to down-type quarks. To forbid another terms, we used a $U(1)^{\prime}$ symmetry. This model is known as two Higgs doublets model type II (2HDM-II)~\cite{Davidson:2005cw}. Also, these symmetry allows us to forbid Dirac mass terms at tree level. Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$. The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the Yukawa interactions. In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.

The most general Yukawa Lagrangian is:
%
\begin{align*}
\label{Eq:LagY}
    \mathcal{L} \subset& -[ 
    h^{a}_{i} \overline{L_{i}} \psi_{a} \widetilde{\eta}  +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S^{*} + h.c.] \\
    &- \mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma)\,,
\end{align*}
%
where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{*}$ and $\mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma)$ is the scalar potential. $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
%
\begin{table}
  \centering
  \begin{tabular}{|l|l|l|}
    \hline  
    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
    $H_{d} $  & $(2,-1/2)$ &  2 \\
    $H_{u} $  & $(2, 1/2)$ &  0 \\
    $\eta$ & $(2,1/2)$ & $-1$ \\
    $S$ & $(1,0)$ & $-2$ \\
    $\sigma$ & $(1,0)$ & $-3$ \\
    \hline
    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $-2$ \\
    \hline
    $L_i$  & $(2,-1/2)$ & $0$ \\
    $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $4$\\
    $\overline{\nu_{R_k}}$ & $(1,0)$ & $-5$\\
    $\psi_{i}$  & $(1,0)$ & $-1$ \\\hline
  \end{tabular}
  \caption{Scalars and left-handed fermions with their respective charges.}
  \label{tab:partcont}
\end{table}
%

The most general gauge invariant scalar potential for this model is
%
\begin{align*}
    \mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma) = & \mathcal{V}(H_{u}) + \mathcal{V}(H_{d}) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
    &+ \lambda_{1} (H^{\dagger}_{u} H_{u}) (H^{\dagger}_{d} H_{d}) + \lambda_{2} (H^{\dagger}_{u} H_{d}) (H^{\dagger}_{d} H_{u}) + \lambda_{3} (H_{u}^{\dagger} H_{u} ) (S^{*} S) + \lambda_{4} (H_{u}^{\dagger} H_{u} ) (\sigma^{*} \sigma ) \\
    &+ \lambda_{5} (H_{u}^{\dagger} H_{u} ) (\eta^{\dagger} \eta ) + \lambda_{6} (H_{d}^{\dagger} H_{d} ) (S^{*} S) + \lambda_{7} (H_{d}^{\dagger} H_{d} ) (\sigma^{*} \sigma ) + \lambda_{8} (H_{d}^{\dagger} H_{d} ) (\eta^{\dagger} \eta )  \\
    &+ \lambda_{9} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{10} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{12} (\eta^{\dagger} H_{u} ) (H^{\dagger}_{u} \eta ) \\
    &+ \lambda_{13} (\eta^{\dagger} H_{d} ) (H^{\dagger}_{d} \eta ) + (\mu \epsilon_{a b} H_{d}^{a} \eta^{b} \sigma + \mu_{1} \widetilde{H^{\dagger}_{d}} H_{u} S + \text{h.c.})\,,
\end{align*}
%
where $\mathcal{V}(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$. We consider that the parameters are real, since we are not going to deal with the CP violation~\cite{Abe:2016sqa}.

\section{Scalar mass spectrum}
\label{sec:ScaMassSpect}

 After spontaneous symmetry breaking, both Higgs doublet and scalar $S$ can to acquire vev's
%
\begin{align*}
    H_{u} =& \begin{pmatrix}0 \\ \frac{1}{\sqrt{2}} (h+\upsilon_{1}) \end{pmatrix} \,,
    &H_{d} =& \begin{pmatrix}\frac{1}{\sqrt{2}} (H+\upsilon_{2}+iA_{0}) \\ h^{-} \end{pmatrix} \,, &S =& \frac{1}{\sqrt{2}} (\phi+\upsilon_{s})
    &\eta =& \begin{pmatrix}\eta^{+} \\ \eta^{0} \end{pmatrix} \,,
\end{align*}
%
with $\eta^{0} = (\eta_{1}^{0}+i \eta_{2}^{0})/\sqrt{2}$ and $\sigma = ({\sigma}_{1}+i {\sigma}_{2})/\sqrt{2}$ and $\langle  H_{i} \rangle = \upsilon_{i}$ with $\upsilon=\sqrt{\upsilon_{1}^2+\upsilon_{2}^2} \simeq 246$\,GeV. It's possible to parameterize the ratio of these vev's as $\tan \beta = \upsilon_{2}/\upsilon_{1}$.

With the minimum of the scalar potential it is possible to write $\mu_{H_{u}}^{2}$,$\mu_{H_{d}}^{2}$ and $\mu^{2}_{s}$ in terms of the other parameters the following way
%
\begin{align*}
    \mu^{2}_{H_{u}} =& -\frac{\upsilon^{2}}{2}\left[ 2 \lambda_{H_{u}} c^{2}_{\beta} - 2 t^{2}_{\beta} \left(\frac{\mu^{2}_{H_{d}}}{\upsilon^{2}}+\lambda_{H_{d}} s^{2}_{\beta} \right) + \left( \lambda_{3} - \lambda_{6} t^{2}_{\beta} \right) \frac{\upsilon^{2}_{s}}{\upsilon^{2}} \right]\,, \\
    \mu_{1} =& -\frac{\upsilon^{2}}{\sqrt{2}} \left[ \left( \frac{2\mu^{2}_{H_{d}}}{\upsilon_{s}} + \lambda_{6} \upsilon_{s} \right) \frac{s_{\beta}}{\upsilon_{1} \upsilon} + \left( (\lambda_{1}+\lambda_{2})c^{2}_{\beta} + 2 \lambda_{H_{d}} s^{2}_{\beta} \right) \frac{t_{\beta}}{\upsilon_{s}} \right]\,, \\
   \mu^{2}_{s} =& -\frac{\upsilon^{4}}{2 \upsilon^{2}_{s}} \left[ -2s^{2}_{\beta} \left( \lambda_{H_{d}} s^{2}_{\beta} + \frac{\mu^{2}_{H_{d}}}{\upsilon^{2}_{s}}\right) + \left( \frac{\lambda_{3}}{\upsilon^{2}} - (\lambda_{1}+\lambda_{2})s^{2}_{\beta} \right) c^{2}_{\beta} + 2 \lambda_{6} \frac{\upsilon^{4}_{s}}{\upsilon^{4}} \right]\,,
\end{align*}
%
where $t_{\beta} = \tan \beta$, $c_{\beta} = \cos \beta$ and $s_{\beta} = \sin \beta$. This allows to reduce the number of free parameters.

Of the original sixteen scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G^{0}$ and $G^{\prime}$). There are two physical neutral CP-even Higgs state ($H$ and $h$, where $m_{H} \geq m_{h}$), one scalar state ($\phi$), one physical CP-odd Higgs scalar ($A^{0}$), two CP-even scalar state ($\sigma_{1}$ and $\eta^{0}_{1}$), two CP-odd scalar state ($\sigma_{2}$ and $\eta^{0}_{2}$), one charged scalar pairs ($\eta^{\pm}$) and one charged Higgs pairs ($h^{\pm}$). The mass spectrum for the scalar sector is given by
\begin{align*}
    m_{h^{\pm}}^{2} &= \mu^{2}_{H_{d}} + \frac{1}{2}(\lambda_{1} \upsilon^{2}_{1} + 2\lambda_{H_{d}} \upsilon^{2}_{2} + \lambda_{6} \upsilon^{2}_{s})\,, \\
    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{5} \upsilon^{2}_{1} + \lambda_{8} \upsilon^{2}_{2} + \lambda_{10} \upsilon^{2}_{s} )\,, \\
    m_{A^{0}}^{2} &= m_{h^{\pm}}^{2} + \frac{1}{2} \lambda_{2} \upsilon^{2}_{1} \,,
\end{align*}
%
note that the two charged scalars do not mix among themselves. The neutral mass eigenstate are defined as
%
\begin{align*}
    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(1,2)} \\ \eta_{(1,2)} \end{pmatrix} \,,
\end{align*}
%
where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{4} \upsilon^{2}_{1} + \lambda_{7} \upsilon^{2}_{2} + \lambda_{9} \upsilon^{2}_{s})$\,,
$b = \mu^{2}_{\eta^{\pm}} + \frac{1}{2}(\lambda_{12} \upsilon^{2}_{1} + \lambda_{13} \upsilon^{2}_{2})$ and $c = \mu \upsilon_{2}/\sqrt{2}$\,. The corresponding mass eigenvalues are
\begin{align*}
    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c} \right)\,, \\
     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c} \right)\,,
\end{align*}

\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Figures/Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generate to one loop level, which is shown in fig(\ref{fig:zee}). The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\sqrt{2}\mu \upsilon_{2}}{64 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i}^{a} M_{\psi_{a}}y_{j}^{a}}{m_{\chi_{R2}}^{2}-m_{\chi_{R1}}^{2}} \left[ F\left( \frac{m_{\chi_{R2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is loop function, $M_{\psi_{a}}$ is the fermión mass  and $\chi_{R_(1,2)}$ are the two CP-even mass eigenstate and $\chi_{I_{(1,2)}}$ are two CP-odd mass eigenstate.To obtain neutrino masses it is necessary that $\mu \neq 0$. In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large. Another possibility is small values of $\mu$, this suppress the value of the neutrino masses. The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h^{a}_{i} y^{b}_{j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one fermion $\psi$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}. In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).

For the Dirac neutrinos the mass matrices are diagonalized by
\begin{align}
(U^{(\nu)}_R)^{\dagger} M_{\nu_{D}} U^{(\nu)}_L = M_{\nu_{D}}^{\text{diag}} = \text{diag}(m1, m2, m3)\,,
\end{align}
where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
\begin{align}
U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
\end{align}
If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstate, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$. Therefore, we can to express the Dirac neutrino mass matrix following way
\begin{align}
(M_{\nu_{D}})_{ij} = (U_{\text{PMNS}})_{ij} (M_{\nu_{D}}^{\text{diag}})_{jj}\,,
\end{align}
where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
\begin{align}
U_{\text{PMNS}} = \begin{pmatrix}
    1 & 0		& 0 \\
    0 & c_{23}  & s_{23} \\
    0 & -s_{23} & c_{23}
\end{pmatrix}
\begin{pmatrix}
    c_{13}  &  0 & s_{13}e^{-i\delta} \\
    0 		&  1 & 0 \\
    -s_{13}e^{i\delta} &  0 & c_{13}
\end{pmatrix}
\begin{pmatrix}
    c_{12}  & s_{12} & 0 \\
    -s_{12} & c_{12} & 0 \\
    0		& 0		 & 1
\end{pmatrix}\,,
\end{align}
where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles.

\section{Lepton flavor violation}
\label{sec:LFV}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/LFV.pdf}
\caption{Feynman diagram for process $l^{-}_{i} \to l^{-}_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%
The new Yukawa interactions in Eq~\eqref{Eq:LagY} in our model introduce processes that violate the leptonic flavor in the charged sector (CLFV). These CLFV processes are induced at one loop level, as shown in the figure~\ref{fig:LFV}. In this case, the $\psi_{a} \widetilde{\eta}^{\dagger} L_{i}$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.

The most common search for CLFV focuses on the $l^{-}_{i} \to l^{-}_{j} \gamma$ process. This process is described by the effective Lagrangian
%
\begin{align}
    \mathcal{L} = \frac{\mu_{m}^{\alpha \beta}}{2} l^{-}_{\beta} \sigma^{\mu \nu} l^{-}_{\alpha} F_{\mu \nu}
\end{align}
%
where $\mu_{m}^{\alpha \beta}$ is a transition magnetic moment~\cite{Toma:2013zsa}.
The decay rate is given by~\cite{Lavoura:2003xp}
%
\begin{align}
 \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h^{\alpha}_{i} m_{i} h^{\alpha}_{j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
\end{align}
%
where $t_{\alpha} = M^{2}_{\psi_{\alpha}}/M^{2}_{\eta^{-}}$ and
%
\begin{align}
    K(t_{\alpha}) = \frac{2t_{\alpha}^{2}+5t_{\alpha}-1}{12(t_{\alpha}-1)^{3}} - \frac{t_{\alpha}^{2}\log t_{\alpha}}{2(t_{\alpha}-1)^{4}}\,.
\end{align}
%
If we assume that $t_{\alpha} \to 0$, $t_{\alpha} \to 1$ and $t_{\alpha} \to \infty$, we have that $K(t_{\alpha}) = 1/12$, $K(t_{\alpha}) = 1/24$ and $K(t_{\alpha}) = 1/(6t)$, respectively.

For $i \neq j$ we have CLFV processes. These processes are severely restricted by the current bounds , which set limits to the Yukawas. The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$. These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.3 \times 10^{-13} $~\cite{Adam:2013mnn}, Br$(\tau \to e\gamma) $\textless$ 3.3 \times 10^{-8}$ and Br$(\tau \to~\mu\gamma) $\textless$ 4.4 \times 10^{-8}$~\cite{Aubert:2009ag, Bona:2007qt, Miyazaki:2012mx}.

For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment. In the case of the anomalous muon magnetic dipole moment, the experimental measurements do not agree with the values predicted by the SM~\cite{Lindner:2016bgg}. This can be a proof of the veracity of the model, in addition to giving restrictions on the Yukawas.

\section{Dark matter}
\label{sec:DM}
Depending on the the new particles mass hierarchy (scalars and fermions charged odd under $U(1)^{\prime}$), it is possible to have two candidates for DM. The first DM candidate is the lightest majorana fermion (assuming that $\psi_{1} < \psi_{2} < \psi_{3}$). The second candidate is scalar DM. The scalar that assumes the role of DM depends on which is the lightest scalar particle charged odd under $U(1)^{\prime}$. In this model the scalar DM can be the neutral component of the scalar doublet $\eta^{0}$ or the scalar singlet $\sigma$.

\subsection{Fermionic dark matter}
In the case that the mass of the lightest fermion $\psi$ is smaller than the mass of the scalars, the DM will be fermionic. For this DM it is possible to have the following observable decay of the scalar $\eta^{\pm} \to l^{\pm} \psi_{1}$, therefore, the other fermions decay as $ \psi \to l^{\pm} l^{\mp} \psi_{1}$ and $\psi \to l^{\pm} l^{\mp} \psi_{1,2} $, through $\eta^{\pm}$. The relic density of DM can be controlled by annihilation $\psi_{1} \psi_{1} \to l _{\alpha} \overline{l}_{\beta} $, via Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted under LFV and neutrino masses. But, Yukawa couplings $y^{a}_{j}$ is free.

Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa links and this particle does not interact with gluons and quarks, this model has no direct detection restrictions for DM. In the case where the mass of the other fermions and scalars is nearly degenerated to $\psi_{1} $, the processes of coaniquilación are relevant in relic density~\cite{Klasen:2013jpa}.

\subsection{Scalar dark matter}
For scalar DM we have that the lightest scalar charged odd under $U(1)^{\prime}$ must have a mass smaller than the lightest $\psi$ fermion. Contrary to fermionic DM, scalar DM has additional interactions to Yukawa couplings (scalar and gauge interactions), which can be used to control relic density.

If the lightest scale is the neutral part of the scalar doublet, we will have that the DM will be similar to the model of the inert doublet~\cite{Honorez:2010re}. For the inert doublet model there are two mass regions for DM which can to reproduce adequately the relic density ($50$GeV \textless $m_{DM}$ \textless $70$GeV and $535$GeV \textless $m_{DM}$ \textless $20$TeV)~\cite{Garcia-Cely:2015khw}. In recent studies, these two regions are connected through use of a second doublet~\cite{Borah:2019aeq}. How we have in the model the Yukawa coupling, the decay $\psi_{i} \to l^{\pm} \eta^{\mp}$ is possible. In addition, decay is given via scalar interactions $\eta^{\pm} \to \eta^{0} + {W^{\pm}}$, where $W^{\pm}$ can be real or virtual and decay to leptons or quarks.

Now, if the lightest scale is the scalar singlet, the DM will be similar to the model in Ref.~\cite{Athron:2017kgt}. The mass range for the scalar singlet that produces the adequate relic density is between approximately the Higgs mass and about $300$GeV and masses above $1$TeV. For this model, the term in the Lagrangian $\sigma^{2} H^{2}_{i}$ is known as the \textquotedblleft Higgs portal\textquotedblright. This term generates interesting phenomenological consequences. Such as, thermal production of DM in the early universe~\cite{Yaguna:2008hd}, direct detection and $h \to \sigma \sigma$~\cite{Mambrini:2011ik}. In addition, this model has important contributions to cosmology, in phenomena such as inflation~\cite{Lerner:2009xg} and baryogenesis~\cite{Cline:2012hg}.

\section{Cosmological constrain}
\begin{comment}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/Tdec.pdf}
\includegraphics[scale=0.6]{Figures/Delta_Neff1.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:Neff}
\end{figure}
%
\end{comment}

The existence of three new right neutrinos in nature contribute to the total energy density of the universe. These new contributions can modify the cosmological observables in the CMB (cosmic microwave background). These new neutrinos contribute to the existence of dark radiation, which affects the expansion processes of the universe, which affects the number of relativistic degrees of freedom for neutrinos.

In the case of our models, this new gauge symmetry introduces a new gauge boson that mediates the interaction of the right neutrinos and the SM. This allows the right neutrinos to thermally modify the relativistic degrees of freedom, this contributions are given by~\cite{Anchordoqui:2012qu, Anchordoqui:2011nh}
%
\begin{align*}
    \Delta N_{eff} = N_{eff} - N^{SM}_{eff} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{dec})}{g(T^{\nu_{R}}_{dec})} \right)^{4}
\end{align*}
%
where $ g(T) $ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}. The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{dec} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ dec}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}. The rate of interaction of the right neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
%
\begin{align*}
    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \,, \\
    &= \frac{g^{2}_{\nu_R}}{n_{\nu_R}(T)} \int \frac{d^{3} p}{(2 \pi)^{3}} f_{\nu_R}(p) \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k) \sigma_{f}(s) \upsilon\,,
\end{align*}
%
where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distributión, $g_{\nu_R} = 2$ is spin number, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, where $p$ and $k$ are the momenta of the particle and $\theta$, the angle between them and the number density of right-handed neutrinos is given by
\begin{align*}
n_{\nu_R}(T) = g_{\nu_R} \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k)\,.
\end{align*}

The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{dec} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
%
\begin{align*}
    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
\end{align*}
%
where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e. $N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new simmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson. Solving the integrals with this last cross section we obtain that the interaction rate is given by
%
\begin{align*}
    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
\end{align*}
%
%
\begin{figure}
\centering
\includegraphics[scale=0.8]{Figures/DeltaNeff.pdf}
\caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$. In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{eff}$) in function of $M_{z^{\prime}}/g^{\prime}$. The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}. The region shaded in violet shows the bound from LEP  LEP~\cite{Alioli:2017nzr}.}
\label{fig:Neff}
\end{figure}
%
where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature T. To estimate the contribution to relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{dec}$). The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
%
\begin{align*}
\Gamma(T^{\nu_R}_{dec}) = H(T^{\nu_R}_{dec})\,, 
\end{align*}
%
where the Hubble expansion parameter is
%
\begin{align*}
    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
\end{align*}
%
where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom. By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{dec} $ by a root finding method, it is possible to calculate $\Delta N_{eff}$.

The results of $T^{\nu_R}_{dec}$ and $\Delta N_{eff}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in Fig~\ref{fig:Neff}. We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa. The bound that come from Planck~\cite{ghanim:2018eyx}

\includegraphics[scale=0.9]{Figures/DeltaNeff.pdf}

is stronger than the bound of LEP~\cite{Alioli:2017nzr}. For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$.

\appendix

%\bibliographystyle{h-physrev4}
%\bibliographystyle{JHEP-2}
%\bibliographystyle{JHEP}
\bibliographystyle{apsrev4-1long}
%\bibliographystyle{apsrev4-1longdoi}
\bibliography{susy}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "draft"
%%% ispell-local-dictionary: "american"
%%% End: 
The cross section is given in [], in the case with heavy mediator $T^{\nu_R}_{dec} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is

### 2019-07-07 draft.tex
Updates from Overleaf

@@
 \begin{document}
-%\maketitle
+\maketitle
 \ReportNumbers{XXX-XXX}
@@
 
-We propose two Higgs doublets model based on the scotogenic model.
-In this model neutrino masses are radiative and we assume that neutrinos are Dirac fermion.
-Viable candidates for dark matter are the mediators in the loop.
-In addition, we propose that the fermionic mediator in the loop be Majorana fermion.
-This model is restricted by observables of neutrino physics,  lepton flavor violation and cosmological constrain in the number of relativistic degrees of freedom for neutrinos.
-Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$..
+We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop.
+This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including
+the effective number light neutrinos $N_{\text{eff}}$ . Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
 \end{abstract}
@@
 \label{sec:intro}
+%Dirac vs Majorana (From previous paper: must be rephrased
+The interpretation of neutrino experimental data in terms of neutrino
+oscillations is compatible with both Majorana or Dirac neutrino
+masses \cite{Tanabashi:2018oca}. The former possibility  has received the most attention but, given the lack of signals in neutrinoless double beta decay experiments
+\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed}, the latter cannot be dismissed.
+If neutrinos are Dirac particles, the Standard Model (SM) particle content must be extended with right-handed neutrinos, which can increase the number the effective number light neutrinos, $N_{\text{eff}}$, until 6.
+To give small masses to at least two Majorana or Dirac neutrinos, as required to explain the neutrino oscillation experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually invoked.
+
+and some symmetry must be imposed to prevent their Majorana mass terms.
+% Tree-level see-saw with fermionic mediators: Dirac for Dirac, Majorana-Majorana
+% One-loop level: Majorana-Majorana, Dirac-Dirac, Majorana-Dirac. Simplest model with Dirac-Majorana still missing
+% At one-loop Dark Matter is predicted in model-dependent ways. In this case...
 
@@
 \centering
-\includegraphics[scale=0.75]{Figures/Neutrino_Loop.pdf}
+\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
 \caption{One-loop generation of Dirac neutrino mass}
@@
 \centering
-\includegraphics[scale=0.6]{Figures/LFV.pdf}
+\includegraphics[scale=0.6]{LFV.pdf}
 \caption{Feynman diagram for process $l^{-}_{i} \to l^{-}_{j} \gamma$}
@@
 \centering
-\includegraphics[scale=0.6]{Figures/Tdec.pdf}
-\includegraphics[scale=0.6]{Figures/Delta_Neff1.pdf}
+\includegraphics[scale=0.6]{Tdec.pdf}
+\includegraphics[scale=0.6]{Delta_Neff1.pdf}
 \caption{One-loop generation of Dirac neutrino mass}
@@
 \centering
-\includegraphics[scale=0.8]{Figures/DeltaNeff.pdf}
+\includegraphics[scale=0.8]{DeltaNeff.pdf}
 \caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$.
@@
 
-\includegraphics[scale=0.9]{Figures/DeltaNeff.pdf}
+\includegraphics[scale=0.9]{DeltaNeff.pdf}
 

### 2019-07-07 draft.tex
ir

@@
 The interpretation of neutrino experimental data in terms of neutrino
-oscillations is compatible with both Majorana or Dirac neutrino
-masses \cite{Tanabashi:2018oca}. The former possibility  has received the most attention but, given the lack of signals in neutrinoless double beta decay experiments
-\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed}, the latter cannot be dismissed.
-If neutrinos are Dirac particles, the Standard Model (SM) particle content must be extended with right-handed neutrinos, which can increase the number the effective number light neutrinos, $N_{\text{eff}}$, until 6.
-To give small masses to at least two Majorana or Dirac neutrinos, as required to explain the neutrino oscillation experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually invoked.
+oscillations is compatible with both Majorana or Dirac neutrino masses
+\cite{Tanabashi:2018oca}. The former possibility has received the most
+attention but, given the lack of signals in neutrinoless double beta
+decay experiments
+\cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
+the latter cannot be dismissed. If neutrinos are Dirac particles, the
+Standard Model (SM) particle content must be extended with
+right-handed neutrinos, which can increase the number the effective
+number light neutrinos, $N_{\text{eff}}$, until 6. To give small
+masses to at least two Majorana or Dirac neutrinos, as required to
+explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
+  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
+invoked.
 
-and some symmetry must be imposed to prevent their Majorana mass terms.
+Discussion: At three level seem to have that we can have also all Majorana mediators for Dirac neutrinos. See plot:
+
+\includegraphics[scale=0.5]{tl}
+
 % Tree-level see-saw with fermionic mediators: Dirac for Dirac, Majorana-Majorana

### 2019-07-09 draft.tex
Updates from Overleaf

@@
 invoked.
+For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{} or light Dirac neutrinos with heavy Dirac mediators~\cite{} (see provisional figure below).
+The radiative type-I seesaw includes these both possibilities:~\cite{} and \cite{}, but now it is possible also to have also Majorana fermions with Dirac mediators.
+In this
+work we want to explore the possibility to build a simple model with
+Dirac masses and Majorana mediators.
 
-Discussion: At three level seem to have that we can have also all Majorana mediators for Dirac neutrinos. See plot:
+%TO BE DELETED
+Preliminary discussion: At three level a Dirac seesaw with Majorana mediators automatically allows for Majorana masses, as illustrated in the provisional plot: neutrinos. See plot:
 
-\includegraphics[scale=0.5]{tl}
+\includegraphics[scale=0.4]{tl}
 

### 2019-07-27 draft.tex
Updates from Overleaf

--- 2019-07-07 draft.tex
@@
 \label{sec:intro}
-%Dirac vs Majorana (From previous paper: must be rephrased
+
 The interpretation of neutrino experimental data in terms of neutrino
@@
 Standard Model (SM) particle content must be extended with
-right-handed neutrinos, which can increase the number the effective
-number light neutrinos, $N_{\text{eff}}$, until 6. To give small
+right-handed neutrinos, which can increase the effective
+number of light neutrinos, $N_{\text{eff}}$, until 6. 
+To be compatible with the current cosmological restrictions on
+$N_{\text{eff}}$, only the  ps w l therm
+To give small
 masses to at least two Majorana or Dirac neutrinos, as required to
@@
 invoked.
+For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia} or light Dirac neutrinos with heavy Dirac mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}.
+The radiative type-I seesaw includes both~\cite{} and~\cite{}, but now it is also possible to have light Majorana neutrinos with heavy  Dirac mediators~\cite{}.
+In this
+work we want to explore the possibility to build a simple model with Dirac neutrino
+masses and heavy  Majorana mediators. It is worth noticing that this idea have been already illustrated in
+an extension of the minimal supersymmetric standard model~\cite{Demir:2007dt} but without show any explicit solution.
 
-Discussion: At three level seem to have that we can have also all Majorana mediators for Dirac neutrinos. See plot:
-
-\includegraphics[scale=0.5]{tl}
-
-% Tree-level see-saw with fermionic mediators: Dirac for Dirac, Majorana-Majorana
-% One-loop level: Majorana-Majorana, Dirac-Dirac, Majorana-Dirac. Simplest model with Dirac-Majorana still missing
-% At one-loop Dark Matter is predicted in model-dependent ways. In this case...
-
-The standard model (SM) does not explain the neutrinos mass predicted by the neutrino oscillation experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}.
-From neutrino oscillation experiments, we know that at least two neutrinos must be massive and their respective mixing angles~\cite{deSalas:2017kay}.
-The experiments still do not determine if the neutrinos are Dirac or Majorana particles, since the double beta decays are not yet conclusive~\cite{Arnold:2016bed, Albert:2017owj, Alduino:2017ehq, Aalseth:2017btx, Agostini:2018tnm, KamLAND-Zen:2016pfg}.
-
-In the SM all fermions acquire masses through a Dirac term, it is natural to believe that neutrinos acquire masses in this way, so there are some studies that develop this hypothesis~\cite{Branco:1978bz}.
-If the neutrinos are  Dirac, this establishes a physics beyond SM (BSM), this predicts the existence of at least two right-handed neutrinos.
-If neutrino mass is generated at tree level, establishes that Yukawas must be very small ($\lesssim 10^{-10}$) to explain tiny neutrino masses~\cite{deSalas:2017kay}.
-So it is preferred to generate the masses through mechanisms that develop in a loop~\cite{Branco:1978bz, Zee:1980ai, Ma:2006km}.
-
-In some models to forbidden terms of Dirac at tree level and Majorana terms, discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
-In recent works, using symmetry ($B-L$) to forbid these terms without resorting to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
-In these cases, it is necessary to introduce new scalars and new dirac or vector-like fermions, that are used for to close the loop.
+In models for Dirac neutrinos with some explanation for the smallness of
+their masses, usually an adhoc discrete symmetry is invoked to forbid
+the SM induced terms of Dirac at tree level and Majorana terms,
+and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
+In recent works, using symmetry ($B-L$) to forbid these terms without resorting
+to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
+In these cases, it is necessary to introduce new scalars and new Dirac or 
+vector-like fermions, that are required to close the loop.
 
@@
 In scotogenic model the neutrino masses and the DM have common explanation.
-The mass of the neutrinos is generated to one-loop, where the mediators in the loop are viable candidates for DM.
+The neutrino masses are generated by one-loop effects, where the candidates for DM are mediators in the loop.
 
-In this work we propose a model with Dirac neutrinos at one-loop, in which the mediators are Majorana fermion and one singlet scalar and one doublet scalar.
-This mediators can to be dark matter candidates.
-Additionally, for generated neutrino mass is necessary to add a second Higgs doublet.
+In this work we propose a Dirac radiative type-I seesaw,
+with Majorana fermion of the mediators in the loop..
+This mediators can to be DM candidate.
 The rest of the paper is organized as follows.
 In the next section we present the model and the particle content.
-In the section~\ref{sec:ScaMassSpect} we study the scale mass spectrum after spontaneous symmetry breaking.
-In section~\ref{sec:Neutrinos} we present the mechanism that generates the neutrino masses.
-In section~\ref{sec:LFV} we show the experimental lepton flavor violation (LFV) constrains.
+In the section~\ref{sec:ScaMassSpect} we study the scalar mass spectrum after spontaneous symmetry breaking.
+In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
+In section~\ref{sec:LFV} we show the lepton flavor violation (LFV)experimental  constraints.
 Finally, in the section~\ref{sec:DM} we present the viable DM candidates.
@@
 As a preliminary model, we propose a model that includes an additional Higgs doublet with $ Y = -1/2 $.
-The two doublets are coupling differently to the fermions, the first doublet is coupled to quarks up-type and the charged leptons, while the second doublet is coupled to down-type quarks.
 To forbid another terms, we used a $U(1)^{\prime}$ symmetry.
-This model is known as two Higgs doublets model type II (2HDM-II)~\cite{Davidson:2005cw}.
+This model is known as two Higgs doublets model (2HDM)~\cite{Davidson:2005cw}.
 Also, these symmetry allows us to forbid Dirac mass terms at tree level.
@@
     \mathcal{L} \subset& -[ 
-    h^{a}_{i} \overline{L_{i}} \psi_{a} \widetilde{\eta}  +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S^{*} + h.c.] \\
-    &- \mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma)\,,
+    h^{a}_{i} \overline{L_{i}} \eta \psi_{a} +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S + \text{h.c}] \\
+    &- \mathcal{V}(H, H_{2}, S, \eta, \sigma)\,,
 \end{align*}
 %
-where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{*}$ and $\mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma)$ is the scalar potential.
+where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, H_{2}, S, \eta, \sigma)$ is the scalar potential.
 $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
@@
     Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
-    $H_{d} $  & $(2,-1/2)$ &  2 \\
-    $H_{u} $  & $(2, 1/2)$ &  0 \\
-    $\eta$ & $(2,1/2)$ & $-1$ \\
-    $S$ & $(1,0)$ & $-2$ \\
-    $\sigma$ & $(1,0)$ & $-3$ \\
+    $H $  & $(2, 1/2)$ &  0 \\
+    $\eta$ & $(2,1/2)$ & $1$ \\
+    $S$ & $(1,0)$ & $2$ \\
+    $\sigma$ & $(1,0)$ & $3$ \\
     \hline
@@
     $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
-    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $-2$ \\
+    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
     \hline
@@
 \begin{align*}
-    \mathcal{V}(H_{u}, H_{d}, S, \eta, \sigma) = & \mathcal{V}(H_{u}) + \mathcal{V}(H_{d}) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
-    &+ \lambda_{1} (H^{\dagger}_{u} H_{u}) (H^{\dagger}_{d} H_{d}) + \lambda_{2} (H^{\dagger}_{u} H_{d}) (H^{\dagger}_{d} H_{u}) + \lambda_{3} (H_{u}^{\dagger} H_{u} ) (S^{*} S) + \lambda_{4} (H_{u}^{\dagger} H_{u} ) (\sigma^{*} \sigma ) \\
-    &+ \lambda_{5} (H_{u}^{\dagger} H_{u} ) (\eta^{\dagger} \eta ) + \lambda_{6} (H_{d}^{\dagger} H_{d} ) (S^{*} S) + \lambda_{7} (H_{d}^{\dagger} H_{d} ) (\sigma^{*} \sigma ) + \lambda_{8} (H_{d}^{\dagger} H_{d} ) (\eta^{\dagger} \eta )  \\
-    &+ \lambda_{9} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{10} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{12} (\eta^{\dagger} H_{u} ) (H^{\dagger}_{u} \eta ) \\
-    &+ \lambda_{13} (\eta^{\dagger} H_{d} ) (H^{\dagger}_{d} \eta ) + (\mu \epsilon_{a b} H_{d}^{a} \eta^{b} \sigma + \mu_{1} \widetilde{H^{\dagger}_{d}} H_{u} S + \text{h.c.})\,,
+    \mathcal{V}(H, S, \eta, \sigma) = & \mathcal{V}(H) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
+    &+  \lambda_{3} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{4} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{5} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
+    &+ \lambda_{9} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{10} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{12} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
+    &+ (\mu \eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
 \end{align*}
@@
 \begin{align*}
-    H_{u} =& \begin{pmatrix}0 \\ \frac{1}{\sqrt{2}} (h+\upsilon_{1}) \end{pmatrix} \,,
-    &H_{d} =& \begin{pmatrix}\frac{1}{\sqrt{2}} (H+\upsilon_{2}+iA_{0}) \\ h^{-} \end{pmatrix} \,, &S =& \frac{1}{\sqrt{2}} (\phi+\upsilon_{s})
+    H =& \begin{pmatrix}0 \\ \frac{1}{\sqrt{2}} (h+\upsilon_{1}) \end{pmatrix} \,,
+    &H_{2} =& \begin{pmatrix}\frac{1}{\sqrt{2}} (H+\upsilon_{2}+iA_{0}) \\ h^{-} \end{pmatrix} \,, &S =& \frac{1}{\sqrt{2}} (\phi+\upsilon_{s})
     &\eta =& \begin{pmatrix}\eta^{+} \\ \eta^{0} \end{pmatrix} \,,
@@
 
-With the minimum of the scalar potential it is possible to write $\mu_{H_{u}}^{2}$,$\mu_{H_{d}}^{2}$ and $\mu^{2}_{s}$ in terms of the other parameters the following way
+With the minimum of the scalar potential it is possible to write $\mu_{H}^{2}$,$\mu_{H_{2}}^{2}$ and $\mu^{2}_{s}$ in terms of the other parameters the following way
 %
 \begin{align*}
-    \mu^{2}_{H_{u}} =& -\frac{\upsilon^{2}}{2}\left[ 2 \lambda_{H_{u}} c^{2}_{\beta} - 2 t^{2}_{\beta} \left(\frac{\mu^{2}_{H_{d}}}{\upsilon^{2}}+\lambda_{H_{d}} s^{2}_{\beta} \right) + \left( \lambda_{3} - \lambda_{6} t^{2}_{\beta} \right) \frac{\upsilon^{2}_{s}}{\upsilon^{2}} \right]\,, \\
-    \mu_{1} =& -\frac{\upsilon^{2}}{\sqrt{2}} \left[ \left( \frac{2\mu^{2}_{H_{d}}}{\upsilon_{s}} + \lambda_{6} \upsilon_{s} \right) \frac{s_{\beta}}{\upsilon_{1} \upsilon} + \left( (\lambda_{1}+\lambda_{2})c^{2}_{\beta} + 2 \lambda_{H_{d}} s^{2}_{\beta} \right) \frac{t_{\beta}}{\upsilon_{s}} \right]\,, \\
-   \mu^{2}_{s} =& -\frac{\upsilon^{4}}{2 \upsilon^{2}_{s}} \left[ -2s^{2}_{\beta} \left( \lambda_{H_{d}} s^{2}_{\beta} + \frac{\mu^{2}_{H_{d}}}{\upsilon^{2}_{s}}\right) + \left( \frac{\lambda_{3}}{\upsilon^{2}} - (\lambda_{1}+\lambda_{2})s^{2}_{\beta} \right) c^{2}_{\beta} + 2 \lambda_{6} \frac{\upsilon^{4}_{s}}{\upsilon^{4}} \right]\,,
+    \mu^{2}_{H} =& -\frac{\upsilon^{2}}{2}\left[ 2 \lambda_{H} c^{2}_{\beta} - 2 t^{2}_{\beta} \left(\frac{\mu^{2}_{H_{2}}}{\upsilon^{2}}+\lambda_{H_{2}} s^{2}_{\beta} \right) + \left( \lambda_{3} - \lambda_{6} t^{2}_{\beta} \right) \frac{\upsilon^{2}_{s}}{\upsilon^{2}} \right]\,, \\
+    \mu_{1} =& -\frac{\upsilon^{2}}{\sqrt{2}} \left[ \left( \frac{2\mu^{2}_{H_{2}}}{\upsilon_{s}} + \lambda_{6} \upsilon_{s} \right) \frac{s_{\beta}}{\upsilon_{1} \upsilon} + \left( (\lambda_{1}+\lambda_{2})c^{2}_{\beta} + 2 \lambda_{H_{2}} s^{2}_{\beta} \right) \frac{t_{\beta}}{\upsilon_{s}} \right]\,, \\
+   \mu^{2}_{s} =& -\frac{\upsilon^{4}}{2 \upsilon^{2}_{s}} \left[ -2s^{2}_{\beta} \left( \lambda_{H_{2}} s^{2}_{\beta} + \frac{\mu^{2}_{H_{2}}}{\upsilon^{2}_{s}}\right) + \left( \frac{\lambda_{3}}{\upsilon^{2}} - (\lambda_{1}+\lambda_{2})s^{2}_{\beta} \right) c^{2}_{\beta} + 2 \lambda_{6} \frac{\upsilon^{4}_{s}}{\upsilon^{4}} \right]\,,
 \end{align*}
@@
 \begin{align*}
-    m_{h^{\pm}}^{2} &= \mu^{2}_{H_{d}} + \frac{1}{2}(\lambda_{1} \upsilon^{2}_{1} + 2\lambda_{H_{d}} \upsilon^{2}_{2} + \lambda_{6} \upsilon^{2}_{s})\,, \\
+    m_{h^{\pm}}^{2} &= \mu^{2}_{H_{2}} + \frac{1}{2}(\lambda_{1} \upsilon^{2}_{1} + 2\lambda_{H_{2}} \upsilon^{2}_{2} + \lambda_{6} \upsilon^{2}_{s})\,, \\
     m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{5} \upsilon^{2}_{1} + \lambda_{8} \upsilon^{2}_{2} + \lambda_{10} \upsilon^{2}_{s} )\,, \\
@@
 \begin{align}
-(U^{(\nu)}_R)^{\dagger} M_{\nu_{D}} U^{(\nu)}_L = M_{\nu_{D}}^{\text{diag}} = \text{diag}(m1, m2, m3)\,,
+(U^{(\nu)}_R)^{\dagger} M_{\nu_{2}} U^{(\nu)}_L = M_{\nu_{2}}^{\text{diag}} = \text{diag}(m1, m2, m3)\,,
 \end{align}
@@
 \begin{align}
-(M_{\nu_{D}})_{ij} = (U_{\text{PMNS}})_{ij} (M_{\nu_{D}}^{\text{diag}})_{jj}\,,
+(M_{\nu_{2}})_{ij} = (U_{\text{PMNS}})_{ij} (M_{\nu_{2}}^{\text{diag}})_{jj}\,,
 \end{align}
@@
 
-\section{Cosmological constrain}
+\section{Cosmological constraints}
 \begin{comment}
@@
 \end{comment}
+
+%
+\begin{table}
+  \centering
+  \begin{tabular}{|l|l|c|c|}
+    \hline  
+    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)_{L}$& $Z_2$\\ \hline
+    $H $  & $(2, 1/2)$ &  0 &$+$\\
+    %$\widetilde{H_{2}}$  & $(2,1/2)$ &  $0$ &$-$\\
+    $\eta$ & $(2,1/2)$ & $1-\psi\to 5/2$ &$-$\\
+    $S$ & $(1,0)$ & $-2\psi\to 3$ &$+$\\
+    $\sigma$ & $(1,0)$ & $\nu+\psi=\eta=1-\psi\to 5/2$&$-$\\
+    \hline
+    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$& $+$\\
+    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$& $+$\\
+    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$& $+$\\
+    \hline
+    $L_i$  & $(2,-1/2)$ & $-1$& $+$\\
+    $\overline{e_{R_i}}$ & $(1,1)$ & $+1$ & $+$ \\
+    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $\nu\to 1-2\psi\to 4$&$+$\\
+    $\overline{\nu_{R_k}}$ & $(1,0)$ & $\nu_k$&$+$\\
+    $\psi_{i}$  & $(1,0)$ & $\psi\to -3/2$ &$-$\\\hline
+  \end{tabular}
+  \caption{Scalars and left-handed fermions with their respective charges. $Z_2$ to define THDM Type-II~\cite{1303.0168}}
+  \label{tab:partcont}
+\end{table}
+%
+
+The solution in Table~\ref{tab:partcont} is no anomaly free.
+To have $L=-1$ while keeping the same minimal set of scalars would require anomaly solutions with at least two pairs of the very same lepton charges, such that
+\begin{align}
+    2\psi+2\nu+\cdots=&3 \nonumber\\
+    2\psi^3+2\nu^3+\cdots=&3
+\end{align}
+If we introduce two additional left-handed fields $(\xi_i)^\dagger$,  with $U(1)_L$ $+3/2$, the anomalies cancel out.
+Moreover, we have both Dirac mass terms $(\Upsilon_i)^\dagger\psi_j$ and $ \Upsilon_i \Upsilon_j \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
+The lighter of them a would be dark matter particle.
 

### 2019-07-29 draft.tex
Updates from Overleaf

@@
 \label{sec:Model}
-As a preliminary model, we propose a model that includes an additional Higgs doublet with $ Y = -1/2 $.
-To forbid another terms, we used a $U(1)^{\prime}$ symmetry.
-This model is known as two Higgs doublets model (2HDM)~\cite{Davidson:2005cw}.
-Also, these symmetry allows us to forbid Dirac mass terms at tree level.
+As a preliminary model, we propose a model that includes an additional gauge symmetry $U(1)^{\prime}$.
+Where  gauge invariance is used to forbid Dirac and Majorana mass terms at tree level.
 Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$.
-The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the Yukawa interactions.
+The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the gauge invariance in Yukawa interactions.
 In this model the neutrinos are Dirac fermions.
@@
     h^{a}_{i} \overline{L_{i}} \eta \psi_{a} +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S + \text{h.c}] \\
-    &- \mathcal{V}(H, H_{2}, S, \eta, \sigma)\,,
+    &- \mathcal{V}(H, S, \eta, \sigma)\,,
 \end{align*}
 %
-where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, H_{2}, S, \eta, \sigma)$ is the scalar potential.
+where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, S, \eta, \sigma)$ is the scalar potential.
 $h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
@@
     \mathcal{V}(H, S, \eta, \sigma) = & \mathcal{V}(H) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
-    &+  \lambda_{3} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{4} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{5} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
-    &+ \lambda_{9} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{10} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{11} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{12} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
-    &+ (\mu \eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
+    &+  \lambda_{1} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
+    &+ \lambda_{4} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{5} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
+    &+ \mu (\eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
 \end{align*}

### 2019-07-29 draft.tex
sln

@@
 \begin{abstract}    
-
 We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop.
@@
 Standard Model (SM) particle content must be extended with
-right-handed neutrinos, which can increase the effective
-number of light neutrinos, $N_{\text{eff}}$, until 6. 
-To be compatible with the current cosmological restrictions on
-$N_{\text{eff}}$, only the  ps w l therm
-To give small
-masses to at least two Majorana or Dirac neutrinos, as required to
-explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
-  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
-invoked.
-For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia} or light Dirac neutrinos with heavy Dirac mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}.
-The radiative type-I seesaw includes both~\cite{} and~\cite{}, but now it is also possible to have light Majorana neutrinos with heavy  Dirac mediators~\cite{}.
-In this
-work we want to explore the possibility to build a simple model with Dirac neutrino
-masses and heavy  Majorana mediators. It is worth noticing that this idea have been already illustrated in
-an extension of the minimal supersymmetric standard model~\cite{Demir:2007dt} but without show any explicit solution.
+right-handed neutrinos, which can increase the effective number of
+light neutrinos, $N_{\text{eff}}$, until 6.  To be compatible with the
+current cosmological restrictions on $N_{\text{eff}}$, the interaction
+of the extra right-handed neutrinos with the primordial plasma must be
+highly suppressed.  To give small masses to at least two Majorana or
+Dirac neutrinos, as required to explain the neutrino oscillation
+experiments~\cite{Ahmad:2002jz, Fukuda:1998mi}, the seesaw mechanism
+with heavy fermions is usually invoked. For the tree-level type-I
+seesaw we can have either light Majorana neutrinos with heavy Majorana
+mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia}
+or light Dirac neutrinos with heavy Dirac
+mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}. The
+radiative type-I seesaw includes both~\cite{} possibilities~\cite{}, but now it
+is also possible to have light Majorana neutrinos with heavy Dirac
+mediators~\cite{}. In this work we want to explore the possibility to
+build a simple model with Dirac neutrino masses and heavy Majorana
+mediators. It is worth noticing that this idea have been already
+illustrated in an extension of the minimal supersymmetric standard
+model~\cite{Demir:2007dt} but without show any explicit solution.
 
 In models for Dirac neutrinos with some explanation for the smallness of
-their masses, usually an adhoc discrete symmetry is invoked to forbid
-the SM induced terms of Dirac at tree level and Majorana terms,
+their masses, usually  adhoc discrete symmetries are invoked to forbid
+tree level SM Dirac or Majorana mass terms,
 and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
@@
 
+% Checl also:
+$-2,6,-9,-3,7$
+
 The solution in Table~\ref{tab:partcont} is no anomaly free.

### 2019-08-01 draft.tex
hjj

--- 2019-07-29 draft.tex
@@
 \begin{abstract}    
-
-We propose a two-Higgs-doublet model (THDM) for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop.
+We propose a model for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop.
 This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including
-the effective number light neutrinos $N_{\text{eff}}$ . Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
+the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
 \end{abstract}
@@
 \label{sec:intro}
+%Dirac or Majorana
 
@@
 \cite{KamLAND-Zen:2016pfg,Agostini:2018tnm,Aalseth:2017btx,Alduino:2017ehq,Albert:2017owj,Arnold:2016bed},
-the latter cannot be dismissed. If neutrinos are Dirac particles, the
+the latter cannot be dismissed.
+%Dirac case
+If neutrinos are Dirac particles, the
 Standard Model (SM) particle content must be extended with
-right-handed neutrinos, which can increase the effective
-number of light neutrinos, $N_{\text{eff}}$, until 6. 
-To be compatible with the current cosmological restrictions on
-$N_{\text{eff}}$, only the  ps w l therm
-To give small
-masses to at least two Majorana or Dirac neutrinos, as required to
-explain the neutrino oscillation experiments~\cite{Ahmad:2002jz,
-  Fukuda:1998mi}, the seesaw mechanism with heavy fermions is usually
-invoked.
-For the tree-level type-I seesaw we can have either light Majorana neutrinos with heavy Majorana mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia} or light Dirac neutrinos with heavy Dirac mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}.
-The radiative type-I seesaw includes both~\cite{} and~\cite{}, but now it is also possible to have light Majorana neutrinos with heavy  Dirac mediators~\cite{}.
-In this
-work we want to explore the possibility to build a simple model with Dirac neutrino
-masses and heavy  Majorana mediators. It is worth noticing that this idea have been already illustrated in
-an extension of the minimal supersymmetric standard model~\cite{Demir:2007dt} but without show any explicit solution.
+right-handed neutrinos,
+%with cosmology implications
+which can increase the effective number of
+light neutrinos, $N_{\text{eff}}$, until 6. Therefore, to be compatible with the
+current cosmological restrictions on $N_{\text{eff}}$, the interactions
+of the extra right-handed neutrinos with the primordial plasma must be
+highly suppressed.
 
-In models for Dirac neutrinos with some explanation for the smallness of
-their masses, usually an adhoc discrete symmetry is invoked to forbid
-the SM induced terms of Dirac at tree level and Majorana terms,
-and discrete ad hoc symmetries are added~\cite{Han:2018zcn, Wang:2017mcy}.
-In recent works, using symmetry ($B-L$) to forbid these terms without resorting
-to discrete symmetries~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}.
-In these cases, it is necessary to introduce new scalars and new Dirac or 
-vector-like fermions, that are required to close the loop.
+%Smallness of neutrinos for both Dirac and Majorana
+On the other hand, To give small masses to at least two Majorana or
+Dirac neutrinos, as required to explain the neutrino oscillation
+experiments~\cite{Ahmad:2002jz, Fukuda:1998mi},
+%focus in seesaw type I
+the seesaw mechanism
+with heavy fermions is usually invoked.
+%tree-level case
+For the tree-level type-I
+seesaw we can have either light Majorana neutrinos with heavy Majorana
+mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia}
+or light Dirac neutrinos with heavy Dirac
+mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}.
+%one-loop case
+The
+radiative type-I seesaw includes both~\cite{} possibilities~\cite{},
+%new possibility in radiative case
+but now it is also possible to have light Majorana neutrinos with
 
-Another evidence that SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM).
+heavy Dirac mediators~\cite{}.
+%New in this work
+In this work we want to explore the
+possibility to build a simple Dirac radiative type-I seesaw  model with 
+heavy Majorana mediators.
+%Old idea but first realized here
+It is worth noticing that this idea have
+been already illustrated in an extension of the minimal supersymmetric
+standard model~\cite{Demir:2007dt} but without show any explicit
+solution.
+
+%Features of the new propossed solution
+In general, solutions for light Dirac neutrino masses require a continous symmetry to guarantee their Diracness.
+This symmetry is usally identified as the $\operatorname{U}(1)_{B-L}$.
+In models for light Dirac neutrinos, with some explanation for the smallness of
+their masses, usually  adhoc discrete symmetries are invoked to forbbid
+tree level Dirac or Majorana mass terms for the light right-handed neutrinos~\cite{Han:2018zcn,Wang:2017mcy}.
+%tree-level without adhoc symmetries
+The tree-level Dirac type-I seesaw with
+proper choices for the $\operatorname{U}(1)_{B-L}$ charges have been shown to be consistent without require extra ad-hoc discrette symmetries~\cite{}.
+%one-loop 
+In recent works, it has been shown that even at one-loop it is possible to have  $\operatorname{U}(1)_{B-L}$ as the only extra symmetry beyond the SM~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}\footnote{
+%extra-loops
+  For extensions with only extra scalars, solutions have been found with two and three loops}.
+%conexion with dark matter
+In this radiative cases, as a bonus,  the new scalars and fermions circulating the loop, can be dark matter candidates with the stability of the ligthest particle guarantee by the  very same continous symmetry.
+% remark
+We focus here in solutions for the radiative Dirac type-I seesaw, with
+only an extra symmetry responsible for the Diracness of the light neutrinos, the absence of any tree-level contribution and the existence of a dark sector constituyed by the particles circulating the loop.
+
+%conexion with DM
+In fact, another evidence that the SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM).
 The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}.

### 2019-08-01 draft.tex
Updates from Overleaf

--- 2019-07-29 draft.tex
@@
 \usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{siunitx} 
+%\usepackage{siunitx} 
 \usepackage{tabularx}
@@
 \label{sec:Model}
-As a preliminary model, we propose a model that includes an additional gauge symmetry $U(1)^{\prime}$.
-Where  gauge invariance is used to forbid Dirac and Majorana mass terms at tree level.
-Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$.
-The $U(1)^{\prime}$ charge for the new particles will be defined by the anomaly cancellation equations and the gauge invariance in Yukawa interactions.
-In this model the neutrinos are Dirac fermions.
-Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.
+%
+\begin{table}[t!]
+  \centering
+  \begin{tabular}{|c|c|c|c|}
+    \hline  
+    Fields     & $SU(2)_L$ & $U(1)_Y $ & $U(1)_X$ \\ \hline
+    % $H $  & 2  1/2  &  0 \\
+    $\eta$  & 2 & 1/2  & $1$ \\
+    $S$ & 1 & 0  & $2$ \\
+    $\sigma$ & 1 & 0 & $3$ \\
+    \hline
+    % $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
+    % $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
+    % $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
+    % \hline
+    % $L_i$  & $(2,-1/2)$ & $0$ \\
+    % $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
+    $\nu_{Ri}$ & 1 & 0 & -4\\
+    $\nu_{R3}$ & 1 & 0 & $5$\\
+    $\psi_{R\alpha}$  & 1 & 0 & $1$ \\\hline
+  \end{tabular}
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $U(1)_X$ gauge symmetry. }
+    \label{tab:partcont}
+\end{table}
+%
+With the aim of illustrate the one-loop Dirac neutrino mass generation we consider the particle content shown in Table \ref{tab:partcont}.
+Specifically, we introduce three scalar fields ($\eta, \sigma$ and $S$), where only $S$ develops a nonzero vacuum expectation value (VEV), and two sets of three singlet fermions, $\nu_{Ri}$ and $\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and $\alpha=1,2,3$.
+The model also includes an additional $U(1)_X$ gauge symmetry which is used to forbid the Dirac and Majorana neutrino mass terms at tree level.
+%Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$.
+The $U(1)_X$ charge for the new particles will be defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
+%In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.
 
-The most general Yukawa Lagrangian is:
+The most general Lagrangian contains the following Yukawa and scalar interactions:
 %
@@
     \mathcal{L} \subset& -[ 
-    h^{a}_{i} \overline{L_{i}} \eta \psi_{a} +  y^{a}_{j} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi_{a} + y_{\psi}^{a b} \overline{\psi^{c}_{a}} \psi_{b} S + \text{h.c}] \\
-    &- \mathcal{V}(H, S, \eta, \sigma)\,,
+    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^\dagger + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,,
 \end{align*}
 %
-where $L_{i}$ are the SM lepton doublets, $\eta = \left( \eta^{+} \ \eta^{0} \right)^{T}$, $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$ and $\mathcal{V}(H, S, \eta, \sigma)$ is the scalar potential.
-$h^{a}_i$ and $y^{a}_{j}$ ($i,j,a=1,2,3$) are matrix in flavor space.
-%
-\begin{table}
-  \centering
-  \begin{tabular}{|l|l|l|}
-    \hline  
-    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)^{\prime}$ \\ \hline
-    $H $  & $(2, 1/2)$ &  0 \\
-    $\eta$ & $(2,1/2)$ & $1$ \\
-    $S$ & $(1,0)$ & $2$ \\
-    $\sigma$ & $(1,0)$ & $3$ \\
-    \hline
-    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$ \\
-    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$ \\
-    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$ \\
-    \hline
-    $L_i$  & $(2,-1/2)$ & $0$ \\
-    $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
-    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $4$\\
-    $\overline{\nu_{R_k}}$ & $(1,0)$ & $-5$\\
-    $\psi_{i}$  & $(1,0)$ & $-1$ \\\hline
-  \end{tabular}
-  \caption{Scalars and left-handed fermions with their respective charges.}
-  \label{tab:partcont}
-\end{table}
-%
-
-The most general gauge invariant scalar potential for this model is
+where $L_{i}$ and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
+The scalar potential can be cast as
 %
 \begin{align*}
-    \mathcal{V}(H, S, \eta, \sigma) = & \mathcal{V}(H) + \mathcal{V}(S) + \mathcal{V}(\eta) + \mathcal{V}(\sigma) \\
+    \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \\
     &+  \lambda_{1} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
@@
 %
-where $\mathcal{V}(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$.
-We consider that the parameters are real, since we are not going to deal with the CP violation~\cite{Abe:2016sqa}.
+with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$.
+We assume $\mu$ real to preserve CP symmetry in the scalar sector, and $\mu^2_\eta,\mu^2_\sigma>0$ to avoid tree-level mixing terms among the fermions.
+Moreover, the scalar couplings are subject to perturbativity and vacuum stability constraints:
+\begin{align*}
+Stability constraints\\
+\lambda_{H} &\geq 0\,, & \lambda_{\eta} &\geq 0\,, & \lambda_{S} &\geq 0\,, & \lambda_{\sigma} &\geq 0\,, & \lambda_{1} &\geq 0\,, & \\
+\lambda_{2} &\geq 0\,, &
+\lambda_{3}+\lambda_{7} &\geq 0\,, & \lambda_{4} &\geq 0\,, & \lambda_{5} &\geq 0\,, & \lambda_{6} &\geq 0\,,
+\end{align*}
+where we can set $\rho^{2} = 1$, because we assume that $\lambda_{7} \leq 0$.
 
-\section{Scalar mass spectrum}
-\label{sec:ScaMassSpect}
-
- After spontaneous symmetry breaking, both Higgs doublet and scalar $S$ can to acquire vev's
+% \subsection{Scalar mass spectrum}
+%\label{sec:ScaMassSpect}
+By denotating the scalar fields as
 %
 \begin{align*}
-    H =& \begin{pmatrix}0 \\ \frac{1}{\sqrt{2}} (h+\upsilon_{1}) \end{pmatrix} \,,
-    &H_{2} =& \begin{pmatrix}\frac{1}{\sqrt{2}} (H+\upsilon_{2}+iA_{0}) \\ h^{-} \end{pmatrix} \,, &S =& \frac{1}{\sqrt{2}} (\phi+\upsilon_{s})
-    &\eta =& \begin{pmatrix}\eta^{+} \\ \eta^{0} \end{pmatrix} \,,
+  H = \begin{pmatrix}G^{\pm} \\ \frac{1}{\sqrt{2}} (\varphi+v_{H}+iG) \end{pmatrix} \,,&\hspace{1cm}
+  \eta = \begin{pmatrix}\eta^{+} \\ \frac{1}{\sqrt{2}}(\eta_R+i\eta_I) \end{pmatrix} \,,\\
+  S = \frac{1}{\sqrt{2}} (S_R+v_{S}+iS_I)\,,&\hspace{1cm}\sigma = \frac{1}{\sqrt{2}} (\sigma_R+i\sigma_I),
 \end{align*}
 %
-with $\eta^{0} = (\eta_{1}^{0}+i \eta_{2}^{0})/\sqrt{2}$ and $\sigma = ({\sigma}_{1}+i {\sigma}_{2})/\sqrt{2}$ and $\langle  H_{i} \rangle = \upsilon_{i}$ with $\upsilon=\sqrt{\upsilon_{1}^2+\upsilon_{2}^2} \simeq 246$\,GeV.
-It's possible to parameterize the ratio of these vev's as $\tan \beta = \upsilon_{2}/\upsilon_{1}$.
-
-With the minimum of the scalar potential it is possible to write $\mu_{H}^{2}$,$\mu_{H_{2}}^{2}$ and $\mu^{2}_{s}$ in terms of the other parameters the following way
+with $v_H= 246.22$ GeV.  
+By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
 %
 \begin{align*}
-    \mu^{2}_{H} =& -\frac{\upsilon^{2}}{2}\left[ 2 \lambda_{H} c^{2}_{\beta} - 2 t^{2}_{\beta} \left(\frac{\mu^{2}_{H_{2}}}{\upsilon^{2}}+\lambda_{H_{2}} s^{2}_{\beta} \right) + \left( \lambda_{3} - \lambda_{6} t^{2}_{\beta} \right) \frac{\upsilon^{2}_{s}}{\upsilon^{2}} \right]\,, \\
-    \mu_{1} =& -\frac{\upsilon^{2}}{\sqrt{2}} \left[ \left( \frac{2\mu^{2}_{H_{2}}}{\upsilon_{s}} + \lambda_{6} \upsilon_{s} \right) \frac{s_{\beta}}{\upsilon_{1} \upsilon} + \left( (\lambda_{1}+\lambda_{2})c^{2}_{\beta} + 2 \lambda_{H_{2}} s^{2}_{\beta} \right) \frac{t_{\beta}}{\upsilon_{s}} \right]\,, \\
-   \mu^{2}_{s} =& -\frac{\upsilon^{4}}{2 \upsilon^{2}_{s}} \left[ -2s^{2}_{\beta} \left( \lambda_{H_{2}} s^{2}_{\beta} + \frac{\mu^{2}_{H_{2}}}{\upsilon^{2}_{s}}\right) + \left( \frac{\lambda_{3}}{\upsilon^{2}} - (\lambda_{1}+\lambda_{2})s^{2}_{\beta} \right) c^{2}_{\beta} + 2 \lambda_{6} \frac{\upsilon^{4}_{s}}{\upsilon^{4}} \right]\,,
+    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  \upsilon^{2}_{H} + \lambda_{1}  \upsilon^{2}_{S}\right)\,,  &
+    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  \upsilon^{2}_{S} + \lambda_{1}  \upsilon^{2}_{H}\right)\,.
 \end{align*}
 %
-where $t_{\beta} = \tan \beta$, $c_{\beta} = \cos \beta$ and $s_{\beta} = \sin \beta$. This allows to reduce the number of free parameters.
-
-Of the original sixteen scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G^{0}$ and $G^{\prime}$).
-There are two physical neutral CP-even Higgs state ($H$ and $h$, where $m_{H} \geq m_{h}$), one scalar state ($\phi$), one physical CP-odd Higgs scalar ($A^{0}$), two CP-even scalar state ($\sigma_{1}$ and $\eta^{0}_{1}$), two CP-odd scalar state ($\sigma_{2}$ and $\eta^{0}_{2}$), one charged scalar pairs ($\eta^{\pm}$) and one charged Higgs pairs ($h^{\pm}$).
+Of the original twelve scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
+There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar state ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar state ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar pairs ($\eta^{\pm}$).
 The mass spectrum for the scalar sector is given by
 \begin{align*}
-    m_{h^{\pm}}^{2} &= \mu^{2}_{H_{2}} + \frac{1}{2}(\lambda_{1} \upsilon^{2}_{1} + 2\lambda_{H_{2}} \upsilon^{2}_{2} + \lambda_{6} \upsilon^{2}_{s})\,, \\
-    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{5} \upsilon^{2}_{1} + \lambda_{8} \upsilon^{2}_{2} + \lambda_{10} \upsilon^{2}_{s} )\,, \\
-    m_{A^{0}}^{2} &= m_{h^{\pm}}^{2} + \frac{1}{2} \lambda_{2} \upsilon^{2}_{1} \,,
+    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{3} \upsilon^{2}_{H} + \lambda_{5} \upsilon^{2}_{s} )\,, \\
+    m_{H}^{2} &= \lambda_{H} \upsilon_{H}^{2} + \mathcal{O}()\,, \\
+    m_{S}^{2} &= \lambda_{S} \upsilon_{S}^{2} + \mathcal{O}()\,.
 \end{align*}
 %
-note that the two charged scalars do not mix among themselves. The neutral mass eigenstate are defined as
+The neutral mass eigenstate are defined as
 %
 \begin{align*}
-    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(1,2)} \\ \eta_{(1,2)} \end{pmatrix} \,,
+    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
 \end{align*}
 %
-where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{4} \upsilon^{2}_{1} + \lambda_{7} \upsilon^{2}_{2} + \lambda_{9} \upsilon^{2}_{s})$\,,
-$b = \mu^{2}_{\eta^{\pm}} + \frac{1}{2}(\lambda_{12} \upsilon^{2}_{1} + \lambda_{13} \upsilon^{2}_{2})$ and $c = \mu \upsilon_{2}/\sqrt{2}$\,. The corresponding mass eigenvalues are
+where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\mu \upsilon_{H} \upsilon_{S}$\,.
+The corresponding mass eigenvalues are
 \begin{align*}
-    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c} \right)\,, \\
-     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c} \right)\,,
+    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c^{2}} \right)\,, \\
+     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c^{2}} \right)\,,
 \end{align*}
@@
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} = \frac{\sqrt{2}\mu \upsilon_{2}}{64 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i}^{a} M_{\psi_{a}}y_{j}^{a}}{m_{\chi_{R2}}^{2}-m_{\chi_{R1}}^{2}} \left[ F\left( \frac{m_{\chi_{R2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{\mu \upsilon_{H} \upsilon_{S}}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
 \end{align}
 %
-where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is loop function, $M_{\psi_{a}}$ is the fermión mass  and $\chi_{R_(1,2)}$ are the two CP-even mass eigenstate and $\chi_{I_{(1,2)}}$ are two CP-odd mass eigenstate.To obtain neutrino masses it is necessary that $\mu \neq 0$.
+where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is loop function, $M_{\psi_{a}}$ is the fermión mass  and $\chi_{R_{(1,2)}}$ are the two CP-even mass eigenstate and $\chi_{I_{(1,2)}}$ are two CP-odd mass eigenstate.To obtain neutrino masses it is necessary that $\mu \neq 0$.
 In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large.
 Another possibility is small values of $\mu$, this suppress the value of the neutrino masses.
-The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h^{a}_{i} y^{b}_{j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}.
+The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}.
 If only one fermion $\psi$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}.
@@
 \begin{align}
-(U^{(\nu)}_R)^{\dagger} M_{\nu_{2}} U^{(\nu)}_L = M_{\nu_{2}}^{\text{diag}} = \text{diag}(m1, m2, m3)\,,
+(U^{(\nu)}_R)^{\dagger} \mathcal{M}_{\nu} U^{(\nu)}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
 \end{align}
@@
 \begin{align}
-(M_{\nu_{2}})_{ij} = (U_{\text{PMNS}})_{ij} (M_{\nu_{2}}^{\text{diag}})_{jj}\,,
+(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
 \end{align}
@@
 \end{align}
-where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles.
+where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.
 
@@
 These CLFV processes are induced at one loop level, as shown in the figure~\ref{fig:LFV}.
-In this case, the $\psi_{a} \widetilde{\eta}^{\dagger} L_{i}$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.
+In this case, the $\overline{L} \tilde{\eta} \psi_{R}$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.
 
@@
 
-For $i \neq j$ we have CLFV processes.
-These processes are severely restricted by the current bounds , which set limits to the Yukawas.
+For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
 The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
@@
 For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment.
-In the case of the anomalous muon magnetic dipole moment, the experimental measurements do not agree with the values predicted by the SM~\cite{Lindner:2016bgg}.
+In the case of the anomalous muon magnetic dipole moment, the experimental measurements does not agree with the values predicted by the SM~\cite{Lindner:2016bgg}.
 This can be a proof of the veracity of the model, in addition to giving restrictions on the Yukawas.
@@
 \label{sec:DM}
-Depending on the the new particles mass hierarchy (scalars and fermions charged odd under $U(1)^{\prime}$), it is possible to have two candidates for DM.
+Depending on the the new particles mass hierarchy (scalars and fermions charged odd under $U(1)_X$), it is possible to have two candidates for DM.
 The first DM candidate is the lightest majorana fermion (assuming that $\psi_{1} < \psi_{2} < \psi_{3}$).
 The second candidate is scalar DM.
-The scalar that assumes the role of DM depends on which is the lightest scalar particle charged odd under $U(1)^{\prime}$.
+The scalar that assumes the role of DM depends on which is the lightest scalar particle charged odd under $U(1)_X$.
 In this model the scalar DM can be the neutral component of the scalar doublet $\eta^{0}$ or the scalar singlet $\sigma$.
@@
 \subsection{Scalar dark matter}
-For scalar DM we have that the lightest scalar charged odd under $U(1)^{\prime}$ must have a mass smaller than the lightest $\psi$ fermion.
+For scalar DM we have that the lightest scalar charged odd under $U(1)_X$ must have a mass smaller than the lightest $\psi$ fermion.
 Contrary to fermionic DM, scalar DM has additional interactions to Yukawa couplings (scalar and gauge interactions), which can be used to control relic density.
@@
 The lighter of them a would be dark matter particle.
+
+\footnote{Check 2r+2nu: -2,6,7,-9,-3  3r+2nu: -(5/2),7/2,-7,6,9/2}
 

### 2019-08-02 draft.tex
beta version of introduction

@@
 %Dirac or Majorana
-
+%TODO: check ad-hoc symmetries
 The interpretation of neutrino experimental data in terms of neutrino
@@
 the latter cannot be dismissed.
-%Dirac case
-If neutrinos are Dirac particles, the
-Standard Model (SM) particle content must be extended with
-right-handed neutrinos,
-%with cosmology implications
-which can increase the effective number of
-light neutrinos, $N_{\text{eff}}$, until 6. Therefore, to be compatible with the
-current cosmological restrictions on $N_{\text{eff}}$, the interactions
-of the extra right-handed neutrinos with the primordial plasma must be
-highly suppressed.
+% Dirac case
+If neutrinos are Dirac particles, the Standard Model (SM) particle
+content must be extended with right-handed neutrinos,
+% with cosmology implications
+which can increase the effective number of light neutrinos,
+$N_{\text{eff}}$, until 6. Therefore, to be compatible with the
+current cosmological restrictions on $N_{\text{eff}}$, the
+interactions of the extra right-handed neutrinos with the primordial
+plasma must be highly suppressed.
 
 %Smallness of neutrinos for both Dirac and Majorana
-On the other hand, To give small masses to at least two Majorana or
+On the other hand, to give small masses to at least two Majorana or
 Dirac neutrinos, as required to explain the neutrino oscillation
@@
 %focus in seesaw type I
-the seesaw mechanism
-with heavy fermions is usually invoked.
+the seesaw mechanism with heavy fermions is usually invoked.
 %tree-level case
-For the tree-level type-I
-seesaw we can have either light Majorana neutrinos with heavy Majorana
+For the tree-level type-I seesaw we can have either light Majorana
+neutrinos with heavy Majorana
 mediators~\cite{Minkowski:1977sc,Yanagida:1979as,GellMann:1980vs,Mohapatra:1979ia}
@@
 %one-loop case
-The
-radiative type-I seesaw includes both~\cite{} possibilities~\cite{},
+The radiative type-I seesaw includes both~\cite{Ma:2006km}
+possibilities~\cite{Farzan:2012sa},
 %new possibility in radiative case
 but now it is also possible to have light Majorana neutrinos with
-
-heavy Dirac mediators~\cite{}.
+heavy Dirac mediators~\cite{Ma:2013yga}.
 %New in this work
-In this work we want to explore the
-possibility to build a simple Dirac radiative type-I seesaw  model with 
-heavy Majorana mediators.
+In this work we want to explore the possibility to build a simple
+Dirac radiative type-I seesaw model with heavy Majorana mediators.
 %Old idea but first realized here
-It is worth noticing that this idea have
-been already illustrated in an extension of the minimal supersymmetric
-standard model~\cite{Demir:2007dt} but without show any explicit
-solution.
+It is worth noticing that this idea have been already illustrated in
+an extension of the minimal supersymmetric standard
+model~\cite{Demir:2007dt} but without show any explicit solution.
 
 %Features of the new propossed solution
-In general, solutions for light Dirac neutrino masses require a continous symmetry to guarantee their Diracness.
-This symmetry is usally identified as the $\operatorname{U}(1)_{B-L}$.
-In models for light Dirac neutrinos, with some explanation for the smallness of
-their masses, usually  adhoc discrete symmetries are invoked to forbbid
-tree level Dirac or Majorana mass terms for the light right-handed neutrinos~\cite{Han:2018zcn,Wang:2017mcy}.
+In general, solutions for light Dirac neutrino masses require a
+continuous symmetry to guarantee their Diracness. This symmetry is
+usually identified as the $\operatorname{U}(1)_{B-L}$.  Additionally,
+ad hoc discrete symmetries are invoked to forbid tree level Dirac or
+Majorana mass terms for the light right-handed
+neutrinos~\cite{Roncadelli:1983ty,Han:2018zcn,Wang:2017mcy}. 
 %tree-level without adhoc symmetries
-The tree-level Dirac type-I seesaw with
-proper choices for the $\operatorname{U}(1)_{B-L}$ charges have been shown to be consistent without require extra ad-hoc discrette symmetries~\cite{}.
+However, tree-level Dirac type-I seesaw with proper choices for the
+$\operatorname{U}(1)_{B-L}$ charges have been shown to be consistent
+without require any extra ad-hoc discrete symmetry~\cite{Ma:2014qra}.
 %one-loop 
-In recent works, it has been shown that even at one-loop it is possible to have  $\operatorname{U}(1)_{B-L}$ as the only extra symmetry beyond the SM~\cite{Calle:2018ovc, Bonilla:2018ynb, Saad:2019bqf}\footnote{
+In recent works, it has been shown that even for one-loop Dirac
+neutrino masses, it is possible to have $\operatorname{U}(1)_{B-L}$ as
+the only extra symmetry beyond the SM~\cite{Calle:2018ovc,
+  Bonilla:2018ynb, Saad:2019bqf}\footnote{
 %extra-loops
-  For extensions with only extra scalars, solutions have been found with two and three loops}.
+  For extensions with only extra scalars, solutions have been found with two and three loops~\cite{Saad:2019bqf}}.
 %conexion with dark matter
-In this radiative cases, as a bonus,  the new scalars and fermions circulating the loop, can be dark matter candidates with the stability of the ligthest particle guarantee by the  very same continous symmetry.
+As a bonus in this case, the new scalars and fermions circulating the
+loop can be dark matter candidates with the stability of the lightest
+of them guaranteed by the very same continuous symmetry.
 % remark
-We focus here in solutions for the radiative Dirac type-I seesaw, with
-only an extra symmetry responsible for the Diracness of the light neutrinos, the absence of any tree-level contribution and the existence of a dark sector constituyed by the particles circulating the loop.
+We focus here in solutions for the radiative Dirac type-I seesaw with
+Majorana mediators, which have only an extra symmetry responsible for the
+Diracness of the light neutrinos, the absence of any tree-level
+contribution and the existence of a dark sector constituted by the
+particles circulating the loop.
 
 %conexion with DM
-In fact, another evidence that the SM is not a complete theory is the missing mass in the universe, which is known as dark matter (DM).
-The main proposals that explain DM as a particle are given in Ref.~\cite{Bertone:2004pz}.
-We will make use of the scotogenic model~\cite{Ma:2006km}.
-In scotogenic model the neutrino masses and the DM have common explanation.
-The neutrino masses are generated by one-loop effects, where the candidates for DM are mediators in the loop.
+In fact, another evidence that the SM is not a complete theory is the
+missing matter content of the universe, which is known as dark matter
+(DM).
+% DM as particle
+The main proposals that explain DM as a particle are given in
+Ref.~\cite{Bertone:2004pz}.
+% too many possibilities
+Without evidence of DM as a particle there is not a clear path to pin
+out the DM properties nor the possible heavier companions of some
+extended sector. 
+% connect with other phenomena
+Linking the dark sector to other specific phenomenology allows to
+reduce the arbitrariness in the model building.
+% loop
+In our construction, the dark sector is related to the heavy sector
+responsible of the lightness of the neutrinos and the same symmetry
+which guarantees the lightness of the Dirac neutrinos is the
+responsible of the stability of the lightest dark particle (LDP).
+% new particle prediction
+The number of specific models is restricted.
 
-In this work we propose a Dirac radiative type-I seesaw,
-with Majorana fermion of the mediators in the loop..
-This mediators can to be DM candidate.
+% We will make use of the scotogenic model~\cite{Ma:2006km}. In
+% scotogenic model the neutrino masses and the DM have common
+% explanation. The neutrino masses are generated by one-loop effects,
+% where the candidates for DM are mediators in the loop.
+%Conclusion:
+In this work we propose a Dirac radiative type-I seesaw, with Majorana
+fermion of the mediators in the loop. This mediators can include a DM
+candidate.
+
 The rest of the paper is organized as follows.

### 2019-08-02 draft.tex
beta version of introduction

@@
 neutrino masses, it is possible to have $\operatorname{U}(1)_{B-L}$ as
-the only extra symmetry beyond the SM~\cite{Calle:2018ovc,
-  Bonilla:2018ynb, Saad:2019bqf}\footnote{
+the only extra symmetry beyond the SM~\cite{Calle:2018ovc,Bonilla:2018ynb,Saad:2019bqf}\footnote{
 %extra-loops
-  For extensions with only extra scalars, solutions have been found with two and three loops~\cite{Saad:2019bqf}}.
+  For extensions with only extra scalars, minimal solutions have been found with two and three loops~\cite{Saad:2019bqf}}.
 %conexion with dark matter
@@
 Diracness of the light neutrinos, the absence of any tree-level
-contribution and the existence of a dark sector constituted by the
+mass, and the existence of a dark sector constituted by the
 particles circulating the loop.
@@
 % new particle prediction
-The number of specific models is restricted.
+Therefore, the number of specific models is quite restricted.
 
@@
   \end{tabular}
-  \caption{Scalars and left-handed fermions with their respective charges. $Z_2$ to define THDM Type-II~\cite{1303.0168}}
+  \caption{Scalars and left-handed fermions with their respective charges. $Z_2$ to define THDM Type-II~\cite{Chiang:2013ixa}}
   \label{tab:partcont}

### 2019-08-05 draft.tex
uf

@@
 %Dirac or Majorana
-%TODO: check ad-hoc symmetries
 The interpretation of neutrino experimental data in terms of neutrino
@@
 usually identified as the $\operatorname{U}(1)_{B-L}$.  Additionally,
-ad hoc discrete symmetries are invoked to forbid tree level Dirac or
+ad-hoc discrete symmetries are invoked to forbid tree level Dirac or
 Majorana mass terms for the light right-handed
@@
 %Conclusion:
-In this work we propose a Dirac radiative type-I seesaw, with Majorana
-fermion of the mediators in the loop. This mediators can include a DM
-candidate.
+In this work we propose a radiative Dirac type-I seesaw, with Majorana
+fermions as mediators in the loop. This full set of mediators in the
+loop can include a DM candidate.
 
@@
 %
-With the aim of illustrate the one-loop Dirac neutrino mass generation we consider the particle content shown in Table \ref{tab:partcont}.
-Specifically, we introduce three scalar fields ($\eta, \sigma$ and $S$), where only $S$ develops a nonzero vacuum expectation value (VEV), and two sets of three singlet fermions, $\nu_{Ri}$ and $\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and $\alpha=1,2,3$.
-The model also includes an additional $U(1)_X$ gauge symmetry which is used to forbid the Dirac and Majorana neutrino mass terms at tree level.
+We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number $L$ conservation.
+Only the new particles including the light right handed neutrinos are charged under this symmetry.
+We choose the new particle set such that the following dimension six operator is genuinely realized
+\begin{align}
+  \mathcal{L}_{6D}=\frac{1}{\Lambda^2} \overline{L_i} H \nu_R S^2\,,
+\end{align}
+where $S$ is the singlet scalar field which can spontanouely break the $\operatorname{U}(1)_X$ symmetry.
+
+With the aim to illustrate the one-loop Dirac neutrino mass generation
+we consider the particle content shown in Table
+\ref{tab:partcont}. Specifically, we introduce three scalar fields
+($\eta, \sigma$ and $S$), where only $S$ develops a nonzero vacuum expectation
+value (VEV), and two sets of three singlet fermions, $\nu_{Ri}$ and
+$\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and $\alpha=1,2,3$.  The model also
+includes an additional $U(1)_X$ gauge symmetry which is used to forbid
+the Dirac and Majorana neutrino mass terms at tree level.
 %Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$.

### 2019-08-05 draft.tex
uf

@@
 \begin{align}
+  \label{eq:ld6}
   \mathcal{L}_{6D}=\frac{1}{\Lambda^2} \overline{L_i} H \nu_R S^2\,,
@@
 With the aim to illustrate the one-loop Dirac neutrino mass generation
-we consider the particle content shown in Table
-\ref{tab:partcont}. Specifically, we introduce three scalar fields
-($\eta, \sigma$ and $S$), where only $S$ develops a nonzero vacuum expectation
-value (VEV), and two sets of three singlet fermions, $\nu_{Ri}$ and
-$\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and $\alpha=1,2,3$.  The model also
-includes an additional $U(1)_X$ gauge symmetry which is used to forbid
-the Dirac and Majorana neutrino mass terms at tree level.
+we consider the particle content shown in Table \ref{tab:partcont} as
+a possible the realization of the effective operator in
+ec.~\eqref{eq:ld6}. Specifically, we introduce three scalar fields
+($\eta, \sigma$ and $S$), where only $S$ develops a nonzero vacuum
+expectation value (VEV), and two sets of three singlet fermions,
+$\nu_{Ri}$ and $\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and
+$\alpha=1,2,3$.  The model also includes an additional $U(1)_X$ gauge
+symmetry which is used to forbid the Dirac and Majorana neutrino mass
+terms at tree level.
 %Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$.
-The $U(1)_X$ charge for the new particles will be defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
+The $U(1)_X$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
 %In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.
@@
     \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \\
-    &+  \lambda_{1} (H^{\dagger} H ) (S^{\dagger} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{\dagger} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
-    &+ \lambda_{4} (S^{\dagger} S) (\sigma^{\dagger} \sigma ) + \lambda_{5} (S^{\dagger} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{\dagger} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
-    &+ \mu (\eta^{\dagger} H S^{\dagger} \sigma + \text{h.c.})\,,
+    &+  \lambda_{1} (H^{\dagger} H ) (S^{*} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{*} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
+    &+ \lambda_{4} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{5} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
+    &+ \lambda_{8} (\eta^{\dagger} H S^{*} \sigma + \text{h.c.})\,,
 \end{align*}
 %
-with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}/2$.
+with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}$.
+After the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the last term gives raise to the soft trilinear coupling
+\begin{align}
+  \mu=\lambda_8 \langle S \rangle\,.
+\end{align}
 We assume $\mu$ real to preserve CP symmetry in the scalar sector, and $\mu^2_\eta,\mu^2_\sigma>0$ to avoid tree-level mixing terms among the fermions.
@@
 \begin{align*}
-Stability constraints\\
 \lambda_{H} &\geq 0\,, & \lambda_{\eta} &\geq 0\,, & \lambda_{S} &\geq 0\,, & \lambda_{\sigma} &\geq 0\,, & \lambda_{1} &\geq 0\,, & \\
@@
 %\label{sec:ScaMassSpect}
-By denotating the scalar fields as
+To establish the scalar spectrum we expand the scalar fields as
 %
 \begin{align*}
-  H = \begin{pmatrix}G^{\pm} \\ \frac{1}{\sqrt{2}} (\varphi+v_{H}+iG) \end{pmatrix} \,,&\hspace{1cm}
+  H = \begin{pmatrix}G^{\pm} \\ \frac{1}{\sqrt{2}} (\varphi+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
   \eta = \begin{pmatrix}\eta^{+} \\ \frac{1}{\sqrt{2}}(\eta_R+i\eta_I) \end{pmatrix} \,,\\
@@
 %
-with $v_H= 246.22$ GeV.  
+with $v= 246.22$ GeV.  
 By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
@@
 \begin{align*}
-    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  \upsilon^{2}_{H} + \lambda_{1}  \upsilon^{2}_{S}\right)\,,  &
-    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  \upsilon^{2}_{S} + \lambda_{1}  \upsilon^{2}_{H}\right)\,.
+    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  v^2 + \lambda_{1}  v_S\right)\,,  &
+    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  v^{2}_{S} + \lambda_{1}  v^2\right)\,.
 \end{align*}
 %
-Of the original twelve scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
+Of the original twelve scalar degrees of freedom in the model\todo{what are the twelve?}, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
 There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar state ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar state ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar pairs ($\eta^{\pm}$).
@@
 %
- The Dirac neutrino mass matrix in this model is generate to one loop level, which is shown in fig(\ref{fig:zee}). The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
+ The Dirac neutrino mass matrix in this model is generated at one loop-level according to the diagram in  fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
 %
@@
 %
-where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is loop function, $M_{\psi_{a}}$ is the fermión mass  and $\chi_{R_{(1,2)}}$ are the two CP-even mass eigenstate and $\chi_{I_{(1,2)}}$ are two CP-odd mass eigenstate.To obtain neutrino masses it is necessary that $\mu \neq 0$.
+where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is the loop function, $M_{\psi_{a}}$ is the fermion mass  and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the two CP-even (CP-odd) mass eigenstates.
+To obtain neutrino masses it is necessary that $\mu \neq 0$.
 In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large.
@@
 The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}.
-If only one fermion $\psi$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}.
+If only one fermion $\psi_R$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}.
 In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).
@@
 \end{align}
-If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstate, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$.
-Therefore, we can to express the Dirac neutrino mass matrix following way
+If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstates, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$.
+Therefore, we can express the Dirac neutrino mass matrix in the following way
 \begin{align}
@@
 The new Yukawa interactions in Eq~\eqref{Eq:LagY} in our model introduce processes that violate the leptonic flavor in the charged sector (CLFV).
-These CLFV processes are induced at one loop level, as shown in the figure~\ref{fig:LFV}.
-In this case, the $\overline{L} \tilde{\eta} \psi_{R}$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.
+These CLFV processes are induced at one loop level, as shown in the fig.~\ref{fig:LFV}.
+In this case, the $\overline{L} \tilde{\eta} \psi_R$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.
 
@@
 
-The results of $T^{\nu_R}_{dec}$ and $\Delta N_{eff}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in Fig~\ref{fig:Neff}.
+The results of $T^{\nu_R}_{dec}$ and $\Delta N_{eff}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}.
 We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
@@
 \appendix
+
+\section{General solution}
+
+The general solution to fig.~\ref{fig:zee} is
+\begin{align}
+  L=&\nu_R+4\psi_R -H \,,& S=& 2\psi_R \nonumber\\
+  \sigma=& -\nu_R-\psi_R\,,& \eta=& H-\nu_R-3\psi_R\,.
+\end{align}
+The consistency condition for $H=0$ is
+\begin{align}
+  L=\nu_R+4\psi_R\,.
+\end{align}
+
+On the other hand, if the second singlet scalar in the quartic vertex is $S'$, we have
+\begin{align}
+  L=-H+\nu_R+2\psi_R+S'\to \nu_R+2\psi_R+S'\,.
+\end{align}
 

### 2019-08-06 draft.tex
lc

@@
 In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
-In section~\ref{sec:LFV} we show the lepton flavor violation (LFV)experimental  constraints.
+In section~\ref{sec:LFV} we show the lepton flavor violation (LFV) experimental  constraints.
 Finally, in the section~\ref{sec:DM} we present the viable DM candidates.
@@
 \begin{align*}
-  H = \begin{pmatrix}G^{\pm} \\ \frac{1}{\sqrt{2}} (\varphi+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
+  H = \begin{pmatrix}G^+ \\ \frac{1}{\sqrt{2}} (\varphi+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
   \eta = \begin{pmatrix}\eta^{+} \\ \frac{1}{\sqrt{2}}(\eta_R+i\eta_I) \end{pmatrix} \,,\\
@@
 %
-Of the original twelve scalar degrees of freedom in the model\todo{what are the twelve?}, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
-There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar state ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar state ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar pairs ($\eta^{\pm}$).
+Of the original twelve scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorve four of them (the Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
+There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar states ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar states ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar ($\eta^{\pm}$).
 The mass spectrum for the scalar sector is given by
@@
 
+On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis defined as $
+\begin{pmatrix}
+  \psi_1 &
+  \psi_2 &
+  \psi_3
+\end{pmatrix}^{\operatorname{T}}
+$, with masses $M_{\psi_a}$ ($a=1,2,3$).
 \section{Neutrinos}

### 2019-08-06 draft.tex
lc

@@
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} = \frac{\mu \upsilon_{H} \upsilon_{S}}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
 \end{align}
 %
-where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is the loop function, $M_{\psi_{a}}$ is the fermion mass  and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the two CP-even (CP-odd) mass eigenstates.
-To obtain neutrino masses it is necessary that $\mu \neq 0$.
-In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large.
-Another possibility is small values of $\mu$, this suppress the value of the neutrino masses.
-The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}.
-If only one fermion $\psi_R$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}.
-In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).
+%check the following formula:
+where $F(x) =x \log x/(x-1)$ is the loop function, $M_{\psi_{a}}$ is
+the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
+two CP-even (CP-odd) mass eigenstates.
+To obtain neutrino masses it is necessary that $\mu \neq 0$. In this
+way, in addition to the suppression from the seesaw mechanism, we can
+have further suppression in the neutrino mass matrix for small values
+of $\mu$.
+The structure of the effective neutrino mass matrix is given by the
+product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to
+the structure of the neutrino mass matrix for the tree-level seesaw
+mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one
+fermion $\psi_R$ is added, we will have two massless neutrinos, which
+does not agree with the current data obtained from the neutrino
+experiments~\cite{deSalas:2017kay}. In our case, we will assume the
+existence of three fermions, generating Dirac scotogenic masses for
+the two neutrinos ($\nu_{k}$ is massless due to the assignment of
+charges).
 
-For the Dirac neutrinos the mass matrices are diagonalized by
+The mass matrix for Dirac neutrinos is diagonalized by
 \begin{align}

### 2019-08-06 draft.tex
lc

@@
 \begin{align}
-(U^{(\nu)}_R)^{\dagger} \mathcal{M}_{\nu} U^{(\nu)}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
+(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
 \end{align}
-where $U^{(\nu)}_R$ and $U^{(\nu)}_L$  are unitary $3 \times 3$ matrices. In the most general Dirac neutrino mass matrices, lepton mixing matrix is
+where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are unitary $3 \times 3$
+matrices. The leptonic charged currents with non-massless neutrinos
+are parametrized in terms of the unitary mass
 \begin{align}
-U_{\text{PMNS}} = (U^{(\ell)}_L)^{\dagger} U^{(\nu)}_L\,.
+U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
 \end{align}
-If we work in the basis where $\ell$ and $\nu_{R}$ are mass eigenstates, the matrices $U_{L}^{(\ell)} = U_{R}^{\nu} = \mathds{1}$.
-Therefore, we can express the Dirac neutrino mass matrix in the following way
+where is the left diagonalization matrix of the charged leptons.
+As we already are in the diagonal basis after the calculation of the
+one-loop neutrino masses, we can set
+$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
+Therefore, we can express the Dirac neutrino mass matrix in the
+following way
 \begin{align}

### 2019-08-06 draft.tex
lc

@@
 \begin{align*}
-\label{Eq:LagY}
+\label{eq:LagY}
     \mathcal{L} \subset& -[ 
@@
 %
-The new Yukawa interactions in Eq~\eqref{Eq:LagY} in our model introduce processes that violate the leptonic flavor in the charged sector (CLFV).
+The new Yukawa interactions in eq.~\eqref{eq:LagY} in our model introduce processes of charged lepton flavor violation (CLFV).
 These CLFV processes are induced at one loop level, as shown in the fig.~\ref{fig:LFV}.
@@
 \label{sec:DM}
-Depending on the the new particles mass hierarchy (scalars and fermions charged odd under $U(1)_X$), it is possible to have two candidates for DM.
-The first DM candidate is the lightest majorana fermion (assuming that $\psi_{1} < \psi_{2} < \psi_{3}$).
-The second candidate is scalar DM.
-The scalar that assumes the role of DM depends on which is the lightest scalar particle charged odd under $U(1)_X$.
-In this model the scalar DM can be the neutral component of the scalar doublet $\eta^{0}$ or the scalar singlet $\sigma$.
+From table~\ref{tab:partcont}. we can see that after the spontaneous breaking of
+$\operatorname{U}(1)_X$ there is remnant $Z_2$ symmetry under which the particles circulating the loop in fig.~\ref{fig:zee}.
+plus $\nu_{R3}$ are odd, while the other right handed neutrinos and the SM particles are even.
+The lightest odd particle can be a dark matter candidate.
+In this way we can have either fermionic or scalar dark matter in the model.
 
 \subsection{Fermionic dark matter}
-In the case that the mass of the lightest fermion $\psi$ is smaller than the mass of the scalars, the DM will be fermionic.
-For this DM it is possible to have the following observable decay of the scalar $\eta^{\pm} \to l^{\pm} \psi_{1}$, therefore, the other fermions decay as $ \psi \to l^{\pm} l^{\mp} \psi_{1}$ and $\psi \to l^{\pm} l^{\mp} \psi_{1,2} $, through $\eta^{\pm}$.
-The relic density of DM can be controlled by annihilation $\psi_{1} \psi_{1} \to l _{\alpha} \overline{l}_{\beta} $, via Yukawa coupling $h^{a}_{i}$.
-These Yukawa couplings are restricted under LFV and neutrino masses.
-But, Yukawa couplings $y^{a}_{j}$ is free.
+The relic density of DM is controlled by annihilation $\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via Yukawa coupling $h^{a}_{i}$.
+These Yukawa couplings are restricted by CLFV and neutrino masses.
+%But, Yukawa couplings $y^{a}_{j}$ is free.
 
-Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa links and this particle does not interact with gluons and quarks, this model has no direct detection restrictions for DM.
-In the case where the mass of the other fermions and scalars is nearly degenerated to $\psi_{1} $, the processes of coaniquilación are relevant in relic density~\cite{Klasen:2013jpa}.
+Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.
+In the case where the mass of the other fermions and scalars is nearly degenerated to $\psi_{1} $, the processes of coannihilation  can be relevant for the relic density calculation~\cite{Klasen:2013jpa}.
+
+% In the case that the mass of the lightest fermion $\psi$ is smaller
+% than the mass of the scalars, the DM will be fermionic. For this DM it
+% is possible to have the following observable decay of the scalar
+% $\eta^{\pm} \to l^{\pm} \psi_{1}$, therefore, the other fermions decay
+% as $ \psi \to l^{\pm} l^{\mp} \psi_{1}$ and
+% $\psi \to l^{\pm} l^{\mp} \psi_{1,2} $, through $\eta^{\pm}$.
 
 \subsection{Scalar dark matter}
-For scalar DM we have that the lightest scalar charged odd under $U(1)_X$ must have a mass smaller than the lightest $\psi$ fermion.
-Contrary to fermionic DM, scalar DM has additional interactions to Yukawa couplings (scalar and gauge interactions), which can be used to control relic density.
+Contrary to fermionic DM, scalar DM has additional interactions beyond the Yukawa couplings  which can be used to control relic density.
+This corresponds to the simplified dark matter model of scalar singlet-doblet dark matter, which have been studied in detail in~\cite{}
 
-If the lightest scale is the neutral part of the scalar doublet, we will have that the DM will be similar to the model of the inert doublet~\cite{Honorez:2010re}.
-For the inert doublet model there are two mass regions for DM which can to reproduce adequately the relic density ($50$GeV \textless $m_{DM}$ \textless $70$GeV and $535$GeV \textless $m_{DM}$ \textless $20$TeV)~\cite{Garcia-Cely:2015khw}.
-In recent studies, these two regions are connected through use of a second doublet~\cite{Borah:2019aeq}.
-How we have in the model the Yukawa coupling, the decay $\psi_{i} \to l^{\pm} \eta^{\mp}$ is possible.
-In addition, decay is given via scalar interactions $\eta^{\pm} \to \eta^{0} + {W^{\pm}}$, where $W^{\pm}$ can be real or virtual and decay to leptons or quarks.
+When the lightest scalar  is mainly a scalar doublet, the phenomenology will be similar inert doublet model~\cite{Honorez:2010re}.
+For this kind of DM model  inert doublet model there are two mass regions for DM which can to reproduce adequately the relic density ($50$GeV \textless $m_{DM}$ \textless $70$GeV and $535$GeV \textless $m_{DM}$ \textless $20$TeV)~\cite{Garcia-Cely:2015khw}.
 
-Now, if the lightest scale is the scalar singlet, the DM will be similar to the model in Ref.~\cite{Athron:2017kgt}.
-The mass range for the scalar singlet that produces the adequate relic density is between approximately the Higgs mass and about $300$GeV and masses above $1$TeV.
-For this model, the term in the Lagrangian $\sigma^{2} H^{2}_{i}$ is known as the \textquotedblleft Higgs portal\textquotedblright.
+% In recent studies, these two regions are connected through use of a
+% second doublet~\cite{Borah:2019aeq}. How we have in the model the
+% Yukawa coupling, the decay $\psi_{i} \to l^{\pm} \eta^{\mp}$ is
+% possible. In addition, decay is given via scalar interactions
+% $\eta^{\pm} \to \eta^{0} + {W^{\pm}}$, where $W^{\pm}$ can be real or
+% virtual and decay to leptons or quarks.
+
+Now, if the lightest scalar is mainly a singlet, the DM will be
+similar to Singlet Scalar Dark Matter
+Model~\cite{Athron:2017kgt}\todo{change for the original ref by Ma et
+  al. etc}.
+The mass range for the scalar singlet that produces the adequate relic
+density is around the Higgs resonance and for masses above $1$TeV. For
+this model~\cite{}, the relevant coupling for DM phenomenology is the
+Higgs portal trough the Lagrangian term $\sigma^{2} H^{2}_{i}$.
 This term generates interesting phenomenological consequences.
-Such as, thermal production of DM in the early universe~\cite{Yaguna:2008hd}, direct detection and $h \to \sigma \sigma$~\cite{Mambrini:2011ik}.
-In addition, this model has important contributions to cosmology, in phenomena such as inflation~\cite{Lerner:2009xg} and baryogenesis~\cite{Cline:2012hg}.
+Such as, thermal production of DM in the early
+universe~\cite{Yaguna:2008hd}, direct detection and invisible decay of
+SM Higgs through $h \to \sigma \sigma$~\cite{Mambrini:2011ik}.
+In addition, this model has important contributions for cosmology, in
+phenomena such as inflation~\cite{Lerner:2009xg} and
+baryogenesis~\cite{Cline:2012hg}.
 
@@
     $H $  & $(2, 1/2)$ &  0 &$+$\\
-    %$\widetilde{H_{2}}$  & $(2,1/2)$ &  $0$ &$-$\\
     $\eta$ & $(2,1/2)$ & $1-\psi\to 5/2$ &$-$\\
@@
     $\sigma$ & $(1,0)$ & $\nu+\psi=\eta=1-\psi\to 5/2$&$-$\\
-    \hline
-    $Q_{L_{i}}$  & $(2,-1/6)$ & $0$& $+$\\
-    $\overline{u_{R_{i}}}$ & $(1,-2/3)$ & $0$& $+$\\
-    $\overline{d_{R_{i}}}$ & $(1,1/3)$ & $0$& $+$\\
-    \hline
     $L_i$  & $(2,-1/2)$ & $-1$& $+$\\
@@
   \end{tabular}
-  \caption{Scalars and left-handed fermions with their respective charges. $Z_2$ to define THDM Type-II~\cite{Chiang:2013ixa}}
+  \caption{Scalars and left-handed fermions with their respective charges.}
   \label{tab:partcont}
@@
 %
-
-% Checl also:
-$-2,6,-9,-3,7$
 

### 2019-08-06 draft.tex
lc

@@
     \hline  
-    Fields     & $SU(2)_L$ & $U(1)_Y $ & $U(1)_X$ \\ \hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_X$ \\ \hline
     % $H $  & 2  1/2  &  0 \\
-    $\eta$  & 2 & 1/2  & $1$ \\
-    $S$ & 1 & 0  & $2$ \\
-    $\sigma$ & 1 & 0 & $3$ \\
+    $\eta$  & $\boldsymbol{2}$ & $1/2$  & $1$ \\
+    $S$ & $\boldsymbol{1}$ & $0$  & $2$ \\
+    $\sigma$ & $\boldsymbol{1}$ & $0$ & $3$ \\
     \hline
@@
     % $\overline{e_{R_i}}$ & $(1,1)$ & $0$ \\
-    $\nu_{Ri}$ & 1 & 0 & -4\\
-    $\nu_{R3}$ & 1 & 0 & $5$\\
-    $\psi_{R\alpha}$  & 1 & 0 & $1$ \\\hline
+    $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$\\
+    $\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $5$\\
+    $\psi_{R\alpha}$  & $\boldsymbol{1}$ & 0 & $1$ \\\hline
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $U(1)_X$ gauge symmetry. }
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. }
     \label{tab:partcont}
@@
 $\nu_{Ri}$ and $\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and
-$\alpha=1,2,3$.  The model also includes an additional $U(1)_X$ gauge
+$\alpha=1,2,3$.  The model also includes an additional $\operatorname{U}(1)_X$ gauge
 symmetry which is used to forbid the Dirac and Majorana neutrino mass
 terms at tree level.
-%Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $SU(2)_L$.
-The $U(1)_X$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
+%Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $\operatorname{SU}(2)_L$.
+The $\operatorname{U}(1)_X$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
 %In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.
@@
 \section{Cosmological constraints}
-\begin{comment}
-%
+
+A not-so-minimal model can be obtained as the one-loop realization of
+the effective 5-dimensional operator for Dirac neutrino masses~\cite{}
+\begin{align}
+  \label{eq:ld5}
+  \mathcal{L}_{5D}=\frac{1}{\Lambda} \overline{L_i} H \nu_R S\,,
+\end{align}
+as displayed in fig.~\ref{fig:ld5}.
+In this case we use the usual $\operatorname{U}(1)_{B-L}$ for the lepton doublet, so that an extra set of quiral fermion needs to be added in a vector-like way to cancel out the anomalies.
+The assignment is displayed in Table~\ref{tab:partcont2}
+
 \begin{figure}
 \centering
-\includegraphics[scale=0.6]{Tdec.pdf}
-\includegraphics[scale=0.6]{Delta_Neff1.pdf}
-\caption{One-loop generation of Dirac neutrino mass}
-\label{fig:Neff}
+\includegraphics[scale=0.75]{Neutrino2.pdf}
+\caption{One-loop realization of the dimension-5 effective Dirac neutrino mass operator }
+\label{fig:ld5}
 \end{figure}
 %
-\end{comment}
 
-%
 \begin{table}
   \centering
-  \begin{tabular}{|l|l|c|c|}
+  \begin{tabular}{|c|c|c|c|}
     \hline  
-    Particles     & $\left( SU(2)_L, U(1)_Y \right)$ & $U(1)_{L}$& $Z_2$\\ \hline
-    $H $  & $(2, 1/2)$ &  0 &$+$\\
-    $\eta$ & $(2,1/2)$ & $1-\psi\to 5/2$ &$-$\\
-    $S$ & $(1,0)$ & $-2\psi\to 3$ &$+$\\
-    $\sigma$ & $(1,0)$ & $\nu+\psi=\eta=1-\psi\to 5/2$&$-$\\
-    $L_i$  & $(2,-1/2)$ & $-1$& $+$\\
-    $\overline{e_{R_i}}$ & $(1,1)$ & $+1$ & $+$ \\
-    $\overline{\nu_{R_{i,j}}}$ & $(1,0)$ & $\nu\to 1-2\psi\to 4$&$+$\\
-    $\overline{\nu_{R_k}}$ & $(1,0)$ & $\nu_k$&$+$\\
-    $\psi_{i}$  & $(1,0)$ & $\psi\to -3/2$ &$-$\\\hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{B-L}$ \\ \hline
+     $L $  & $\boldsymbol{1}$& $-1/2$  &  $-1$ \\
+    $\eta$  & $\boldsymbol{2}$ & $+1/2$  & $4-r$ \\
+    $S$ & $\boldsymbol{1}$ & $0$  & $2r$ \\
+    $\sigma$ & $\boldsymbol{1}$ & $0$ & $4-r$ \\
+    \hline
+     $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$\\
+    $\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $5$\\
+    $\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$ & $r$ \\\hline
+    $\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $r$ \\\hline
   \end{tabular}
-  \caption{Scalars and left-handed fermions with their respective charges.}
-  \label{tab:partcont}
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. Now $\alpha=1,2$}
+    \label{tab:partcont2}
 \end{table}
-%
 
-The solution in Table~\ref{tab:partcont} is no anomaly free.
-To have $L=-1$ while keeping the same minimal set of scalars would require anomaly solutions with at least two pairs of the very same lepton charges, such that
-\begin{align}
-    2\psi+2\nu+\cdots=&3 \nonumber\\
-    2\psi^3+2\nu^3+\cdots=&3
-\end{align}
-If we introduce two additional left-handed fields $(\xi_i)^\dagger$,  with $U(1)_L$ $+3/2$, the anomalies cancel out.
-Moreover, we have both Dirac mass terms $(\Upsilon_i)^\dagger\psi_j$ and $ \Upsilon_i \Upsilon_j \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
+In this way we end up with a model with four Majorana fermions, one more than in the minimal solution.
+Alternatively we can have a single set of $\psi_R$ and $\xi_L$ but with two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk}.
+If we choose $r$ as a fraction with denominator $2$, let say $r=3/2$, the $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
+
+The two additional left-handed fields $\xi_{L\alpha}$,  with a $\operatorname{U}(1)_{B-L}$ charge of $r=3/2$,  cancel out the anomalies.
+Moreover, we have both Dirac mass terms $\overline{\xi_{L \alpha}}\psi_{R \beta}$ and $ \overline{\xi_{L\alpha}^c }\xi_{L \beta} \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
 The lighter of them a would be dark matter particle.
 
-\footnote{Check 2r+2nu: -2,6,7,-9,-3  3r+2nu: -(5/2),7/2,-7,6,9/2}
+% \footnote{Check 2r+2nu: -2,6,7,-9,-3  3r+2nu: -(5/2),7/2,-7,6,9/2}
 
 The existence of three new right neutrinos in nature contribute to the total energy density of the universe.
-These new contributions can modify the cosmological observables in the CMB (cosmic microwave background).
-These new neutrinos contribute to the existence of dark radiation, which affects the expansion processes of the universe, which affects the number of relativistic degrees of freedom for neutrinos.
+These new contributions can modify the cosmological observables in the cosmic microwave background (CMB).
+These new neutrinos contribute to the existence of dark radiation, which affects the expansion processes of the universe and the number of relativistic degrees of freedom for neutrinos.
 
-In the case of our models, this new gauge symmetry introduces a new gauge boson that mediates the interaction of the right neutrinos and the SM.
-This allows the right neutrinos to thermally modify the relativistic degrees of freedom, this contributions are given by~\cite{Anchordoqui:2012qu, Anchordoqui:2011nh}
+In the case of our model, the new gauge symmetry introducesa  new gauge boson that mediates interaction of the right neutrinos and the SM.
+This allows the right neutrinos to thermally modify the relativistic degrees of freedom with contributions given by~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
 %
 \begin{align*}
-    \Delta N_{eff} = N_{eff} - N^{SM}_{eff} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{dec})}{g(T^{\nu_{R}}_{dec})} \right)^{4}
+    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{SM}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
 \end{align*}
@@
 where $ g(T) $ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
-The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{dec} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ dec}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}.
+The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}.
 The rate of interaction of the right neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
@@
 
-The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{dec} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
+The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
 %
@@
 \caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$.
-In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{eff}$) in function of $M_{z^{\prime}}/g^{\prime}$.
+In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{z^{\prime}}/g^{\prime}$.
 The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}.
@@
 where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature T.
-To estimate the contribution to relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{dec}$).
+To estimate the contribution to relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$).
 The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
@@
 \begin{align*}
-\Gamma(T^{\nu_R}_{dec}) = H(T^{\nu_R}_{dec})\,, 
+\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
 \end{align*}
@@
 where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom.
-By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{dec} $ by a root finding method, it is possible to calculate $\Delta N_{eff}$.
+By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
 
-The results of $T^{\nu_R}_{dec}$ and $\Delta N_{eff}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}.
+The results of $T^{\nu_R}_{\text{dec}}$ and $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}.
 We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
@@
 \begin{align}
-  L=&\nu_R+4\psi_R -H \,,& S=& 2\psi_R \nonumber\\
-  \sigma=& -\nu_R-\psi_R\,,& \eta=& H-\nu_R-3\psi_R\,.
+  L=&\nu_R+4\psi_R -H \,,& \eta=& H-\nu_R-3\psi_R \nonumber\\
+  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
 \end{align}
@@
 \begin{align}
-  L=-H+\nu_R+2\psi_R+S'\to \nu_R+2\psi_R+S'\,.
+  L=&-H+\nu_R+2\psi_R+S'\to \nu_R+2\psi_R+S'\,, &
+  \eta=&H-\nu_R-\psi_R-S' \nonumber\\
+  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
 \end{align}
@@
 %%% End: 
-The cross section is given in [], in the case with heavy mediator $T^{\nu_R}_{dec} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
+The cross section is given in [], in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is

### 2019-08-06 draft.tex
lc

@@
 $\operatorname{U}(1)_{B-L}$ charges have been shown to be consistent
-without require any extra ad-hoc discrete symmetry~\cite{Ma:2014qra}.
+without require any extra ad-hoc discrete symmetries~\cite{Ma:2014qra}.
 %one-loop 
@@
 %
-We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number $L$ conservation.
+We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
 Only the new particles including the light right handed neutrinos are charged under this symmetry.
@@
 With the aim to illustrate the one-loop Dirac neutrino mass generation
-we consider the particle content shown in Table \ref{tab:partcont} as
-a possible the realization of the effective operator in
+we consider the particle content shown in Table \ref{tab:partcont}. as
+a possible realization of the effective operator in
 ec.~\eqref{eq:ld6}. Specifically, we introduce three scalar fields
-($\eta, \sigma$ and $S$), where only $S$ develops a nonzero vacuum
-expectation value (VEV), and two sets of three singlet fermions,
-$\nu_{Ri}$ and $\nu_{R3}$, and $\psi_{R\alpha}$, where $i=1,2$ and
+$\eta, \sigma$ and $S$, where only $S$ develops a nonzero vacuum
+expectation value (VEV),  two sets of three singlet fermions,
+$\nu_{Ri}$ and $\nu_{R3}$, and a set a heavy Majorana fermions, $\psi_{R\alpha}$, where $i=1,2$ and
 $\alpha=1,2,3$.  The model also includes an additional $\operatorname{U}(1)_X$ gauge
@@
 A not-so-minimal model can be obtained as the one-loop realization of
-the effective 5-dimensional operator for Dirac neutrino masses~\cite{}
+the effective 5-dimensional operator for Dirac neutrino masses~\cite{Gu:2006dc}
 \begin{align}
@@
 as displayed in fig.~\ref{fig:ld5}.
-In this case we use the usual $\operatorname{U}(1)_{B-L}$ for the lepton doublet, so that an extra set of quiral fermion needs to be added in a vector-like way to cancel out the anomalies.
-The assignment is displayed in Table~\ref{tab:partcont2}
+In this case we can use the standard $\operatorname{U}(1)_{B-L}$
+charge of $-1$ for the lepton doublets.
+It is well established that the solution for anomaly cancellation
+conditions with three quiral fields with exotic
+$\operatorname{U}(1)_{B-L}$ charges: $-4$,~$-4$,~$5$,  when assigned to the
+three light right-handed neutrinos can forbid three level Dirac and
+Majorana masses~\cite{Calle:2018ovc}.
+The presence of a set of heavy Majorana mediators to realize the
+dimension-5 operator at one-loop with the diagram in
+fig.~\ref{fig:ld5}., would spoil the anomaly cancellation conditions.
+However, we can further add an extra set of quiral fermion in a
+vector-like way, such that the full set heavy fermions do not affect
+the anomaly cancellation. A such assignment is displayed in
+Table~\ref{tab:partcont2}.
+The fields $\xi_{L \alpha}$ guarantee the anomaly cancellation and
+their Majorana masses are obtained in the same way than the ones for
+$\psi_{R\alpha}$.
 
@@
 Moreover, we have both Dirac mass terms $\overline{\xi_{L \alpha}}\psi_{R \beta}$ and $ \overline{\xi_{L\alpha}^c }\xi_{L \beta} \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
-The lighter of them a would be dark matter particle.
+The lighter of them a would be dark matter candidate.
 
@@
 
-The existence of three new right neutrinos in nature contribute to the total energy density of the universe.
-These new contributions can modify the cosmological observables in the cosmic microwave background (CMB).
-These new neutrinos contribute to the existence of dark radiation, which affects the expansion processes of the universe and the number of relativistic degrees of freedom for neutrinos.
+The coupling of $Z'$ with the lepton doublets opens up the possibility
+of thermalization of the right handed neutrinos in the primordial
+plasma.
+In fact, the existence of three new right neutrinos in nature
+contribute to the total energy density of the universe. These new
+contributions can modify the cosmological observables in the cosmic
+microwave background (CMB). These new neutrinos contribute to the
+existence of dark radiation, which affects the expansion processes of
+the universe and the number of relativistic degrees of freedom for
+neutrinos.
 
-In the case of our model, the new gauge symmetry introducesa  new gauge boson that mediates interaction of the right neutrinos and the SM.
+In the case of our model, the new gauge symmetry introduces  new gauge boson that mediates interaction of the right neutrinos and the SM.
 This allows the right neutrinos to thermally modify the relativistic degrees of freedom with contributions given by~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
@@
 \begin{align*}
-    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{SM}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
+    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
 \end{align*}
@@
 %
-where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distributión, $g_{\nu_R} = 2$ is spin number, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, where $p$ and $k$ are the momenta of the particle and $\theta$, the angle between them and the number density of right-handed neutrinos is given by
+where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$ is the spin number, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, where $p$ and $k$ are the momenta of the particle and $\theta$, the angle between them, and the number density of right-handed neutrinos is given by
 \begin{align*}
@@
 
-The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masse, we have that the cross section is
+The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is
 %
@@
 where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e.
-$N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new simmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson.
+$N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson.
 Solving the integrals with this last cross section we obtain that the interaction rate is given by
@@
 %
-%
-\begin{figure}
-\centering
-\includegraphics[scale=0.8]{DeltaNeff.pdf}
-\caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$.
-In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{z^{\prime}}/g^{\prime}$.
-The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}.
-The region shaded in violet shows the bound from LEP  LEP~\cite{Alioli:2017nzr}.}
-\label{fig:Neff}
-\end{figure}
-%
-where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature T.
-To estimate the contribution to relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$).
+where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$.
+To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$).
 The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
@@
 %
-where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom.
+and the $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom.
 By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
@@
 We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
-The bound that come from Planck~\cite{ghanim:2018eyx}
+The bound that come from Planck~\cite{ghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
+For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$.
+
+%
+\begin{figure}
+\centering
+\includegraphics[scale=0.8]{DeltaNeff.pdf}
+\caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$.
+In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{z^{\prime}}/g^{\prime}$.
+The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}.
+The region shaded in violet shows the bound from LEP  LEP~\cite{Alioli:2017nzr}.}
+\label{fig:Neff}
+\end{figure}
+%
 
 \includegraphics[scale=0.9]{DeltaNeff.pdf}
-
-is stronger than the bound of LEP~\cite{Alioli:2017nzr}. For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$.
 
@@
 %%% End:
-The cross section is given in [], in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is

### 2019-08-12 draft.tex
Updates from Overleaf

@@
 %
-where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\mu \upsilon_{H} \upsilon_{S}$\,.
+where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\lambda_8 v_{H} v_{S}$\,.
 The corresponding mass eigenvalues are
@@
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}^{2}} \right) \right] + (R \to I)\,,
 \end{align}
@@
 the structure of the neutrino mass matrix for the tree-level seesaw
-mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one
+mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}.
+
+If only one
 fermion $\psi_R$ is added, we will have two massless neutrinos, which
@@
 charges).
-
+If we consider the case in which $m_{\eta^{\pm}}^2 = \mu_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$ and $\lambda_7$, $\lambda_2$, $\lambda_4 \gg 1$.
+Taking $m_{\chi_{R_{2}}}-m_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m_{\chi_{R_{2}}}+m_{\chi_{R_{1}}} = 2 m_{\eta^{\pm}}^{2}$ one finds
+%
+\begin{align*}
+(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}-M_{\psi_{a}}^{2}} \left[1 - \frac{M_{\psi_{a}}^{2}}{m_{\eta^{\pm}}^{2}-M_{\psi_{a}}^{2}} \log \left( \frac{m_{\eta^{\pm}}^{2}}{M_{\psi_{a}}^{2}} \right)\right]\,,
+\end{align*}
+%
+and if we take $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$ one has 
+%
+\begin{align}
+(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}}\,, \\
+& \sim 0.006~\text{eV} \left( \frac{\lambda_8}{1 \text{GeV}}\right) \left( \frac{v_{S}}{10 \text{TeV}}\right) \left( \frac{M_{\psi_{a}}}{1 \text{TeV}}\right) \left( \frac{50 \text{TeV}}{m_{\eta^{\pm}}}\right)^{2} \left( \frac{h_{i a} y_{a j}^{\dagger}}{10^{-6}}\right)\,.
+\nonumber
+\end{align}
+%
 The mass matrix for Dirac neutrinos is diagonalized by
-\begin{align}
+\begin{align*}
 (U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
-\end{align}
+\end{align*}
 where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are unitary $3 \times 3$
@@
 are parametrized in terms of the unitary mass
-\begin{align}
+\begin{align*}
 U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
-\end{align}
+\end{align*}
 where is the left diagonalization matrix of the charged leptons.
@@
 where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
-\begin{align}
+\begin{align*}
 U_{\text{PMNS}} = \begin{pmatrix}
@@
 \end{pmatrix}\,,
-\end{align}
+\end{align*}
 where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.
@@
 The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
-These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.3 \times 10^{-13} $~\cite{Adam:2013mnn}, Br$(\tau \to e\gamma) $\textless$ 3.3 \times 10^{-8}$ and Br$(\tau \to~\mu\gamma) $\textless$ 4.4 \times 10^{-8}$~\cite{Aubert:2009ag, Bona:2007qt, Miyazaki:2012mx}.
+These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn}, Br$(\tau \to e\gamma) $\textless$ 3.3 \times 10^{-8}$ and Br$(\tau \to~\mu\gamma) $\textless$ 4.4 \times 10^{-8}$~\cite{Aubert:2009ag, Bona:2007qt, Miyazaki:2012mx}.
 
+In the limit $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$, $t_{\alpha} \to 0$ the decay width reads
+%
+\begin{align}
+ \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h^{\alpha}_{i} m_{i} h^{\alpha}_{j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,,
+\end{align}
+%
+using the current experimental constraint, can be fullfilled provided
+%
+\begin{align*}
+    \left( \sum_{\alpha} \frac{h^{}_{i \alpha} h_{\alpha j}^{*}}{M^{2}_{\eta^{-}}} \right)^{2} \leq 5.7 \times 10^{-13} \frac{768 \pi G_{F}^{2}}{\alpha_{EM}}
+\end{align*}
+%
+which leads to a very slight requirement,
+\begin{align*}
+    \left| \sum_{\alpha}h^{}_{i \alpha} h_{\alpha j}^{*}\left(\frac{50\text{TeV}}{M^{2}_{\eta^{-}}} \right)^{2} \right| \leq 12.65
+\end{align*}
+%
 For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment.

### 2019-08-12 draft.tex
lc

@@
 \subsection{Fermionic dark matter}
-The relic density of DM is controlled by annihilation $\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via Yukawa coupling $h^{a}_{i}$.
-These Yukawa couplings are restricted by CLFV and neutrino masses.
-%But, Yukawa couplings $y^{a}_{j}$ is free.
+The relic density of DM is controlled by the $Z'$ portal~\footnote{For
+  a recent review of Majorana Dark matter with a $Z'$ portal
+  see~\cite{Blanco:2019hah} } and
+% check Ibarra papers
+also through the annihilation
+$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via
+Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
+CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
+In the case where the mass of the other fermions and scalars is nearly
+degenerated to $\psi_{1} $, the processes of coannihilation can be
+relevant for the relic density calculation~\cite{Klasen:2013jpa}.
 
 Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.
-In the case where the mass of the other fermions and scalars is nearly degenerated to $\psi_{1} $, the processes of coannihilation  can be relevant for the relic density calculation~\cite{Klasen:2013jpa}.
 

### 2019-08-13 draft.tex
fp
fc
Updates from Overleaf
full solutions

@@
 \end{align*}
+For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
+The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
+These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\
 
@@
   \centering
-  \begin{tabular}{|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|c|}
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{B-L}$ \\ \hline
-     $L $  & $\boldsymbol{1}$& $-1/2$  &  $-1$ \\
-    $\eta$  & $\boldsymbol{2}$ & $+1/2$  & $4-r$ \\
-    $S$ & $\boldsymbol{1}$ & $0$  & $2r$ \\
-    $\sigma$ & $\boldsymbol{1}$ & $0$ & $4-r$ \\
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_A$& $\operatorname{U}(1)_B$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
+$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1/3$&  $-1$&  $1$&  $0$&  $2/3$ \\
+$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $1/3$&  $1$&  $-1$&  $1$&  $-1/3$ \\
+$Q $  & $\boldsymbol{2}$& $-1/6$  &  $1/3$&  $0$ &  $0$&  $1/2$&  $1/6$ \\\hline
+$e_R $  & $\boldsymbol{1}$& $-1$  &  $-1$&  $1$ &  $-1$ &  $-2$&  $0$ \\
+$L $  & $\boldsymbol{2}$& $-1/2$  &  $-1$&  $0$ &  $0$ &  $-3/2$&  $-1/2$ \\
+$H $  & $\boldsymbol{2}$& $-1/2$  &  $0$&  $1$ &  $-1$ &  $1/2$&  $-1/2$ \\
+$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $5/2$& $-3/2$ &$3/2$ &$3$&$2$ \\
+$S$ & $\boldsymbol{1}$ & $0$  & $3$& $-3$ & $3$ & $3$& $3$ \\
+$\sigma$ & $\boldsymbol{1}$ & $0$ & $5/2$& $-5/2$ & $5/2$ & $5/2$& $5/2$ \\
 \hline
-     $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$\\
-    $\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $5$\\
-    $\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$ & $r$ \\\hline
-    $\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $r$ \\\hline
+ $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $4$ & $-4$ & $-4$& $-4$\\
+$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $-5$ & $5$ & $5$& $5$\\
+$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/2$& $-3/2$ & $3/2$ & $3/2$& $3/2$ \\\hline
+$\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/2$ & $-3/2$ & $3/2$ & $3/2$& $3/2$\\\hline
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. Now $\alpha=1,2$}
+  \caption{The new scalars and fermions with their respective charges. The SM fields have the usual $U(1)_{B-L}$ assignment. Now $\alpha=1,2$}
     \label{tab:partcont2}
@@
 
-On the other hand, if the second singlet scalar in the quartic vertex is $S'$, we have
+On the other hand, for fig.~\ref{fig:ld5}
 \begin{align}
-  L=&-H+\nu_R+2\psi_R+S'\to \nu_R+2\psi_R+S'\,, &
-  \eta=&H-\nu_R-\psi_R-S' \nonumber\\
+  L=&-H+\nu_R+2\psi_R &
+  \eta=&H-\nu_R-\psi_R \nonumber\\
   \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
 \end{align}
+$\nu_R$, $H$  and $L$ are fixed from the anomaly cancellation conditions.
 

### 2019-08-13 draft.tex
nn

@@
 as displayed in fig.~\ref{fig:ld5}.
-In this case we can use the standard $\operatorname{U}(1)_{B-L}$
-charge of $-1$ for the lepton doublets.
-It is well established that the solution for anomaly cancellation
-conditions with three quiral fields with exotic
-$\operatorname{U}(1)_{B-L}$ charges: $-4$,~$-4$,~$5$,  when assigned to the
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc}.
+We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
+The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
+\begin{align}
+  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
+\end{align}
+The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos.
+For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
+\begin{align}
+  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
+\end{align}
+
+We are interested here in the case of the exotic set of $X$-charges
+charges: $\mp 4$,~$\mp 4$,~$\pm 5$, that when assigned to the
 three light right-handed neutrinos can forbid three level Dirac and
-Majorana masses~\cite{Calle:2018ovc}.
+Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
+Abelian gauge groups $X=B-L,A,B,D,G$ defined in~\cite{Campos:2017dgc}.
 The presence of a set of heavy Majorana mediators to realize the
@@
 
+Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
+
 \appendix

### 2019-08-15 draft.tex
Updates from Overleaf
jfjf

@@
 
-With the aim to illustrate the one-loop Dirac neutrino mass generation
+eszWith the aim to illustrate the one-loop Dirac neutrino mass generation
 we consider the particle content shown in Table \ref{tab:partcont}. as
@@
 \end{align*}
+For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
+The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
+These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\
+
 For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
@@
 as displayed in fig.~\ref{fig:ld5}.
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc}.
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc,Okada:2018tgy}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
@@
 \end{align}
+There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
+\begin{align}
+  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
+\end{align}
+The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
+
+For this kind of solutions we have that
+\begin{align}
+  \psi=&-\frac{\nu+1}{2}\,,&\eta=&-\frac{\nu+1}{2}-l\,,&\sigma=&\frac{1-\nu}{2}\,.
+\end{align}
 
@@
 Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
-Abelian gauge groups $X=B-L,A,B,D,G$ defined in~\cite{Campos:2017dgc}.
+Abelian gauge groups $X=B-L,B,D,G$ defined in~\cite{Campos:2017dgc}.
 The presence of a set of heavy Majorana mediators to realize the
@@
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_A$& $\operatorname{U}(1)_B$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
-$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1/3$&  $-1$&  $1$&  $0$&  $2/3$ \\
-$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $1/3$&  $1$&  $-1$&  $1$&  $-1/3$ \\
-$Q $  & $\boldsymbol{2}$& $-1/6$  &  $1/3$&  $0$ &  $0$&  $1/2$&  $1/6$ \\\hline
-$e_R $  & $\boldsymbol{1}$& $-1$  &  $-1$&  $1$ &  $-1$ &  $-2$&  $0$ \\
-$L $  & $\boldsymbol{2}$& $-1/2$  &  $-1$&  $0$ &  $0$ &  $-3/2$&  $-1/2$ \\
-$H $  & $\boldsymbol{2}$& $-1/2$  &  $0$&  $1$ &  $-1$ &  $1/2$&  $-1/2$ \\
-$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $5/2$& $-3/2$ &$3/2$ &$3$&$2$ \\
-$S$ & $\boldsymbol{1}$ & $0$  & $3$& $-3$ & $3$ & $3$& $3$ \\
-$\sigma$ & $\boldsymbol{1}$ & $0$ & $5/2$& $-5/2$ & $5/2$ & $5/2$& $5/2$ \\
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_B$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
+$L $  & $\boldsymbol{2}$& $-1/2$  &  $l$&  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
+$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1+2l/3$&  $1/3$&    $1$&  $0$&  $2/3$ \\
+$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
+$Q $  & $\boldsymbol{2}$& $-1/6$  &  $-l/3$& $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
+$e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
+$H $  & $\boldsymbol{2}$& $-1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
+$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/2-l$& $5/2$& $3/2$ &$3$&$2$ \\
+$S$ & $\boldsymbol{1}$ & $0$  & $3$& $3$&  $3$ & $3$& $3$ \\
+$\sigma$ & $\boldsymbol{1}$ & $0$ & $5/2$& $5/2$&  $5/2$ & $5/2$& $5/2$ \\
 \hline
- $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $4$ & $-4$ & $-4$& $-4$\\
-$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $-5$ & $5$ & $5$& $5$\\
-$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/2$& $-3/2$ & $3/2$ & $3/2$& $3/2$ \\\hline
-$\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/2$ & $-3/2$ & $3/2$ & $3/2$& $3/2$\\\hline
+ $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
+$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $+5$&  $5$ & $5$& $5$\\
+$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/2$ & $3/2$&  $3/2$ & $3/2$& $3/2$ \\\hline
+$\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/2$& $3/2$ &  $3/2$ & $3/2$& $3/2$\\\hline
   \end{tabular}

### 2019-08-29 draft.tex
Updates from Overleaf

@@
 In the next section we present the model and the particle content.
-In the section~\ref{sec:ScaMassSpect} we study the scalar mass spectrum after spontaneous symmetry breaking.
+In the section~\ref{sec:Model} we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
 In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
 In section~\ref{sec:LFV} we show the lepton flavor violation (LFV) experimental  constraints.
-Finally, in the section~\ref{sec:DM} we present the viable DM candidates.
+In section~\ref{sec:DM} we present the viable DM candidates.
+Finally, In section~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{eff}$) in a nonminimum model for different extra abelian symmetries.
 
@@
 Only the new particles including the light right handed neutrinos are charged under this symmetry.
-We choose the new particle set such that the following dimension six operator is genuinely realized
+We choose the new particle set such that the following dimension six operator is genuinely realized at one-loop level
 \begin{align}
   \label{eq:ld6}
-  \mathcal{L}_{6D}=\frac{1}{\Lambda^2} \overline{L_i} H \nu_R S^2\,,
+  \mathcal{O}_{6D}=\frac{1}{\Lambda^2} \overline{L_i} \tilde{H} \nu_R S^2\,,
 \end{align}
-where $S$ is the singlet scalar field which can spontanouely break the $\operatorname{U}(1)_X$ symmetry.
+where $S$ is the singlet scalar field which spontaneously breaks the $\operatorname{U}(1)_X$ symmetry needed to forbid the Dirac and Majorana neutrino mass terms at tree level.
 
-eszWith the aim to illustrate the one-loop Dirac neutrino mass generation
-we consider the particle content shown in Table \ref{tab:partcont}. as
-a possible realization of the effective operator in
-ec.~\eqref{eq:ld6}. Specifically, we introduce three scalar fields
+With the aim to illustrate the one-loop Dirac neutrino mass generation
+we consider the particle content shown in Table \ref{tab:partcont} as
+a possible realization of the effective operator $\mathcal{O}_{6D}$. Specifically, we introduce three scalar fields
 $\eta, \sigma$ and $S$, where only $S$ develops a nonzero vacuum
-expectation value (VEV),  two sets of three singlet fermions,
-$\nu_{Ri}$ and $\nu_{R3}$, and a set a heavy Majorana fermions, $\psi_{R\alpha}$, where $i=1,2$ and
-$\alpha=1,2,3$.  The model also includes an additional $\operatorname{U}(1)_X$ gauge
-symmetry which is used to forbid the Dirac and Majorana neutrino mass
-terms at tree level.
+expectation value (VEV),  a set of three singlet fermions,
+$\nu_{Ri}$ ($i=1,2$) and $\nu_{R3}$, and another set of three heavy Majorana fermions, $\psi_{R\alpha}$ ($\alpha=1,2,3$).  
+%The model also includes an additional $\operatorname{U}(1)_X$ gauge
+%symmetry which is used to forbid the Dirac and Majorana neutrino mass
+%terms at tree level.
 %Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $\operatorname{SU}(2)_L$.
@@
 \label{eq:LagY}
-    \mathcal{L} \subset& -[ 
-    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^{\dagger} \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^\dagger + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,,
+    \mathcal{L} \supset& -[ 
+    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^* \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^* + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,,
 \end{align*}
 %
-where $L_{i}$ and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^{\dagger}$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
+where $L_{i}$ and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
 The scalar potential can be cast as
@@
 %
+%
+%\begin{align*}
+%    \mathcal{V}(H, S, \eta, \sigma) = & \sum_{i} %V(\omega_i)+\sum_{i<j}|\omega_i|^2|\omega_j|^2+ \lambda_{7} (\eta^{\dagger} H ) %(H^{\dagger} \eta) +\lambda_{8} (\eta^{\dagger} H S^{*} \sigma + \text{h.c.})\,,
+%\end{align*}
+%
 with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}$. 
-After the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the last term gives raise to the soft trilinear coupling
-\begin{align}
-  \mu=\lambda_8 \langle S \rangle\,.
-\end{align}
-We assume $\mu$ real to preserve CP symmetry in the scalar sector, and $\mu^2_\eta,\mu^2_\sigma>0$ to avoid tree-level mixing terms among the fermions.
-Moreover, the scalar couplings are subject to perturbativity and vacuum stability constraints:
-\begin{align*}
-\lambda_{H} &\geq 0\,, & \lambda_{\eta} &\geq 0\,, & \lambda_{S} &\geq 0\,, & \lambda_{\sigma} &\geq 0\,, & \lambda_{1} &\geq 0\,, & \\
-\lambda_{2} &\geq 0\,, &
-\lambda_{3}+\lambda_{7} &\geq 0\,, & \lambda_{4} &\geq 0\,, & \lambda_{5} &\geq 0\,, & \lambda_{6} &\geq 0\,,
-\end{align*}
-where we can set $\rho^{2} = 1$, because we assume that $\lambda_{7} \leq 0$.
-
+Note that after the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the $\lambda_8$ term gives rise to the mixing between the neutral parts of $\eta$ and $\sigma$, which is mandatory to generate non-zero radiative masses.
+%Note that after the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the last term gives rise to the soft trilinear coupling
+%\begin{align}
+%  \mu=\lambda_8 \langle S \rangle\,,
+%\end{align}
+We assume $\lambda_8$ and $\langle S\rangle$ reals to preserve CP symmetry in the scalar sector, and $\mu^2_\eta,\mu^2_\sigma>0$ to avoid tree-level mixing terms among the fermions. 
+Moreover, we also assume $\lambda_1\ll1$  such that the scalar $S$ and $H$ do not mix allowing us to identify the CP even scalar particle in $H$ as the SM Higgs boson. 
 % \subsection{Scalar mass spectrum}
@@
 \begin{align*}
-  H = \begin{pmatrix}G^+ \\ \frac{1}{\sqrt{2}} (\varphi+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
+  H = \begin{pmatrix}G^+ \\ \frac{1}{\sqrt{2}} (h+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
   \eta = \begin{pmatrix}\eta^{+} \\ \frac{1}{\sqrt{2}}(\eta_R+i\eta_I) \end{pmatrix} \,,\\
@@
 %
-with $v= 246.22$ GeV.  
-By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
+with $v_H= 246.22$ GeV.  
+%By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
+%
+%\begin{align*}
+%    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  v^2 + \lambda_{1}  v_S\right)\,,  &
+%    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  v^{2}_{S} + \lambda_{1}  v^2\right)\,.
+%\end{align*}
+%
+Of the original twelve scalar degrees of freedom in the model, the gauge bosons $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorb four of them (the Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
+Thus, the scalar spectrum contains two sets of two neutral CP-even states ($h$ and $S_{R}$,  and $\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar states ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar ($\eta^{\pm}$).
+%We assume that $\lambda_{1} \ll 1$, such that the scalar $S$ and $H$ do not mix. 
+The mass spectrum for the unmixed scalars reads
+\begin{align*}
+   & m_{\eta^{\pm}}^{2}= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{3} \upsilon^{2}_{H} + \lambda_{5} \upsilon^{2}_{S} )\,,\,\,\,\, m_{H}^{2} = \lambda_{H} \upsilon_{H}^{2}\,,\,\,\,\,    m_{S}^{2}= \lambda_{S} \upsilon_{S}^{2}\,.
+\end{align*}
+%
+The other mass eigenstates are defined as
 %
 \begin{align*}
-    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  v^2 + \lambda_{1}  v_S\right)\,,  &
-    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  v^{2}_{S} + \lambda_{1}  v^2\right)\,.
+    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} \cos\theta & -\sin\theta \\ \sin\theta & \cos\theta \end{pmatrix} \begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
 \end{align*}
 %
-Of the original twelve scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorve four of them (the Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
-There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar states ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar states ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar ($\eta^{\pm}$).
-The mass spectrum for the scalar sector is given by
-\begin{align*}
-    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{3} \upsilon^{2}_{H} + \lambda_{5} \upsilon^{2}_{s} )\,, \\
-    m_{H}^{2} &= \lambda_{H} \upsilon_{H}^{2} + \mathcal{O}()\,, \\
-    m_{S}^{2} &= \lambda_{S} \upsilon_{S}^{2} + \mathcal{O}()\,.
-\end{align*}
+where $\tan\theta= 2c/(b-a)$, with $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\lambda_8 v_{H} v_{S}$\,.
+Note that the CP-even  states $\chi_{R(1,2)}$ are mass degenerate with CP-odd ones $\chi_{I(1,2)}$, with masses $ m_{\chi_{(1,2)}}^{2}= [a + b \mp \sqrt{(a-b)^{2} + 4c^{2}}]/2$.
+
+%The other neutral mass eigenstates are defined as
 %
-The neutral mass eigenstate are defined as
+%\begin{align*}
+%    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} %c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} %\begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
+%\end{align*}
 %
-\begin{align*}
-    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
-\end{align*}
-%
-where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\lambda_8 v_{H} v_{S}$\,.
-The corresponding mass eigenvalues are
-\begin{align*}
-    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c^{2}} \right)\,, \\
-     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c^{2}} \right)\,,
-\end{align*}
-For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
-The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
-These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\
+%where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$, with $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} %\upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} %\upsilon^{2}_{S})$ and $c = \frac{1}{2}\lambda_8 v_{H} v_{S}$\,.
+%The corresponding mass eigenvalues are
+%\begin{align*}
+%   m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c^{2}} \right)\,, \\
+%     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c^{2}} \right)\,,
+%\end{align*}
 
-For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
-The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
-These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\
+On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
+%\begin{pmatrix}
+  %\psi_1 &
+  %\psi_2 &
+  %\psi_3
+%\end{pmatrix}^{\operatorname{T}}$$
 
-On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis defined as $
-\begin{pmatrix}
-  \psi_1 &
-  \psi_2 &
-  \psi_3
-\end{pmatrix}^{\operatorname{T}}
-$, with masses $M_{\psi_a}$ ($a=1,2,3$).
 \section{Neutrinos}
@@
 %
- The Dirac neutrino mass matrix in this model is generated at one loop-level according to the diagram in  fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
+ The Dirac neutrino mass matrix in this model is generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by
 %
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}^{2}} \right) \right] + (R \to I)\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
 \end{align}
@@
 %check the following formula:
-where $F(x) =x \log x/(x-1)$ is the loop function, $M_{\psi_{a}}$ is
-the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
-two CP-even (CP-odd) mass eigenstates.
-To obtain neutrino masses it is necessary that $\mu \neq 0$. In this
+where $F(x) =x \log x/(x-1)$. 
+%, $M_{\psi_{a}}$ is
+%the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
+%two CP-even (CP-odd) mass eigenstates.
+It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 v_S \neq 0$. In this
 way, in addition to the suppression from the seesaw mechanism, we can
@@
 charges).
-If we consider the case in which $m_{\eta^{\pm}}^2 = \mu_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$ and $\lambda_7$, $\lambda_2$, $\lambda_4 \gg 1$.
-Taking $m_{\chi_{R_{2}}}-m_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m_{\chi_{R_{2}}}+m_{\chi_{R_{1}}} = 2 m_{\eta^{\pm}}^{2}$ one finds
+If we consider the case in which $m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$ and $\lambda_7$, $\lambda_2$, $\lambda_4 \ll 1$.
+Taking $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m_{\eta^{\pm}}^{2}$ one finds
 %
 \begin{align*}
-(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}-M_{\psi_{a}}^{2}} \left[1 - \frac{M_{\psi_{a}}^{2}}{m_{\eta^{\pm}}^{2}-M_{\psi_{a}}^{2}} \log \left( \frac{m_{\eta^{\pm}}^{2}}{M_{\psi_{a}}^{2}} \right)\right]\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{a}}y^{*}_{j\alpha}} {m_{\eta^{\pm}}^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_{\eta^{\pm}}^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\eta^{\pm}}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
 \end{align*}
@@
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}}\,, \\
-& \sim 0.006~\text{eV} \left( \frac{\lambda_8}{1 \text{GeV}}\right) \left( \frac{v_{S}}{10 \text{TeV}}\right) \left( \frac{M_{\psi_{a}}}{1 \text{TeV}}\right) \left( \frac{50 \text{TeV}}{m_{\eta^{\pm}}}\right)^{2} \left( \frac{h_{i a} y_{a j}^{\dagger}}{10^{-6}}\right)\,.
+(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}}\,, \\
+& \sim 0.003~\text{eV} \left( \frac{\lambda_8}{1 \text{GeV}}\right) \left( \frac{v_{S}}{10 \text{TeV}}\right) \left( \frac{M_{\psi_{a}}}{1 \text{TeV}}\right) \left( \frac{50 \text{TeV}}{m_{\eta^{\pm}}}\right)^{2} \left( \frac{h_{i a} y_{a j}^{\dagger}}{10^{-6}}\right)\,.
 \nonumber
@@
 \centering
-\includegraphics[scale=0.6]{LFV.pdf}
-\caption{Feynman diagram for process $l^{-}_{i} \to l^{-}_{j} \gamma$}
+\includegraphics[scale=0.75]{LFV.pdf}
+\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
 \label{fig:LFV}
@@
 \begin{align}
- \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h^{\alpha}_{i} m_{i} h^{\alpha}_{j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
+ \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
 \end{align}
@@
 \begin{align}
- \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h^{\alpha}_{i} m_{i} h^{\alpha}_{j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,,
+ \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,, 
 \end{align}
 %
-using the current experimental constraint, can be fullfilled provided
+using the current experimental constraint to Br$(\mu \to e\gamma)$, can be fullfilled provided
 %
@@
 Contrary to fermionic DM, scalar DM has additional interactions beyond the Yukawa couplings  which can be used to control relic density.
-This corresponds to the simplified dark matter model of scalar singlet-doblet dark matter, which have been studied in detail in~\cite{}
+This corresponds to the simplified dark matter model of scalar singlet-doblet dark matter, which have been studied in detail in~\cite{Restrepo:2019soi}
 
@@
 \section{Cosmological constraints}
-
+\label{sec:CosmoConstraints}
 A not-so-minimal model can be obtained as the one-loop realization of
@@
 
-In this way we end up with a model with four Majorana fermions, one more than in the minimal solution.
-Alternatively we can have a single set of $\psi_R$ and $\xi_L$ but with two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk}.
+In this way we end up with a model with four Majorana fermions, two more than in the minimal solution.
+Alternatively we can have a single set of $\psi_R$ and $\xi_L$ but two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk}.
 If we choose $r$ as a fraction with denominator $2$, let say $r=3/2$, the $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
@@
 %
-where $ g(T) $ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
+where $N_{\nu_R}$ is the neutrino number with same charges and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
 The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}.
@@
 \end{align*}
-%
+% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,
+
 where the Hubble expansion parameter is
-%
+% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,
+
 \begin{align*}
@@
 We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
-The bound that come from Planck~\cite{ghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
-For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$.
+The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
+For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$ for all the symmetries studied here.
 
@@
 \centering
-\includegraphics[scale=0.8]{DeltaNeff.pdf}
-\caption{In the upper panel is the decoupling temperature of the right neutrino $\nu_{R}$ in function of $M_{z^{\prime}}/g^{\prime}$.
-In the lower panel is the additional contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{z^{\prime}}/g^{\prime}$.
-The gray shaded region is excluded by the measurements in the Planck CMB~\cite{Aghanim:2018eyx}.
-The region shaded in violet shows the bound from LEP  LEP~\cite{Alioli:2017nzr}.}
+\includegraphics[scale=0.8]{D_Neff.pdf}
+\caption{Contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
+The region above the gray line is excluded by the measurements in the Planck~\cite{Aghanim:2018eyx}.
+The horizontal dashed lines show the sensitivity of future experiments, SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
+}
 \label{fig:Neff}
 \end{figure}
-%
-
-\includegraphics[scale=0.9]{DeltaNeff.pdf}
 

### 2019-08-29 draft.tex
h

@@
 continuous symmetry to guarantee their Diracness. This symmetry is
-usually identified as the $\operatorname{U}(1)_{B-L}$.  Additionally,
-ad-hoc discrete symmetries are invoked to forbid tree level Dirac or
-Majorana mass terms for the light right-handed
+usually identified as the local $\operatorname{U}(1)_{B-L}$.
+Additionally, ad-hoc discrete symmetries are invoked to forbid tree
+level Dirac or Majorana mass terms for the light right-handed
 neutrinos~\cite{Roncadelli:1983ty,Han:2018zcn,Wang:2017mcy}.
@@
 We focus here in solutions for the radiative Dirac type-I seesaw with
-Majorana mediators, which have only an extra symmetry responsible for the
+Majorana mediators, which have only an extra local symmetry responsible for the
 Diracness of the light neutrinos, the absence of any tree-level
@@
 Ref.~\cite{Bertone:2004pz}.
+%not found
+However, there have been only gravitational evidence for the existence
+of dark matter so far.
 % too many possibilities
-Without evidence of DM as a particle there is not a clear path to pin
+Without evidence of DM as a particle, there is not a clear path to pin
 out the DM properties nor the possible heavier companions of some
-extended sector. 
+extended dark sector. 
 % connect with other phenomena

### 2019-09-07 draft.tex
Updates from Overleaf

@@
 Only the new particles including the light right handed neutrinos are charged under this symmetry.
-We choose the new particle set such that the following dimension six operator is genuinely realized at one-loop level
+We choose the new particle set such that the following dimension six operator is realized at one-loop level
 \begin{align}
   \label{eq:ld6}
-  \mathcal{O}_{6D}=\frac{1}{\Lambda^2} \overline{L_i} \tilde{H} \nu_R S^2\,,
+  \mathcal{O}_{6D}=\frac{1}{\Lambda^2} \overline{L} \tilde{H} \nu_R S^2\,,
 \end{align}
@@
 expectation value (VEV),  a set of three singlet fermions,
-$\nu_{Ri}$ ($i=1,2$) and $\nu_{R3}$, and another set of three heavy Majorana fermions, $\psi_{R\alpha}$ ($\alpha=1,2,3$).  
+$\nu_{Rj}$ ($j=1,2$) and $\nu_{R3}$, and another set of three heavy Majorana fermions, $\psi_{R\alpha}$ ($\alpha=1,2,3$).  
 %The model also includes an additional $\operatorname{U}(1)_X$ gauge
@@
 %
-where $L_{i}$ and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
+where $L_{i}$ ($i=1,2,3$) and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
 The scalar potential can be cast as
@@
 
-On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
+On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha}v_S=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
 %\begin{pmatrix}
@@
 
-\section{Neutrinos}
+\section{Neutrino masses and charged lepton flavor violation}
 \label{sec:Neutrinos}
@@
 \includegraphics[scale=0.75]{Neutrino_Loop.pdf}
-\caption{One-loop generation of Dirac neutrino mass}
+\caption{One-loop realization of the dimension-6 operator $\overline{L} \tilde{H} \nu_R S^2$ leading to Dirac neutrino masses with Majorana mediators.}
 \label{fig:zee}
@@
 %
- The Dirac neutrino mass matrix in this model is generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by
+Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}.
+The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
 %
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S^2 v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
+%(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} %{m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} %M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( %\frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( %\frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
 \end{align}
@@
 %check the following formula:
-where $F(x) =x \log x/(x-1)$. 
+where $F(x) =x \log x/(x-1)$ and $M_{\psi_\alpha}=\kappa_{\alpha}v_S$ has been used once. 
 %, $M_{\psi_{a}}$ is
@@
 %two CP-even (CP-odd) mass eigenstates.
-It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 v_S \neq 0$. In this
-way, in addition to the suppression from the seesaw mechanism, we can
-have further suppression in the neutrino mass matrix for small values
-of $\mu$.
-The structure of the effective neutrino mass matrix is given by the
-product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to
+%It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 %v_S \neq 0$. 
+Note that the structure of the effective neutrino mass matrix, given by the
+product $(M_{\nu})_{ij} \propto h_{i \alpha} y_{j\alpha}$, is similar to
 the structure of the neutrino mass matrix for the tree-level seesaw
 mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. 
+It is also worth mentioning that if only one
+fermion $\psi_R$ is added, then there will be two massless neutrinos, which
+would be ruled out by the current neutrino oscillation data~\cite{deSalas:2017kay}. 
+In our case, we assume the
+existence of three of such fermions, generating Dirac scotogenic masses for
+the two left-handed neutrinos ($\nu_{3}=\nu_{L3}+\nu_{R3}$ is massless due to the charge assignment).
 
-If only one
-fermion $\psi_R$ is added, we will have two massless neutrinos, which
-does not agree with the current data obtained from the neutrino
-experiments~\cite{deSalas:2017kay}. In our case, we will assume the
-existence of three fermions, generating Dirac scotogenic masses for
-the two neutrinos ($\nu_{k}$ is massless due to the assignment of
-charges).
-If we consider the case in which $m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$ and $\lambda_7$, $\lambda_2$, $\lambda_4 \ll 1$.
-Taking $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m_{\eta^{\pm}}^{2}$ one finds
+In order to estimate the possible values for the parameters involved in the neutrino masses we consider the case where $\lambda_2$, $\lambda_4$, $\lambda_7 \ll 1$ and $m_\chi^2\equiv m_{\eta^{\pm}}^2 = \mu^2_{\sigma} \gg \frac{1}{2} \lambda_8 v v_S$, which leads to $a\approx b\gg c$.
+Taking into account that for the mentioned case $m^2_{\chi_{R_{2}}}-m^2_{\chi_{R_{1}}} = \lambda_8 v v_{S}$ and $m^2_{\chi_{R_{2}}}+m^2_{\chi_{R_{1}}} = 2 m^2_\chi$, we have that
 %
 \begin{align*}
-(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{a}}y^{*}_{j\alpha}} {m_{\eta^{\pm}}^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_{\eta^{\pm}}^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\eta^{\pm}}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S^2 v}{32 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
 \end{align*}
 %
-and if we take $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$ one has 
+and by furhter assuming $m_{\chi}^{2} \gg (\kappa_\alpha v_S)^2$ one finds 
 %
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\eta^{\pm}}^{2}}\,, \\
-& \sim 0.003~\text{eV} \left( \frac{\lambda_8}{1 \text{GeV}}\right) \left( \frac{v_{S}}{10 \text{TeV}}\right) \left( \frac{M_{\psi_{a}}}{1 \text{TeV}}\right) \left( \frac{50 \text{TeV}}{m_{\eta^{\pm}}}\right)^{2} \left( \frac{h_{i a} y_{a j}^{\dagger}}{10^{-6}}\right)\,.
+(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S^2 v}{32 \pi^{2}m_{\chi}^{2}} \sum_{\alpha=1}^{3} h_{i \alpha} \kappa_{\alpha}y^{*}_{j\alpha}\,, \\
+& \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right)^2 \left( \frac{\kappa_\alpha}{0.5}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,.
 \nonumber
@@
 %
-The mass matrix for Dirac neutrinos is diagonalized by
-\begin{align*}
-(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = \text{diag}(m_1, m_2, m_3)\,,
-\end{align*}
-where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are unitary $3 \times 3$
-matrices. The leptonic charged currents with non-massless neutrinos
-are parametrized in terms of the unitary mass
-\begin{align*}
-U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
-\end{align*}
-where is the left diagonalization matrix of the charged leptons.
-As we already are in the diagonal basis after the calculation of the
-one-loop neutrino masses, we can set
-$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
-Therefore, we can express the Dirac neutrino mass matrix in the
-following way
-\begin{align}
-(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
-\end{align}
-where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
-\begin{align*}
-U_{\text{PMNS}} = \begin{pmatrix}
-    1 & 0		& 0 \\
-    0 & c_{23}  & s_{23} \\
-    0 & -s_{23} & c_{23}
-\end{pmatrix}
-\begin{pmatrix}
-    c_{13}  &  0 & s_{13}e^{-i\delta} \\
-    0 		&  1 & 0 \\
-    -s_{13}e^{i\delta} &  0 & c_{13}
-\end{pmatrix}
-\begin{pmatrix}
-    c_{12}  & s_{12} & 0 \\
-    -s_{12} & c_{12} & 0 \\
-    0		& 0		 & 1
-\end{pmatrix}\,,
-\end{align*}
-where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are neutrino mixing angles and $\delta$ is CP-violating phase.
+In this way, in addition to the loop suppression it is possible to 
+have further suppression in the neutrino mass matrix for small values
+of either $v_S$, $\lambda_8$ or $h_{i \alpha} y_{j\alpha}$.
 
-\section{Lepton flavor violation}
-\label{sec:LFV}
+%The mass matrix for Dirac neutrinos is diagonalized by
+%\begin{align*}
+%(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = %\text{diag}(m_1, m_2, m_3)\,,
+%\end{align*}
+%where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are the unitary $3 \times 3$
+%matrices associated to the right-handed and left-handed neutrino sectors. The leptonic %charged currents with non-massless neutrinos
+%are parametrized in terms of the unitary mass
+%\begin{align*}
+%U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
+%\end{align*}
+%where is the left diagonalization matrix of the charged leptons.
+%As we already are in the diagonal basis after the calculation of the
+%one-loop neutrino masses, we can set
+%$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
+%Therefore, we can express the Dirac neutrino mass matrix in the
+%following way
+%\begin{align}
+%(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
+%\end{align}
+%where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
+%\begin{align*}
+%U_{\text{PMNS}} = \begin{pmatrix}
+%    1 & 0		& 0 \\
+%    0 & c_{23}  & s_{23} \\
+%    0 & -s_{23} & c_{23}
+%\end{pmatrix}
+%\begin{pmatrix}
+%    c_{13}  &  0 & s_{13}e^{-i\delta} \\
+%    0 		&  1 & 0 \\
+%    -s_{13}e^{i\delta} &  0 & c_{13}
+%\end{pmatrix}
+%\begin{pmatrix}
+%    c_{12}  & s_{12} & 0 \\
+%    -s_{12} & c_{12} & 0 \\
+%    0		& 0		 & 1
+%\end{pmatrix}\,,
+%\end{align*}
+%where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are %neutrino mixing angles and $\delta$ is CP-violating phase.
+
+%\section{Lepton flavor violation}
+%\label{sec:LFV}
 %
@@
 %
-The new Yukawa interactions in eq.~\eqref{eq:LagY} in our model introduce processes of charged lepton flavor violation (CLFV).
-These CLFV processes are induced at one loop level, as shown in the fig.~\ref{fig:LFV}.
-In this case, the $\overline{L} \tilde{\eta} \psi_R$ interaction allows the part of the double scalar $\eta$ ($\eta^{\pm}$) to mediate in the loop.
+On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$) as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type.
+current experimental constraint on Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn} and for the case $m_\chi^2=m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$
+ we obtain an upper bound for the Yukawa couplings product (for a given $m_\chi$)
+\begin{align}
+    \left| \sum_{\alpha}h_{i \alpha} h_{j\alpha}^{*} \right| \lesssim 0.02 \left(\frac{m_\chi}{2\,\text{TeV}} \right)^{2}.
+\end{align}
+It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of LFV processes. 
+%
+%which leads to a very slight requirement,
 
-The most common search for CLFV focuses on the $l^{-}_{i} \to l^{-}_{j} \gamma$ process. This process is described by the effective Lagrangian
+%The most common search for CLFV focuses on the $l^{-}_{i} \to l^{-}_{j} \gamma$ process. This process is described by the effective Lagrangian
 %
-\begin{align}
-    \mathcal{L} = \frac{\mu_{m}^{\alpha \beta}}{2} l^{-}_{\beta} \sigma^{\mu \nu} l^{-}_{\alpha} F_{\mu \nu}
-\end{align}
+%\begin{align}
+%    \mathcal{L} = \frac{\mu_{m}^{\alpha \beta}}{2} l^{-}_{\beta} \sigma^{\mu \nu} l^{-}_{\alpha} F_{\mu \nu}
+%\end{align}
 %
-where $\mu_{m}^{\alpha \beta}$ is a transition magnetic moment~\cite{Toma:2013zsa}.
-The decay rate is given by~\cite{Lavoura:2003xp}
+%where $\mu_{m}^{\alpha \beta}$ is a transition magnetic moment~\cite{Toma:2013zsa}.
+%The decay rate is given by~\cite{Lavoura:2003xp}
 %
-\begin{align}
- \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
-\end{align}
+%\begin{align}
+% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
+%\end{align}
 %
-where $t_{\alpha} = M^{2}_{\psi_{\alpha}}/M^{2}_{\eta^{-}}$ and
+%where $t_{\alpha} = M^{2}_{\psi_{\alpha}}/M^{2}_{\eta^{-}}$ and
 %
-\begin{align}
-    K(t_{\alpha}) = \frac{2t_{\alpha}^{2}+5t_{\alpha}-1}{12(t_{\alpha}-1)^{3}} - \frac{t_{\alpha}^{2}\log t_{\alpha}}{2(t_{\alpha}-1)^{4}}\,.
-\end{align}
+%\begin{align}
+%    K(t_{\alpha}) = \frac{2t_{\alpha}^{2}+5t_{\alpha}-1}{12(t_{\alpha}-1)^{3}} - %\frac{t_{\alpha}^{2}\log t_{\alpha}}{2(t_{\alpha}-1)^{4}}\,.
+%\end{align}
 %
-If we assume that $t_{\alpha} \to 0$, $t_{\alpha} \to 1$ and $t_{\alpha} \to \infty$, we have that $K(t_{\alpha}) = 1/12$, $K(t_{\alpha}) = 1/24$ and $K(t_{\alpha}) = 1/(6t)$, respectively.
+%If we assume that $t_{\alpha} \to 0$, $t_{\alpha} \to 1$ and $t_{\alpha} \to \infty$, we have that $K(t_{\alpha}) = 1/12$, $K(t_{\alpha}) = 1/24$ and $K(t_{\alpha}) = 1/(6t)$, respectively.
 
-For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
+%For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
 The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
@@
 
-In the limit $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$, $t_{\alpha} \to 0$ the decay width reads
+%In the limit $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$, $t_{\alpha} \to 0$ the decay width reads
 %
-\begin{align}
- \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,, 
-\end{align}
+%\begin{align}
+% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,, 
+%\end{align}
 %
-using the current experimental constraint to Br$(\mu \to e\gamma)$, can be fullfilled provided
+%using the current experimental constraint to Br$(\mu \to e\gamma)$, can be fullfilled provided
 %
-\begin{align*}
-    \left( \sum_{\alpha} \frac{h^{}_{i \alpha} h_{\alpha j}^{*}}{M^{2}_{\eta^{-}}} \right)^{2} \leq 5.7 \times 10^{-13} \frac{768 \pi G_{F}^{2}}{\alpha_{EM}}
-\end{align*}
+%\begin{align*}
+%    \left( \sum_{\alpha} \frac{h^{}_{i \alpha} h_{\alpha j}^{*}}{M^{2}_{\eta^{-}}} \right)^{2} \leq 5.7 \times 10^{-13} \frac{768 \pi G_{F}^{2}}{\alpha_{EM}}
+%\end{align*}
 %
-which leads to a very slight requirement,
-\begin{align*}
-    \left| \sum_{\alpha}h^{}_{i \alpha} h_{\alpha j}^{*}\left(\frac{50\text{TeV}}{M^{2}_{\eta^{-}}} \right)^{2} \right| \leq 12.65
-\end{align*}
+%which leads to a very slight requirement,
+%\begin{align*}
+%    \left| \sum_{\alpha}h^{}_{i \alpha} h_{\alpha j}^{*}\left(\frac{50\text{TeV}}{M^{2}_{\eta^{-}}} \right)^{2} \right| \leq 12.65
+%\end{align*}
 %
-For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment.
+%For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment.
 In the case of the anomalous muon magnetic dipole moment, the experimental measurements does not agree with the values predicted by the SM~\cite{Lindner:2016bgg}.
@@
 \label{sec:DM}
-From table~\ref{tab:partcont}. we can see that after the spontaneous breaking of
-$\operatorname{U}(1)_X$ there is remnant $Z_2$ symmetry under which the particles circulating the loop in fig.~\ref{fig:zee}.
-plus $\nu_{R3}$ are odd, while the other right handed neutrinos and the SM particles are even.
-The lightest odd particle can be a dark matter candidate.
-In this way we can have either fermionic or scalar dark matter in the model.
+From the charge assignment presented in Table~\ref{tab:partcont} we have that a residuar $Z_2$ symmetry is left over after the $\operatorname{U}(1)_X$ symmetry breaking, with the particles circulating the one-loop neutrino mass diagram  (see Fig.~\ref{fig:zee}) and $\nu_{R3}$ being odd under it whereas $\nu_{R1}, \nu_{R2}$ and and all the SM particles are even.
+Thus the lightest neutral $Z_2$-odd particle can be a dark matter candidate.
+In other words, this model features either fermion ($\psi_1$) or scalar ($\chi_{1R}$ or $\chi_{1I}$) dark matter\footnote{Note that $Z'$ is not stable because the $Z'\to\bar{\nu}_{R3}\nu_{R3}$ decay channel can not be kinematically closed.}.
 
-\subsection{Fermionic dark matter}
-The relic density of DM is controlled by the $Z'$ portal~\footnote{For
-  a recent review of Majorana Dark matter with a $Z'$ portal
-  see~\cite{Blanco:2019hah} } and
+\subsection{Fermion dark matter}
+Since $\psi_{R1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
+The scenario where $\psi_{R1}$ is self annihilating through $h_{i\alpha}$ interaction resembles the very well known scotogenic model \cite{Ma:2006km} whereas for dominant gauge interactions we have the  Majorana Dark matter with a $Z'$ portal.
+
+%$Z'$ portal~\footnote{For a recent review of Majorana Dark matter with a $Z'$ portal see~\cite{Blanco:2019hah} }
 % check Ibarra papers
-also through the annihilation
-$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via
-Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
-CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
-In the case where the mass of the other fermions and scalars is nearly
-degenerated to $\psi_{1} $, the processes of coannihilation can be
-relevant for the relic density calculation~\cite{Klasen:2013jpa}.
+%also through the annihilation
+%$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via
+%Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
+%CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
+%In the case where the mass of the other fermions and scalars is nearly
+%degenerated to $\psi_{1} $, the processes of coannihilation can be
+%relevant for the relic density calculation~\cite{Klasen:2013jpa}.
 
-Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.
+%   Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.
 
@@
 this model~\cite{}, the relevant coupling for DM phenomenology is the
-Higgs portal trough the Lagrangian term $\sigma^{2} H^{2}_{i}$.
+Higgs portal trough the Lagrangian
+
+ term $\sigma^{2} H^{2}_{i}$.
 This term generates interesting phenomenological consequences.
@@
 \label{sec:CosmoConstraints}
+A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc,Okada:2018tgy}.
+We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
+The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
+\begin{align}
+  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
+\end{align}
+The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos.
+For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
+\begin{align}
+  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
+\end{align}
+There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
+\begin{align}
+  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
+  \label{Eq:SMCharges}
+\end{align}
+The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
+
+For this kind of solutions we have that
+\begin{align}
+  \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
+\end{align}
+
+We are interested here in the case of the exotic set of $X$-charges
+charges: $\mp 4$,~$\mp 4$,~$\pm 5$, that when assigned to the
+three light right-handed neutrinos can forbid three level Dirac and
+Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
+Abelian gauge groups $X=B-L,B,D,G$ defined in~\cite{Campos:2017dgc}.
+The presence of a set of heavy Majorana mediators to realize the
+dimension-5 operator at one-loop with the diagram in
+fig.~\ref{fig:ld5}., would spoil the anomaly cancellation conditions.
+However, we can further add an extra set of quiral fermion in a
+vector-like way, such that the full set heavy fermions do not affect
+the anomaly cancellation. A such assignment is displayed in
+Table~\ref{tab:partcont2}.
+The fields $\xi_{L \alpha}$ guarantee the anomaly cancellation and
+their Majorana masses are obtained in the same way than the ones for
+$\psi_{R\alpha}$.
+
+In this way we end up with a model with four Majorana fermions, two more than in the minimal solution.
+Alternatively we can have a single set of $\psi_R$ and $\xi_L$ but two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk}.
+If we choose $r$ as a fraction with denominator $4$, let say $r=3/4$, the $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
+
+The two additional left-handed fields $\xi_{L\alpha}$,  with a $\operatorname{U}(1)_{B-L}$ charge of $r=3/4$,  cancel out the anomalies.
+Moreover, we have both Dirac mass terms $\overline{\xi_{L \alpha}}\psi_{R \beta}$ and $ \overline{\xi_{L\alpha}^c }\xi_{L \beta} \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
+The lighter of them a would be dark matter candidate.
+
+%the charges for the SM particles are in equations~\ref{Eq:SMCharges}. Since these are determined by the anomaly cancellation equations.
+%For this operator we have that the charges for the new particles are given by
+%\begin{align}
+%    \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
+%\end{align}
+%As we are interested here in the case of the exotic set of X-charges charges:$\mp 4$,$\mp 4$,$\pm 5$, the charges for the model particles are shown in the table~\ref{tab:partcont3}.
+%Because the charges of the SM fermions are the same for both operators ($5d$ and $6d$), the $N_{eff}$ restrictions shown in the figure~\ref{fig:Neff} apply to both operators.
+%
+\begin{table}
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|c|c|}
+    \hline  
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_B$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
+$L $  & $\boldsymbol{2}$& $-1/2$  &  $l$&  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
+$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1+2l/3$&  $1/3$&    $1$&  $0$&  $2/3$ \\
+$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
+$Q $  & $\boldsymbol{2}$& $-1/6$  &  $-l/3$& $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
+$e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
+$H $  & $\boldsymbol{2}$& $-1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
+$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/4-l$& $7/4$& $3/4$ &$9/4$&$5/4$ \\
+$S$ & $\boldsymbol{1}$ & $0$  & $3/2$& $3/2$&  $3/2$ & $3/2$& $3/2$ \\
+$\sigma$ & $\boldsymbol{1}$ & $0$ & $13/4$& $13/4$&  $13/4$ & $13/4$& $13/4$ \\
+\hline
+ $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
+$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $+5$&  $5$ & $5$& $5$\\
+$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/4$ & $3/4$&  $3/4$ & $3/4$& $3/4$ \\\hline
+$\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/4$& $3/4$ &  $3/4$ & $3/4$& $3/4$\\\hline
+  \end{tabular}
+  \caption{The new scalars and fermions with their respective charges for the 6-dimensional operator. The SM fields have the usual $U(1)_{B-L}$ assignment. Now $\alpha=1,2$}
+    \label{tab:partcont3}
+\end{table}
+%
+
+% \footnote{Check 2r+2nu: -2,6,7,-9,-3  3r+2nu: -(5/2),7/2,-7,6,9/2}
+
+The coupling of $Z'$ with the lepton doublets opens up the possibility
+of thermalization of the right handed neutrinos in the primordial
+plasma.
+In fact, the existence of three new right neutrinos in nature
+contribute to the total energy density of the universe. These new
+contributions can modify the cosmological observables in the cosmic
+microwave background (CMB). These new neutrinos contribute to the
+existence of dark radiation, which affects the expansion processes of
+the universe and the number of relativistic degrees of freedom for
+neutrinos.
+
+In the case of our model, the new gauge symmetry introduces  new gauge boson that mediates interaction of the right neutrinos and the SM.
+This allows the right neutrinos to thermally modify the relativistic degrees of freedom with contributions given by~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
+%
+\begin{align*}
+    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
+\end{align*}
+%
+where $N_{\nu_R}$ is the neutrino number with same charges and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
+The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}.
+The rate of interaction of the right neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
+%
+\begin{align*}
+    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \,, \\
+    &= \frac{g^{2}_{\nu_R}}{n_{\nu_R}(T)} \int \frac{d^{3} p}{(2 \pi)^{3}} f_{\nu_R}(p) \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k) \sigma_{f}(s) \upsilon\,,
+\end{align*}
+%
+where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$ is the spin number, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, where $p$ and $k$ are the momenta of the particle and $\theta$, the angle between them, and the number density of right-handed neutrinos is given by
+\begin{align*}
+n_{\nu_R}(T) = g_{\nu_R} \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k)\,.
+\end{align*}
+
+The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is
+%
+\begin{align*}
+    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
+\end{align*}
+%
+where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e.
+$N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson.
+Solving the integrals with this last cross section we obtain that the interaction rate is given by
+%
+\begin{align*}
+    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
+\end{align*}
+%
+where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$.
+To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$).
+The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
+%
+\begin{align*}
+\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
+\end{align*}
+% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,
+
+where the Hubble expansion parameter is
+% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,
+
+\begin{align*}
+    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
+\end{align*}
+%
+where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom.
+By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
+
+The results of $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}.
+We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
+The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
+For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$ for all the symmetries studied here.
+
+%
+\begin{figure}
+\centering
+\includegraphics[scale=0.8]{D_Neff.pdf}
+\caption{Contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
+The region above the gray line is excluded by the measurements in the Planck~\cite{Aghanim:2018eyx}.
+The horizontal dashed lines show the sensitivity of future experiments, SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
+}
+\label{fig:Neff}
+\end{figure}
+
+Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
+
+\section{Discussion and summary}
+
+\appendix
+
+\section{General solution}
+
+The general solution to fig.~\ref{fig:zee} is
+\begin{align}
+  L=&\nu_R+4\psi_R -H \,,& \eta=& H-\nu_R-3\psi_R \nonumber\\
+  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
+\end{align}
+The consistency condition for $H=0$ is
+\begin{align}
+  L=\nu_R+4\psi_R\,.
+\end{align}
+
+On the other hand, for fig.~\ref{fig:ld5}
+\begin{align}
+  L=&-H+\nu_R+2\psi_R &
+  \eta=&H-\nu_R-\psi_R \nonumber\\
+  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
+\end{align}
+$\nu_R$, $H$  and $L$ are fixed from the anomaly cancellation conditions.
+
+\section{5d model}
+\label{sec:5dmodel}
 A not-so-minimal model can be obtained as the one-loop realization of
@@
   u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
+  \label{Eq:SMCharges}
 \end{align}
@@
 
-The coupling of $Z'$ with the lepton doublets opens up the possibility
-of thermalization of the right handed neutrinos in the primordial
-plasma.
-In fact, the existence of three new right neutrinos in nature
-contribute to the total energy density of the universe. These new
-contributions can modify the cosmological observables in the cosmic
-microwave background (CMB). These new neutrinos contribute to the
-existence of dark radiation, which affects the expansion processes of
-the universe and the number of relativistic degrees of freedom for
-neutrinos.
-
-In the case of our model, the new gauge symmetry introduces  new gauge boson that mediates interaction of the right neutrinos and the SM.
-This allows the right neutrinos to thermally modify the relativistic degrees of freedom with contributions given by~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
-%
-\begin{align*}
-    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
-\end{align*}
-%
-where $N_{\nu_R}$ is the neutrino number with same charges and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
-The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}.
-The rate of interaction of the right neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
-%
-\begin{align*}
-    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \,, \\
-    &= \frac{g^{2}_{\nu_R}}{n_{\nu_R}(T)} \int \frac{d^{3} p}{(2 \pi)^{3}} f_{\nu_R}(p) \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k) \sigma_{f}(s) \upsilon\,,
-\end{align*}
-%
-where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$ is the spin number, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, where $p$ and $k$ are the momenta of the particle and $\theta$, the angle between them, and the number density of right-handed neutrinos is given by
-\begin{align*}
-n_{\nu_R}(T) = g_{\nu_R} \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k)\,.
-\end{align*}
-
-The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is
-%
-\begin{align*}
-    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
-\end{align*}
-%
-where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e.
-$N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson.
-Solving the integrals with this last cross section we obtain that the interaction rate is given by
-%
-\begin{align*}
-    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
-\end{align*}
-%
-where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$.
-To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$).
-The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
-%
-\begin{align*}
-\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
-\end{align*}
-% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,
-
-where the Hubble expansion parameter is
-% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,,
-
-\begin{align*}
-    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
-\end{align*}
-%
-and the $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom.
-By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
-
-The results of $T^{\nu_R}_{\text{dec}}$ and $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}.
-We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
-The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
-For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$ for all the symmetries studied here.
-
-%
-\begin{figure}
-\centering
-\includegraphics[scale=0.8]{D_Neff.pdf}
-\caption{Contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
-The region above the gray line is excluded by the measurements in the Planck~\cite{Aghanim:2018eyx}.
-The horizontal dashed lines show the sensitivity of future experiments, SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
-}
-\label{fig:Neff}
-\end{figure}
-
-Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
-
-\appendix
-
-\section{General solution}
-
-The general solution to fig.~\ref{fig:zee} is
-\begin{align}
-  L=&\nu_R+4\psi_R -H \,,& \eta=& H-\nu_R-3\psi_R \nonumber\\
-  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
-\end{align}
-The consistency condition for $H=0$ is
-\begin{align}
-  L=\nu_R+4\psi_R\,.
-\end{align}
-
-On the other hand, for fig.~\ref{fig:ld5}
-\begin{align}
-  L=&-H+\nu_R+2\psi_R &
-  \eta=&H-\nu_R-\psi_R \nonumber\\
-  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
-\end{align}
-$\nu_R$, $H$  and $L$ are fixed from the anomaly cancellation conditions.
-
 %\bibliographystyle{h-physrev4}

### 2019-09-11 draft.tex
Updates from Overleaf

@@
 
-\subsection{Fermion dark matter}
+%\subsection{Fermion dark matter}
 Since $\psi_{R1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
-The scenario where $\psi_{R1}$ is self annihilating through $h_{i\alpha}$ interaction resembles the very well known scotogenic model \cite{Ma:2006km} whereas for dominant gauge interactions we have the  Majorana Dark matter with a $Z'$ portal.
-
-%$Z'$ portal~\footnote{For a recent review of Majorana Dark matter with a $Z'$ portal see~\cite{Blanco:2019hah} }
+The scenario where $\psi_{1}$ self-annihilates dominantly through $h_{i\alpha}$-mediated interactions resembles the very well known scotogenic model \cite{Ma:2006km}. 
+In this case sizable $h_{i\alpha}$ are required to reproduce the correct DM abundance, which in turn leads to a mild tension with experimental upper bounds on the rates for rare charged lepton decays.
+The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm}.
+On the other hand, when the $Z'$ portal is the main gate to visible sector, $\psi_1$ largely annihilates  into neutrinos (see~\cite{Blanco:2019hah} for a recent review on $Z'$-mediated Majorana DM).
 % check Ibarra papers
@@
 
-\subsection{Scalar dark matter}
+%\subsection{Scalar dark matter}
 Contrary to fermionic DM, scalar DM has additional interactions beyond the Yukawa couplings  which can be used to control relic density.
@@
 density is around the Higgs resonance and for masses above $1$TeV. For
-this model~\cite{}, the relevant coupling for DM phenomenology is the
+this model~\cite{}, the relevant c
+
+oupling for DM phenomenology is the
 Higgs portal trough the Lagrangian
@@
 A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc,Okada:2018tgy}.
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
@@
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_B$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
 $L $  & $\boldsymbol{2}$& $-1/2$  &  $l$&  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
@@
 $e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
-$H $  & $\boldsymbol{2}$& $-1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
+$H $  & $\boldsymbol{2}$& $1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
 $\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/4-l$& $7/4$& $3/4$ &$9/4$&$5/4$ \\
@@
 $e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
-$H $  & $\boldsymbol{2}$& $-1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
+$H $  & $\boldsymbol{2}$& $1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
 $\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/2-l$& $5/2$& $3/2$ &$3$&$2$ \\

### 2019-09-11 draft.tex
sf

@@
 where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$.
-To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right neutrinos ($T^{\nu_R}_{\text{dec}}$).
+To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right-handed neutrinos ($T^{\nu_R}_{\text{dec}}$).
 The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
@@
 % \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
-
+%
 where the Hubble expansion parameter is
 % \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
-
+%
 \begin{align*}
@@
 The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
-For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{eff}$ for all the symmetries studied here.
+For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
 

### 2019-09-14 draft.tex
Updates from Overleaf

@@
 A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
@@
 Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
-Abelian gauge groups $X=B-L,B,D,G$ defined in~\cite{Campos:2017dgc}.
+Abelian gauge groups $X=B-L,R,D,G$ defined in~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}}.
 The presence of a set of heavy Majorana mediators to realize the

### 2019-09-14 draft.tex
Updates from Overleaf

@@
 \label{sec:DM}
-From the charge assignment presented in Table~\ref{tab:partcont} we have that a residuar $Z_2$ symmetry is left over after the $\operatorname{U}(1)_X$ symmetry breaking, with the particles circulating the one-loop neutrino mass diagram  (see Fig.~\ref{fig:zee}) and $\nu_{R3}$ being odd under it whereas $\nu_{R1}, \nu_{R2}$ and and all the SM particles are even.
-Thus the lightest neutral $Z_2$-odd particle can be a dark matter candidate.
-In other words, this model features either fermion ($\psi_1$) or scalar ($\chi_{1R}$ or $\chi_{1I}$) dark matter\footnote{Note that $Z'$ is not stable because the $Z'\to\bar{\nu}_{R3}\nu_{R3}$ decay channel can not be kinematically closed.}.
+From the model charge assignment in Table~\ref{tab:partcont} we have that a residual $Z_2$ symmetry is left over after the $\operatorname{U}(1)_X$ symmetry breaking, with the particles circulating the one-loop neutrino mass diagram  (see Fig.~\ref{fig:zee}) and $\nu_{R3}$ being odd under it whereas $\nu_{R1}, \nu_{R2}$ and all the SM particles trivially transforming.
+Thus the lightest electrically-neutral $Z_2$-odd particle becomes a dark matter candidate.
+In other words, this model also provides a solution to the DM puzzle via either fermion ($\psi_1$) or scalar ($\chi_{1R}$ or $\chi_{1I}$) dark matter\footnote{Note that $Z'$ can not constitute a DM candidate due to the instability associated to the $Z'\to\bar{\nu}_{R3}\nu_{R3}$ decay channel, since it can not be kinematically closed.}.
 
 %\subsection{Fermion dark matter}
-Since $\psi_{R1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
-The scenario where $\psi_{1}$ self-annihilates dominantly through $h_{i\alpha}$-mediated interactions resembles the very well known scotogenic model \cite{Ma:2006km}. 
-In this case sizable $h_{i\alpha}$ are required to reproduce the correct DM abundance, which in turn leads to a mild tension with experimental upper bounds on the rates for rare charged lepton decays.
-The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm}.
-On the other hand, when the $Z'$ portal is the main gate to visible sector, $\psi_1$ largely annihilates  into neutrinos (see~\cite{Blanco:2019hah} for a recent review on $Z'$-mediated Majorana DM). 
+Since $\psi_{1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
+The scenario where $\psi_{1}$ self-annihilates dominantly through $h_{i\alpha}$-mediated interactions resembles the very well known scotogenic model \cite{Ma:2006km},  
+where sizable $h_{i\alpha}$ are required to reproduce the correct DM abundance, which in turn leads to a mild tension with experimental upper bounds on the rates for rare charged lepton decays~\cite{Kubo:2006yx,Sierra:2008wj,Ibarra:2016dlb}.
+%The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
+On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Dudas:2009uq} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks neither to charged leptons)
+(see~\cite{Dudas:2009uq,Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for related phenomenological studies on $Z'$-mediated Majorana DM). 
 % check Ibarra papers
@@
 %\subsection{Scalar dark matter}
-Contrary to fermionic DM, scalar DM has additional interactions beyond the Yukawa couplings  which can be used to control relic density.
-This corresponds to the simplified dark matter model of scalar singlet-doblet dark matter, which have been studied in detail in~\cite{Restrepo:2019soi}
+In contrast to fermion DM, the scalar DM candidate has additional interaction terms to the Yukawa and gauge interactions.
+This entails that the later ones can be used to alter the relic density predictions in scenarios with mixed scalar DM.
+Since in the present model the CP-even and CP-odd neutral $Z_2$-odd particles are mass degenerate, we have the scenario of singlet-doublet complex DM~\cite{Kadastik:2009dj,Belanger:2012vp} where the DM candidate is a mixture of a complex singlet \cite{McDonald:1993ex} and a $SU(2)_L$ doublet \cite{Deshpande:1977rw,Barbieri:2006dq}.
+It follows that for negligible Yukawa and gauge interactions there are two DM mass regions that allow us to properly reproduce the relic abundance, one corresponds the Higgs funnel region and the second one lies above $100$ GeV~\cite{Kakizaki:2016dza}.
 
-When the lightest scalar  is mainly a scalar doublet, the phenomenology will be similar inert doublet model~\cite{Honorez:2010re}.
+%This corresponds to the simplified dark matter model of scalar singlet-doublet dark matter, which have been studied in detail in~\cite{Restrepo:2019soi}
+
+%When the lightest scalar  is mainly a scalar doublet, the phenomenology will be similar inert doublet model~\cite{Honorez:2010re}.
 For this kind of DM model  inert doublet model there are two mass regions for DM which can to reproduce adequately the relic density ($50$GeV \textless $m_{DM}$ \textless $70$GeV and $535$GeV \textless $m_{DM}$ \textless $20$TeV)~\cite{Garcia-Cely:2015khw}.
@@
 
-Now, if the lightest scalar is mainly a singlet, the DM will be
-similar to Singlet Scalar Dark Matter
-Model~\cite{Athron:2017kgt}\todo{change for the original ref by Ma et
-  al. etc}.
-The mass range for the scalar singlet that produces the adequate relic
-density is around the Higgs resonance and for masses above $1$TeV. For
-this model~\cite{}, the relevant c
-
-oupling for DM phenomenology is the
-Higgs portal trough the Lagrangian
-
- term $\sigma^{2} H^{2}_{i}$.
-This term generates interesting phenomenological consequences.
-Such as, thermal production of DM in the early
-universe~\cite{Yaguna:2008hd}, direct detection and invisible decay of
-SM Higgs through $h \to \sigma \sigma$~\cite{Mambrini:2011ik}.
-In addition, this model has important contributions for cosmology, in
-phenomena such as inflation~\cite{Lerner:2009xg} and
-baryogenesis~\cite{Cline:2012hg}.
+%Now, if the lightest scalar is mainly a singlet, the DM will be similar to Singlet %Scalar Dark Matter Model~\cite{Athron:2017kgt}\todo{change for the original ref by Ma et al. etc}.
+%The mass range for the scalar singlet that produces the adequate relic
+%density is around the Higgs resonance and for masses above $1$TeV. For
+%this model~\cite{}, the relevant coupling for DM phenomenology is the
+%Higgs portal trough the Lagrangian term $\sigma^{2} H^{2}_{i}$.
+%This term generates interesting phenomenological consequences.
+%Such as, thermal production of DM in the early
+%universe~\cite{Yaguna:2008hd}, direct detection and invisible decay of
+%SM Higgs through $h \to \sigma \sigma$~\cite{Mambrini:2011ik}.
+%In addition, this model has important contributions for cosmology, in
+%phenomena such as inflation~\cite{Lerner:2009xg} and
+%baryogenesis~\cite{Cline:2012hg}.
 
@@
 A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
@@
 
+\section{Collider constraints}
+ATLAS~\cite{}
+recasting~\cite{}
+In fig.~\ref{fig:u1blc}...
+
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.8]{u1blc}
+    \caption{Constraints in the $\operatorname{U}(1)_{B-L}$ model.}
+    \label{fig:u1blc}
+\end{figure}
+
+In the $\operatorname{U}(1)_{B-L}$, cosmlogical constraints are better that current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$
+
 \section{Discussion and summary}
@@
 \appendix
-
-\section{General solution}
-
-The general solution to fig.~\ref{fig:zee} is
-\begin{align}
-  L=&\nu_R+4\psi_R -H \,,& \eta=& H-\nu_R-3\psi_R \nonumber\\
-  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
-\end{align}
-The consistency condition for $H=0$ is
-\begin{align}
-  L=\nu_R+4\psi_R\,.
-\end{align}
-
-On the other hand, for fig.~\ref{fig:ld5}
-\begin{align}
-  L=&-H+\nu_R+2\psi_R &
-  \eta=&H-\nu_R-\psi_R \nonumber\\
-  \sigma=& -\nu_R-\psi_R\,,&S=& 2\psi_R \,.
-\end{align}
-$\nu_R$, $H$  and $L$ are fixed from the anomaly cancellation conditions.
-
-\section{5d model}
-\label{sec:5dmodel}
-A not-so-minimal model can be obtained as the one-loop realization of
-the effective 5-dimensional operator for Dirac neutrino masses~\cite{Gu:2006dc}
-\begin{align}
-  \label{eq:ld5}
-  \mathcal{L}_{5D}=\frac{1}{\Lambda} \overline{L_i} H \nu_R S\,,
-\end{align}
-as displayed in fig.~\ref{fig:ld5}.
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Campos:2017dgc,Okada:2018tgy}.
-We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
-The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
-\begin{align}
-  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
-\end{align}
-The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos.
-For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
-\begin{align}
-  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
-\end{align}
-There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
-\begin{align}
-  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
-  \label{Eq:SMCharges}
-\end{align}
-The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
-
-For this kind of solutions we have that
-\begin{align}
-  \psi=&-\frac{\nu+1}{2}\,,&\eta=&-\frac{\nu+1}{2}-l\,,&\sigma=&\frac{1-\nu}{2}\,.
-\end{align}
-
-We are interested here in the case of the exotic set of $X$-charges
-charges: $\mp 4$,~$\mp 4$,~$\pm 5$, that when assigned to the
-three light right-handed neutrinos can forbid three level Dirac and
-Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
-Abelian gauge groups $X=B-L,B,D,G$ defined in~\cite{Campos:2017dgc}.
-The presence of a set of heavy Majorana mediators to realize the
-dimension-5 operator at one-loop with the diagram in
-fig.~\ref{fig:ld5}., would spoil the anomaly cancellation conditions.
-However, we can further add an extra set of quiral fermion in a
-vector-like way, such that the full set heavy fermions do not affect
-the anomaly cancellation. A such assignment is displayed in
-Table~\ref{tab:partcont2}.
-The fields $\xi_{L \alpha}$ guarantee the anomaly cancellation and
-their Majorana masses are obtained in the same way than the ones for
-$\psi_{R\alpha}$.
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.75]{Neutrino2.pdf}
-\caption{One-loop realization of the dimension-5 effective Dirac neutrino mass operator }
-\label{fig:ld5}
-\end{figure}
-%
-
-\begin{table}
-  \centering
-  \begin{tabular}{|c|c|c|c|c|c|c|c|}
-    \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_B$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
-$L $  & $\boldsymbol{2}$& $-1/2$  &  $l$&  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
-$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1+2l/3$&  $1/3$&    $1$&  $0$&  $2/3$ \\
-$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
-$Q $  & $\boldsymbol{2}$& $-1/6$  &  $-l/3$& $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
-$e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
-$H $  & $\boldsymbol{2}$& $1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
-$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/2-l$& $5/2$& $3/2$ &$3$&$2$ \\
-$S$ & $\boldsymbol{1}$ & $0$  & $3$& $3$&  $3$ & $3$& $3$ \\
-$\sigma$ & $\boldsymbol{1}$ & $0$ & $5/2$& $5/2$&  $5/2$ & $5/2$& $5/2$ \\
-\hline
- $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
-$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $+5$&  $5$ & $5$& $5$\\
-$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/2$ & $3/2$&  $3/2$ & $3/2$& $3/2$ \\\hline
-$\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/2$& $3/2$ &  $3/2$ & $3/2$& $3/2$\\\hline
-  \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. The SM fields have the usual $U(1)_{B-L}$ assignment. Now $\alpha=1,2$}
-    \label{tab:partcont2}
-\end{table}
-
-In this way we end up with a model with four Majorana fermions, two more than in the minimal solution.
-Alternatively we can have a single set of $\psi_R$ and $\xi_L$ but two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk}.
-If we choose $r$ as a fraction with denominator $2$, let say $r=3/2$, the $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
-
-The two additional left-handed fields $\xi_{L\alpha}$,  with a $\operatorname{U}(1)_{B-L}$ charge of $r=3/2$,  cancel out the anomalies.
-Moreover, we have both Dirac mass terms $\overline{\xi_{L \alpha}}\psi_{R \beta}$ and $ \overline{\xi_{L\alpha}^c }\xi_{L \beta} \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
-The lighter of them a would be dark matter candidate.
-
-% \footnote{Check 2r+2nu: -2,6,7,-9,-3  3r+2nu: -(5/2),7/2,-7,6,9/2}
 

### 2019-09-14 draft.tex
wrong caption

@@
 %
-\begin{align*}
+\begin{align}
 \label{eq:LagY}
-    \mathcal{L} \supset& -[ 
-    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^* \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^* + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,,
-\end{align*}
+    \mathcal{L} \supset& -\,g_{X}\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g_{X}\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
+    &-[ 
+    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^* \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^* + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,.
+\end{align}
 %
-where $L_{i}$ ($i=1,2,3$) and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
+In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ and $\phi$ denote the new chiral fermions and new scalars respectively, and $q_{F,\,\phi}$ their $X$ charges.
+In the second row
+$L_{i}$ ($i=1,2,3$) and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 
 The scalar potential can be cast as
@@
 \centering
-\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
+\includegraphics[scale=0.6]{Neutrino_Loop.pdf}
 \caption{One-loop realization of the dimension-6 operator $\overline{L} \tilde{H} \nu_R S^2$ leading to Dirac neutrino masses with Majorana mediators.}
@@
 %\label{sec:LFV}
-%
-\begin{figure}
-\centering
-\includegraphics[scale=0.75]{LFV.pdf}
-\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
-\label{fig:LFV}
-\end{figure}
-%
+
 On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$) as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type.
@@
 It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of LFV processes.
+
+%
+\begin{figure}[t]
+\centering
+\includegraphics[scale=0.6]{LFV.pdf}
+\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
+\label{fig:LFV}
+\end{figure}
+%
+
 %
@@
 %The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
-On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Dudas:2009uq} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks neither to charged leptons)
-(see~\cite{Dudas:2009uq,Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for related phenomenological studies on $Z'$-mediated Majorana DM). 
+On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks neither to charged leptons)
+(see~\cite{Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for phenomenological studies on $Z'$-mediated Majorana DM). 
 % check Ibarra papers
@@
 Since in the present model the CP-even and CP-odd neutral $Z_2$-odd particles are mass degenerate, we have the scenario of singlet-doublet complex DM~\cite{Kadastik:2009dj,Belanger:2012vp} where the DM candidate is a mixture of a complex singlet \cite{McDonald:1993ex} and a $SU(2)_L$ doublet \cite{Deshpande:1977rw,Barbieri:2006dq}.
-It follows that for negligible Yukawa and gauge interactions there are two DM mass regions that allow us to properly reproduce the relic abundance, one corresponds the Higgs funnel region and the second one lies above $100$ GeV~\cite{Kakizaki:2016dza}.
+It follows that for negligible Yukawa and gauge interactions there are two DM mass regions that allow us to properly reproduce the relic abundance, one corresponds the Higgs funnel region and the second one demands masses above $100$ GeV~\cite{Kakizaki:2016dza}.
 
@@
 
-\section{Cosmological constraints}
+\section{Beyond the minimal model: cosmological constraints}
 \label{sec:CosmoConstraints}
@@
     Fields     & $\operatorname{SU}(2)_L$ &  $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
-$L $  & $\boldsymbol{2}$& $-1/2$  &  $l$&  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
-$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1+2l/3$&  $1/3$&    $1$&  $0$&  $2/3$ \\
-$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
-$Q $  & $\boldsymbol{2}$& $-1/6$  &  $-l/3$& $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
-$e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
-$H $  & $\boldsymbol{2}$& $1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
-$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/4-l$& $7/4$& $3/4$ &$9/4$&$5/4$ \\
-$S$ & $\boldsymbol{1}$ & $0$  & $3/2$& $3/2$&  $3/2$ & $3/2$& $3/2$ \\
-$\sigma$ & $\boldsymbol{1}$ & $0$ & $13/4$& $13/4$&  $13/4$ & $13/4$& $13/4$ \\
-\hline
- $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
-$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $+5$&  $5$ & $5$& $5$\\
+$L $     & $\boldsymbol{2}$ & $-1/2$ & $l$      &  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
+$d_R $   & $\boldsymbol{1}$ & $-1/2$ & $1+2l/3$ &  $1/3$&    $1$&  $0$&  $2/3$ \\
+$u_R $   & $\boldsymbol{1}$ & $+2/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
+$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
+$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ \\
+$H $     & $\boldsymbol{2}$ & $1/2$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
+$\eta$   & $\boldsymbol{2}$ & $+1/2$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ \\
+$S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ \\
+$\sigma$ & $\boldsymbol{1}$ & $0$    & $13/4$   & $13/4$&  $13/4$ & $13/4$& $13/4$ \\\hline
+$\nu_{Ri}$& $\boldsymbol{1}$ & $0$   & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
+$\nu_{R3}$& $\boldsymbol{1}$ & $0$   & $+5$& $+5$&  $5$ & $5$& $5$\\
 $\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/4$ & $3/4$&  $3/4$ & $3/4$& $3/4$ \\\hline
@@
 \section{Collider constraints}
-ATLAS~\cite{}
-recasting~\cite{}
-In fig.~\ref{fig:u1blc}...
+The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{1903.06248} was done
+in~\cite{1903.06248} for the $\operatorname{U}(1)_{B-L}$ model.
+The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$.
+To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
+In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{1408.6845},
+\begin{align}
+  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }
+\end{align}
+
+which is obtained from the search for effective four-lepton operators and valid for $M_{Z'}\gg 200\ \text{GeV}$.
+This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, is shown in the excluded magenta region.
 
@@
 
-In the $\operatorname{U}(1)_{B-L}$, cosmlogical constraints are better that current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$
+The constraint of $\Delta N_{\text{eff}}$ for $\operatorname{U}(1)_{B-L}$ is shown in the blue region and start to be better that current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$.
+Similar restrictions can be obtained for other values for the other models quoted in fig.~\ref{fig:Neff}.
 

### 2019-09-14 draft.tex
lc

--- 2019-09-14 draft.tex
@@
 \section{Collider constraints}
-The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{1903.06248} was done
-in~\cite{1903.06248} for the $\operatorname{U}(1)_{B-L}$ model.
+The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
+in~\cite{Aad:2019fac} for the $\operatorname{U}(1)_{B-L}$ model.
 The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$.
 To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
-In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{1408.6845},
+In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa},
 \begin{align}

### 2019-09-14 draft.tex
Updates from Overleaf

@@
 
-The most general Lagrangian contains the following Yukawa and scalar interactions:
+The most general Lagrangian contains the following gauge, Yukawa and scalar interactions:
 %
@@
 %
-In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ and $\phi$ denote the new chiral fermions and new scalars respectively, and $q_{F,\,\phi}$ their $X$ charges.
+In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
 In the second row
@@
 %
-\begin{align*}
-    \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \\
-    &+  \lambda_{1} (H^{\dagger} H ) (S^{*} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{*} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\\
-    &+ \lambda_{4} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{5} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \\
+\begin{align}
+    \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \nonumber\\
+    &+  \lambda_{1} (H^{\dagger} H ) (S^{*} S) + \lambda_{2} (H^{\dagger} H ) (\sigma^{*} \sigma ) + \lambda_{3} (H^{\dagger} H ) (\eta^{\dagger} \eta )\nonumber\\
+    &+ \lambda_{4} (S^{*} S) (\sigma^{*} \sigma ) + \lambda_{5} (S^{*} S) (\eta^{\dagger} \eta ) + \lambda_{6} (\eta^{\dagger} \eta ) (\sigma^{*} \sigma ) + \lambda_{7} (\eta^{\dagger} H ) (H^{\dagger} \eta ) \nonumber\\
     &+ \lambda_{8} (\eta^{\dagger} H S^{*} \sigma + \text{h.c.})\,,
-\end{align*}
+\end{align}
 %
@@
 \label{sec:CosmoConstraints}
+\ref{eq:LagY}
+It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{eff}.
+
 A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 

### 2019-09-15 draft.tex
fix

@@
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_X$ \\ \hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{\mathcal{D}}$ \\ \hline
     % $H $  & 2  1/2  &  0 \\
@@
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. }
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{\mathcal{D}}$ gauge symmetry. }
     \label{tab:partcont}
@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry.
+Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{1807.09877}.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level
@@
 \ref{eq:LagY}
-It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{eff}.
+It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$.
+These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ chargesin our model .
+However, since they do not couple directly to any SM particles, we can simply assume that their interaction with the extra gauge boson and scalars are sufficiently suppressed that they  decouple early enough from the thermal bath.
 

### 2019-09-15 draft.tex
Updates from Overleaf

@@
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{\mathcal{D}}$ \\ \hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_X$ \\ \hline
     % $H $  & 2  1/2  &  0 \\
@@
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{\mathcal{D}}$ gauge symmetry. }
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the new $\operatorname{U}(1)_X$ gauge symmetry. }
     \label{tab:partcont}
@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{1807.09877}.
+Only the new particles including the light right handed neutrinos are charged under this symmetry.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level

### 2019-09-15 draft.tex
Updates from Overleaf

@@
 It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$.
-These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ chargesin our model .
+These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ charges of $\nu_R$'s in our model .
 However, since they do not couple directly to any SM particles, we can simply assume that their interaction with the extra gauge boson and scalars are sufficiently suppressed that they  decouple early enough from the thermal bath.

### 2019-09-15 draft.tex
fix

@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{1807.09877}.
+Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Bertuzzo:2018itn}.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level

### 2019-09-15 draft.tex
Updates from Overleaf

--- 2019-09-15 draft.tex
@@
 It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$.
-These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ charges of $\nu_R$'s in our model .
+These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ charges of $\nu_R$'s.
 However, since they do not couple directly to any SM particles, we can simply assume that their interaction with the extra gauge boson and scalars are sufficiently suppressed that they  decouple early enough from the thermal bath.

### 2019-09-15 draft.tex
lc

--- 2019-09-15 draft.tex
@@
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{\mathcal{D}}$ \\ \hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{N}$ \\ \hline
     % $H $  & 2  1/2  &  0 \\
@@
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{\mathcal{D}}$ gauge symmetry. }
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{N}$ gauge symmetry. }
     \label{tab:partcont}
@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{1807.09877}.
+Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level
@@
 \label{sec:CosmoConstraints}
-\ref{eq:LagY}
 It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$.
-These contributions, which arise from the presence of the new light states $\nu_R$'s, are expected to be sizeable due to the large $X$ charges of $\nu_R$'s.
-However, since they do not couple directly to any SM particles, we can simply assume that their interaction with the extra gauge boson and scalars are sufficiently suppressed that they  decouple early enough from the thermal bath.
+In this model, these contributions arise from the presence of the right-handed neutrinos and may be expected to be sizeable precisely due to the large $X$ charges of the $\nu_R$'s.
+Nevertheless, since those and the $Z'$ do not couple directly to the rest of the SM particles (see Eq.~(\ref{eq:LagY}))  they  decouple early enough from the thermal bath and, therefore, not altering $N_{\text{eff}}$.
 
@@
 In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
+The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.

### 2019-09-15 draft.tex
Updates from Overleaf

@@
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{N}$ \\ \hline
+    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{\mathcal{D}}$ \\ \hline
     % $H $  & 2  1/2  &  0 \\
@@
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{N}$ gauge symmetry. }
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{\mathcal{D}}$ gauge symmetry. }
     \label{tab:partcont}
@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
+Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Bertuzzo:2018itn}.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level
@@
 In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
-The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.

### 2019-09-15 draft.tex
Updates from Overleaf

--- 2019-09-15 draft.tex
@@
 In this model, these contributions arise from the presence of the right-handed neutrinos and may be expected to be sizeable precisely due to the large $X$ charges of the $\nu_R$'s.
-Nevertheless, since those and the $Z'$ do not couple directly to the rest of the SM particles (see Eq.~(\ref{eq:LagY}))  they  decouple early enough from the thermal bath and, therefore, not altering $N_{\text{eff}}$.
+Nevertheless, since the right-handed neutrinos do not couple directly to the rest of the SM particles (see Eq.~(\ref{eq:LagY}))  they  decouple early enough from the thermal bath and, therefore, do not modify the SM prediction for $N_{\text{eff}}$.
 

### 2019-09-15 draft.tex
lc

@@
 The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
-in~\cite{Aad:2019fac} for the $\operatorname{U}(1)_{B-L}$ model.
+in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
 The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$.

### 2019-09-15 draft.tex
lc

@@
 We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
-The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Alioli:2017nzr}.
+% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
 For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
@@
 in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
-The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$.
-To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
+The green (upper) region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
 In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa},
 \begin{align}
-  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }
+  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
 \end{align}
-
 which is obtained from the search for effective four-lepton operators and valid for $M_{Z'}\gg 200\ \text{GeV}$.
-This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, is shown in the excluded magenta region.
+This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, and is shown in the excluded magenta (lower) region of Fig.~\ref{fig:u1blc}.
 
@@
 
-The constraint of $\Delta N_{\text{eff}}$ for $\operatorname{U}(1)_{B-L}$ is shown in the blue region and start to be better that current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$.
-Similar restrictions can be obtained for other values for the other models quoted in fig.~\ref{fig:Neff}.
+The constraint of $\Delta N_{\text{eff}}$ for $\operatorname{U}(1)_{B-L}$ is shown in the blue (middle) region and start to be better than current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$.
+Similar restrictions can be obtained for the other models quoted in fig.~\ref{fig:Neff}.
 

### 2019-09-15 draft.tex
lc

@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
+Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn,1808.02500}.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level
@@
 In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
-The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
+The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn,1808.02500}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.

### 2019-09-15 draft.tex
lc

--- 2019-09-15 draft.tex
@@
 We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
+Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 We choose the new particle set such that the following dimension six operator is realized at one-loop level
@@
 In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
-The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn}.
+The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.

### 2019-09-15 draft.tex
lc

@@
 in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
-The green (upper) region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
+The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
 In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa},
@@
 \end{align}
-which is obtained from the search for effective four-lepton operators and valid for $M_{Z'}\gg 200\ \text{GeV}$.
-This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, and is shown in the excluded magenta (lower) region of Fig.~\ref{fig:u1blc}.
+which is obtained from the search for effective four-lepton operators and is valid for $M_{Z'}\gg 200\ \text{GeV}$.
+This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, and corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc}.
 

### 2019-09-16 draft.tex
Updates from Overleaf

@@
 \label{eq:LagY}
-    \mathcal{L} \supset& -\,g_{X}\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g_{X}\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
+    \mathcal{L} \supset& -\,g'\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g'\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
     &-[ 
@@
 %
-In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
+In the first row $g'$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
 In the second row
@@
 On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha}v_S=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
+Finally, the mass of the new gauge boson is given by $M_{Z'}=q_Sg'v_S$.
 %\begin{pmatrix}
@@
 \label{sec:CosmoConstraints}
-It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$.
+It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$~\cite{Dolgov:2002wy}.
 In this model, these contributions arise from the presence of the right-handed neutrinos and may be expected to be sizeable precisely due to the large $X$ charges of the $\nu_R$'s.
@@
 
-A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
-The previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
-We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
-The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
-\begin{align}
-  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
-\end{align}
-The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos.
-For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
-\begin{align}
-  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
-\end{align}
-There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
-\begin{align}
-  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
-  \label{Eq:SMCharges}
-\end{align}
-The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
+With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing additional chiral SM singlet fields and assigning nonzero $\operatorname{U}(1)_X$ charges to the SM fields.
+%A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
+In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)}_X$ in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 
-For this kind of solutions we have that
-\begin{align}
-  \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
-\end{align}
+Since we are interested here in keeping the exotic set of $X$-charges
+charges $\{\mp 4$,~$\mp 4$,~$\pm 5\}$ in such a way that when assigned to the right-handed neutrinos the tree level Dirac and
+Majorana masses can be forbidden~\cite{Calle:2018ovc}, 
+it follows that this set is compatible with the
+Abelian gauge groups $X=B-L,R,D,G,$ defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}} as long as the set of Majorana mediators $\psi_{R\alpha}$ that  realize the
+dimension-6 operator at one-loop have vanishing $X$-charges. Otherwise, the anomaly cancellation conditions would be spoiled.
+In view of that $\psi_{R\alpha}$ have necessarily nonzero $X$-charges (see the Appendix), we further add an extra set of chiral fermions in 
+such a way the full set heavy fermions  do not affect
+the anomaly cancellation (their charges cancel each other in a vector like way). 
+The resulting charge assignment is displayed in
+Table~\ref{tab:partcont3}, where 
+the fields $\xi_{L \alpha}$ constitute the new set of chiral fermion that guarantee the anomaly cancellation.
+%\footnote{Their Majorana masses are obtained in the same way than the ones for $\psi_{R\alpha}$.}.
+In this way we end up with a model with four Majorana fermions, two more than in the minimal solution, since third generation of chiral fermions is not needed to cancel the $\operatorname{U(1)}_X$ anomaly (alternatively we may consider another simple setup by adding a single set of $\psi_R$ and $\xi_L$ and two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk})\footnote{
+%On the other hand, 
+Seeing that the two additional left-handed fields $\xi_{L\alpha}$,  with a $X$-charge $r=3/4$,  have both Dirac and Majorana mass terms $\overline{\xi_{L \alpha}}\psi_{R \beta}$ and $ \overline{\xi_{L\alpha}^c }\xi_{L \beta} \langle S\rangle$, the full set of Majorana fields are massive and heavy.
+Moreover, because the $\operatorname{U}(1)_{X}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest $Z_2$-odd particle,  we have that the lightest of these Majorana fields may play the role of DM candidate.}.
 
-We are interested here in the case of the exotic set of $X$-charges
-charges: $\mp 4$,~$\mp 4$,~$\pm 5$, that when assigned to the
-three light right-handed neutrinos can forbid three level Dirac and
-Majorana masses~\cite{Calle:2018ovc}. This set is compatible with the
-Abelian gauge groups $X=B-L,R,D,G$ defined in~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}}.
-The presence of a set of heavy Majorana mediators to realize the
-dimension-5 operator at one-loop with the diagram in
-fig.~\ref{fig:ld5}., would spoil the anomaly cancellation conditions.
-However, we can further add an extra set of quiral fermion in a
-vector-like way, such that the full set heavy fermions do not affect
-the anomaly cancellation. A such assignment is displayed in
-Table~\ref{tab:partcont2}.
-The fields $\xi_{L \alpha}$ guarantee the anomaly cancellation and
-their Majorana masses are obtained in the same way than the ones for
-$\psi_{R\alpha}$.
-
-In this way we end up with a model with four Majorana fermions, two more than in the minimal solution.
-Alternatively we can have a single set of $\psi_R$ and $\xi_L$ but two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk}.
-If we choose $r$ as a fraction with denominator $4$, let say $r=3/4$, the $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
-
-The two additional left-handed fields $\xi_{L\alpha}$,  with a $\operatorname{U}(1)_{B-L}$ charge of $r=3/4$,  cancel out the anomalies.
-Moreover, we have both Dirac mass terms $\overline{\xi_{L \alpha}}\psi_{R \beta}$ and $ \overline{\xi_{L\alpha}^c }\xi_{L \beta} \langle S\rangle$ and the full set of Majorana fields are massive and heavy.
-The lighter of them a would be dark matter candidate.
+%Note that if $r$ is a fraction with denominator $4$, let say $r=3/4$, 
+%The $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
 
@@
 $u_R $   & $\boldsymbol{1}$ & $+2/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
-$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
-$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ \\
+$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ \\
+$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ \\\hline
 $H $     & $\boldsymbol{2}$ & $1/2$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
@@
 
-The coupling of $Z'$ with the lepton doublets opens up the possibility
-of thermalization of the right handed neutrinos in the primordial
-plasma.
-In fact, the existence of three new right neutrinos in nature
-contribute to the total energy density of the universe. These new
-contributions can modify the cosmological observables in the cosmic
-microwave background (CMB). These new neutrinos contribute to the
-existence of dark radiation, which affects the expansion processes of
-the universe and the number of relativistic degrees of freedom for
-neutrinos.
-
-In the case of our model, the new gauge symmetry introduces  new gauge boson that mediates interaction of the right neutrinos and the SM.
-This allows the right neutrinos to thermally modify the relativistic degrees of freedom with contributions given by~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
+Accordingly, we may expect that 
+the three right neutrinos within the not-so minimal model
+contribute to the radiation energy density of the Universe, since now   the interaction between the $Z'$ with the SM fermions  opens up the possibility to thermalize them with the primordial plasma.
+%These new contributions can modify the cosmological observables in the cosmic microwave background (CMB). 
+%These new neutrinos contribute to the
+%existence of dark radiation, which affects the expansion processes of
+%the universe and the number of relativistic degrees of freedom for
+%neutrinos.
+%In the case of our model, the new gauge symmetry introduces  new gauge boson that mediates interaction of the right neutrinos and the SM. 
+In other words, this leads to a modification in the relativistic degrees of freedom as~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
 %
@@
 where $N_{\nu_R}$ is the neutrino number with same charges and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
-The decoupling temperature of the left neutrinos $\nu_L$ is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV~\cite{Enqvist:1991gx}, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4 $ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq}.
+The decoupling temperature of the SM neutrinos is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4$ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq,Enqvist:1991gx}.
 The rate of interaction of the right neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
@@
 %
-where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$ is the spin number, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, where $p$ and $k$ are the momenta of the particle and $\theta$, the angle between them, and the number density of right-handed neutrinos is given by
+where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, $p$ and $k$ are the momenta of the particle with $\theta$ the angle between them, and the number density of right-handed neutrinos is given by
 \begin{align*}
@@
 \end{align*}
-
-The cross section is given in~\cite{Barger:2003zh}, in the case with heavy mediator $T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$, we can to take the limit when $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses, we have that the cross section is
+The cross section for the case of a heavy mediator ($T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$), with $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses in the final state is given by~\cite{Barger:2003zh}
 %
 \begin{align*}
-    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} Q^{2}_{\nu_R} (Q^{2}_{f_L} + Q^{2}_{f_R})\,,
+    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} q^{2}_{\nu_R} (q^{2}_{f_L} + q^{2}_{f_R})\,,
 \end{align*}
 %
-where $N^{C}_{f}$ is the color multiplicity of the fermion, i.e.
-$N^{C}_{q(\ell)} = 3(1)$, $Q_{f}$ is the charge of the fermion under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson.
-Solving the integrals with this last cross section we obtain that the interaction rate is given by
+where $N^{C}_{f}=1(3)$ for leptons (quarks),
+%is the color multiplicity of the fermion, i.e. $N^{C}_{q(\ell)} = 3(1)$,
+and $q_{f}$ is the $X$-charge of the SM fermion.  
+%under the new symmetry, $g^{\prime}$ and $M_{Z^{\prime}}$ are the gauge coupling and mass for the new gauge boson. 
+%Solving the integrals with this last cross section we obtain that the interaction rate is given by
+Accordingly the interaction rate takes the form
 %
 \begin{align*}
-    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} Q^{2}_{f}\,,
+    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} q^{2}_{f}\,.
 \end{align*}
 %
-where the sum is performed over all SM fermion that are in thermal equilibrium with the plasma at temperature $T$.
-To estimate the contribution to the relativistic degrees of freedom for neutrinos, it is necessary to calculate the decoupling temperature of the right-handed neutrinos ($T^{\nu_R}_{\text{dec}}$).
-The latter occurs when the interaction rate of neutrinos with the SM drop below the rate of expansion of the universe, i.e.
+In this expression the sum is performed over all SM fermions that are in thermal equilibrium with the plasma at temperature $T$.
+To estimate the contribution to the relativistic degrees of freedom from right-handed neutrinos, it is necessary to calculate the decoupling temperature of the right-handed neutrinos ($T^{\nu_R}_{\text{dec}}$).
+The latter occurs when the interaction rate $\Gamma_{\nu_{R}}(T)$ drops below the rate of expansion of the Universe, $\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, $
 %
-\begin{align*}
-\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
-\end{align*}
+%\begin{align*}
+%\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
+%\end{align*}
+%
 % \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
 %
-where the Hubble expansion parameter is
+with $H(T)= [4 \pi^{3} G_{N}(g(T) + 21/4)/45]^{1/2} T^{2}\,.$
 % \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
 %
-\begin{align*}
-    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 \pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
-\end{align*}
+%\begin{align*}
+%    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 %\pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
+%\end{align*}
 %
-where $21/4$ correspond to the contribution of the right neutrinos to relativistic degrees of freedom.
-By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
+Note that the factor $21/4$ corresponds to the contribution of the right-handed neutrinos to the relativistic degrees of freedom. 
+%By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
 
-The results of $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are exhibited in fig.~\ref{fig:Neff}.
+The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
 We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
@@
 \centering
-\includegraphics[scale=0.8]{D_Neff.pdf}
-\caption{Contribution to the number of relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
-The region above the gray line is excluded by the measurements in the Planck~\cite{Aghanim:2018eyx}.
-The horizontal dashed lines show the sensitivity of future experiments, SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
+\includegraphics[scale=1.2]{D_Neff.pdf}
+\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
+The region above the gray line is excluded by the measurements at $2\sigma$ from PLANCK~\cite{Aghanim:2018eyx}.
+The horizontal dashed lines show the projected sensitivity of the future experiments SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
 }
@@
 \appendix
+\section{Anomaly cancellation}
+We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
+The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
+\begin{align}
+  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
+\end{align}
+The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos.
+For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
+\begin{align}
+  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
+\end{align}
+There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
+\begin{align}
+  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
+  \label{Eq:SMCharges}
+\end{align}
+The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
+
+For this kind of solutions we have that
+\begin{align}
+  \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
+\end{align}
 

### 2019-09-16 draft.tex
Updates from Overleaf

@@
 The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
-We can see that for small decoupling temperatures, the variation in the number of relativistic degrees of freedom of the new species is large and vice versa.
+It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
 % The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
-For our model we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$TeV in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
+It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV.
+%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
+On the other hand, it is remarkable the fact the future CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} have the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
 
@@
 
-Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
+%Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
 

### 2019-09-16 draft.tex
mc

@@
 %Conclusion:
-In this work we propose a radiative Dirac type-I seesaw, with Majorana
-fermions as mediators in the loop. This full set of mediators in the
+In this work we propose a radiative Dirac type-I seesaw with Majorana
+fermions as mediators in the loop, where the full set of mediators in the
 loop can include a DM candidate.
@@
 In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
-In section~\ref{sec:LFV} we show the lepton flavor violation (LFV) experimental  constraints.
+In section~\ref{sec:LFV} we show the lepton flavor violation experimental  constraints.
 In section~\ref{sec:DM} we present the viable DM candidates.
-Finally, In section~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{eff}$) in a nonminimum model for different extra abelian symmetries.
+Finally, In section~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{\text{eff}}$) in a nonminimum model for different extra abelian symmetries.
 
@@
 %
-We extend the standard model with a spontaneously broken Abelian gauge symmetry  which guarantees the total lepton number ($L$) conservation.
-Only the new particles including the light right handed neutrinos are charged under this symmetry, and hence corresponds to a dark symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
-We choose the new particle set such that the following dimension six operator is realized at one-loop level
+We extend the standard model with a spontaneously broken Abelian gauge
+symmetry which guarantees the total lepton number ($L$)
+conservation. Only the new particles, including the light right-handed
+neutrinos, are charged under this new
+$\operatorname{U}(1)_{\mathcal{D}}$ dark gauge
+symmetry~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf} to obtain an anomaly free theory. We
+choose the new particle set such that the following dimension six
+operator is realized at one-loop level
 \begin{align}
@@
 %Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $\operatorname{SU}(2)_L$.
-The $\operatorname{U}(1)_X$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
+The $\operatorname{U}(1)_{\mathcal{D}}$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
 %In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.
 
-The most general Lagrangian contains the following gauge, Yukawa and scalar interactions:
+The most general Lagrangian for some gauge $\operatorname{U}(1)_X$ symmetry, which includes $X=\mathcal{D}$, contains the following gauge, Yukawa and scalar interactions:
 %
@@
 %
-Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}.
-The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
+%Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac
+Neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
 %
@@
 
-On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$) as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type.
-current experimental constraint on Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn} and for the case $m_\chi^2=m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$
- we obtain an upper bound for the Yukawa couplings product (for a given $m_\chi$)
+On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$ as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type.
+By using the current experimental constraint on $\operatorname{Br}(\mu \to e\gamma)<5.7 \times 10^{-13} $~\cite{Adam:2013mnn} and for the case $m_\chi^2=m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$
+ we can obtain an upper bound for the product of Yukawa couplings
 \begin{align}
@@
 \end{align}
-It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of LFV processes.
+It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of CLFV processes.
 
@@
 \label{sec:DM}
-From the model charge assignment in Table~\ref{tab:partcont} we have that a residual $Z_2$ symmetry is left over after the $\operatorname{U}(1)_X$ symmetry breaking, with the particles circulating the one-loop neutrino mass diagram  (see Fig.~\ref{fig:zee}) and $\nu_{R3}$ being odd under it whereas $\nu_{R1}, \nu_{R2}$ and all the SM particles trivially transforming.
-Thus the lightest electrically-neutral $Z_2$-odd particle becomes a dark matter candidate.
-In other words, this model also provides a solution to the DM puzzle via either fermion ($\psi_1$) or scalar ($\chi_{1R}$ or $\chi_{1I}$) dark matter\footnote{Note that $Z'$ can not constitute a DM candidate due to the instability associated to the $Z'\to\bar{\nu}_{R3}\nu_{R3}$ decay channel, since it can not be kinematically closed.}.
+From the model charge assignment in Table~\ref{tab:partcont} we have
+that a residual $Z_2$ symmetry is left over after the
+$\operatorname{U}(1)_{\mathcal{D}}$ symmetry breaking, with the
+particles circulating the one-loop neutrino mass diagram (see
+Fig.~\ref{fig:zee}) and $\nu_{R3}$ being odd under it whereas
+$\nu_{R1}, \nu_{R2}$, $S$ and all the SM particles being even. Thus the lightest electrically-neutral $Z_2$-odd
+particle becomes a dark matter candidate. In other words, this model
+also provides a solution to the DM puzzle via either fermion
+($\psi_1$) or scalar ($\chi_{1R}$ or $\chi_{1I}$) dark
+matter\footnote{Note that $Z'$ cannot constitute a DM candidate due
+  to the instability associated to the $Z'\to\bar{\nu}_{R3}\nu_{R3}$
+  decay channel, which cannot be kinematically closed.}.
 
 %\subsection{Fermion dark matter}
-Since $\psi_{1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
+Since $\psi_{1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa couplings and $\operatorname{U}(1)_{\mathcal{D}}$ gauge interactions. 
 The scenario where $\psi_{1}$ self-annihilates dominantly through $h_{i\alpha}$-mediated interactions resembles the very well known scotogenic model \cite{Ma:2006km},  
@@
 %The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
-On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks neither to charged leptons)
+On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks or charged leptons
 (see~\cite{Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for phenomenological studies on $Z'$-mediated Majorana DM). 

### 2019-09-16 draft.tex
mc

@@
 This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including
-the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
+the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g_D \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
 \end{abstract}
@@
 \label{eq:LagY}
-    \mathcal{L} \supset& -\,g'\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g'\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
+    \mathcal{L} \supset& -\,g_X\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g_X\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
     &-[ 
@@
 %
-In the first row $g'$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
+In the first row $g_X$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
 In the second row
@@
 
-On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha}v_S=\sqrt{2}\kappa_{\alpha\alpha}v_S$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
-Finally, the mass of the new gauge boson is given by $M_{Z'}=q_Sg'v_S$.
+On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha\alpha}v_S/\sqrt{2}$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
+Finally, the mass of the new gauge boson is given by $M_{Z'}=q_Sg_X v_S$.
 %\begin{pmatrix}
@@
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S^2 v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{1}{32 \pi^{2}}  \frac{\lambda_8 v_S v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_\alpha} y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
 %(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} %{m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} %M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( %\frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( %\frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
@@
 %check the following formula:
-where $F(x) =x \log x/(x-1)$ and $M_{\psi_\alpha}=\kappa_{\alpha}v_S$ has been used once. 
+where $F(x) =x \log x/(x-1)$. 
 %, $M_{\psi_{a}}$ is
@@
 \begin{align*}
-(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S^2 v}{32 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
+(\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{\alpha}} y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
 \end{align*}
@@
 \begin{align}
-(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S^2 v}{32 \pi^{2}m_{\chi}^{2}} \sum_{\alpha=1}^{3} h_{i \alpha} \kappa_{\alpha}y^{*}_{j\alpha}\,, \\
-& \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right)^2 \left( \frac{\kappa_\alpha}{0.5}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,.
+(\mathcal{M}_{\nu})_{ij} & = \frac{\lambda_8 v_S v}{16 \pi^{2}m_{\chi}^{2}} \sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_\alpha}y^{*}_{j\alpha}\,, \\
+& \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right) \left( \frac{M_{\psi_\alpha}}{50\,\text{GeV}}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,.
 \nonumber
@@
 %A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)}_X$ in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry corresponds to the fermiophobic setup  $X=N$~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
+In this case we can use the solutions to the anomaly cancellation conditions found for a general  Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,1504.06291,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 
@@
 it follows that this set is compatible with the
-Abelian gauge groups $X=B-L,R,D,G,$ defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}} as long as the set of Majorana mediators $\psi_{R\alpha}$ that  realize the
+Abelian gauge groups $X=B-L,R,D,G,$ defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.} as long as the set of Majorana mediators $\psi_{R\alpha}$ that  realize the
 dimension-6 operator at one-loop have vanishing $X$-charges. Otherwise, the anomaly cancellation conditions would be spoiled.
@@
 %\footnote{Their Majorana masses are obtained in the same way than the ones for $\psi_{R\alpha}$.}.
-In this way we end up with a model with four Majorana fermions, two more than in the minimal solution, since third generation of chiral fermions is not needed to cancel the $\operatorname{U(1)}_X$ anomaly (alternatively we may consider another simple setup by adding a single set of $\psi_R$ and $\xi_L$ and two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk})\footnote{
+In this way we end up with a model with four Majorana fermions, two more than in the minimal solution, since third generation of chiral fermions is not needed to cancel the $\operatorname{U(1)}_X$ anomalies (alternatively we may consider another simple setup by adding a single set of $\psi_R$ and $\xi_L$ and two set of scalars $\eta_\alpha$, $\sigma_{\alpha}$~\cite{Reig:2018mdk})\footnote{
 %On the other hand, 
@@
   \centering
-  \begin{tabular}{|c|c|c|c|c|c|c|c|}
+  \begin{tabular}{|c|c|c|c|c|c|c|c||c|}
     \hline  
-    Fields     & $\operatorname{SU}(2)_L$ &  $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
-$L $     & $\boldsymbol{2}$ & $-1/2$ & $l$      &  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
-$d_R $   & $\boldsymbol{1}$ & $-1/2$ & $1+2l/3$ &  $1/3$&    $1$&  $0$&  $2/3$ \\
-$u_R $   & $\boldsymbol{1}$ & $+2/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
-$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ \\
-$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ \\\hline
-$H $     & $\boldsymbol{2}$ & $1/2$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
-$\eta$   & $\boldsymbol{2}$ & $+1/2$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ \\
-$S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ \\
-$\sigma$ & $\boldsymbol{1}$ & $0$    & $13/4$   & $13/4$&  $13/4$ & $13/4$& $13/4$ \\\hline
-$\nu_{Ri}$& $\boldsymbol{1}$ & $0$   & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
-$\nu_{R3}$& $\boldsymbol{1}$ & $0$   & $+5$& $+5$&  $5$ & $5$& $5$\\
-$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/4$ & $3/4$&  $3/4$ & $3/4$& $3/4$ \\\hline
-$\xi_{L\alpha}$   & $\boldsymbol{1}$ & $0$ & $3/4$& $3/4$ &  $3/4$ & $3/4$& $3/4$\\\hline
+    Fields     & $\operatorname{SU}(2)_L$ &  $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$ & $\operatorname{U}(1)_{\mathcal{D}}$\\ \hline
+$L $     & $\boldsymbol{2}$ & $-1/2$ & $l$      &  $-1$&    $0$ &  $-3/2$&  $-1/2$ & $0$ \\    
+$d_R $   & $\boldsymbol{1}$ & $-1/2$ & $1+2l/3$ &  $1/3$&    $1$&  $0$&    $2/3$ & $0$\\
+$u_R $   & $\boldsymbol{1}$ & $+2/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&   $-1/3$ & $0$ \\
+$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ & $0$ \\
+$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ & $0$\\\hline
+$H $     & $\boldsymbol{2}$ & $1/2$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ & $0$ \\
+$\eta$   & $\boldsymbol{2}$ & $+1/2$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ & $0$ \\
+$S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ & $0$\\
+$\sigma$ & $\boldsymbol{1}$ & $0$    & $13/4$   & $13/4$&  $13/4$ & $13/4$& $13/4$ & $0$\\\hline
+$\nu_{Ri}$& $\boldsymbol{1}$ & $0$   & $-4$& $-4$&  $-4$ & $-4$& $-4$ & $-4$\\
+$\nu_{R3}$& $\boldsymbol{1}$ & $0$   & $+5$& $+5$&  $5$ & $5$& $5$ & $5$\\
+$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/4$ & $3/4$&  $3/4$ & $3/4$& $3/4$ & $1$ \\\hline
+$\xi_{L\alpha}$   & $\boldsymbol{1}$ & $0$ & $3/4$& $3/4$ &  $3/4$ & $3/4$& $3/4$ &$-$\\\hline
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges for the 6-dimensional operator. The SM fields have the usual $U(1)_{B-L}$ assignment. Now $\alpha=1,2$}
+  \caption{The new scalars and fermions with their respective charges for the 6-dimensional operator.
+The SM fields have the usual $U(1)_{B-L}$ assignment.
+Now $\alpha=1,2$.
+The solution in Table~\ref{tab:partcont} is presented in the last column.}
     \label{tab:partcont3}
@@
 Accordingly, we may expect that 
-the three right neutrinos within the not-so minimal model
+the three right-handed neutrinos within the not-so minimal model
 contribute to the radiation energy density of the Universe, since now   the interaction between the $Z'$ with the SM fermions  opens up the possibility to thermalize them with the primordial plasma.
@@
 The decoupling temperature of the SM neutrinos is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4$ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq,Enqvist:1991gx}.
-The rate of interaction of the right neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
+The rate of interaction of the right-handed neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
 %
@@
 \begin{align*}
-    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} q^{2}_{\nu_R} (q^{2}_{f_L} + q^{2}_{f_R})\,,
+    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g_X}{M_{Z^{\prime}}} \right)^{4} q^{2}_{\nu_R} (q^{2}_{f_L} + q^{2}_{f_R})\,,
 \end{align*}
@@
 %Solving the integrals with this last cross section we obtain that the interaction rate is given by
-Accordingly the interaction rate takes the form
+Accordingly, the interaction rate takes the form
 %
 \begin{align*}
-    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} q^{2}_{f}\,.
+    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g_X}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} q^{2}_{f}\,.
 \end{align*}
@@
 \centering
-\includegraphics[scale=1.2]{D_Neff.pdf}
-\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
+\includegraphics[scale=1]{D_Neff.pdf}
+\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g_X$.
 The region above the gray line is excluded by the measurements at $2\sigma$ from PLANCK~\cite{Aghanim:2018eyx}.
@@
 The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
-In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Heeck:2014zfa},
+In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{hep-ph/0408098,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{1611.02672}.
+},
 \begin{align}
@@
 which is obtained from the search for effective four-lepton operators and is valid for $M_{Z'}\gg 200\ \text{GeV}$.
-This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, and corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc}.
+This constraint corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc} and start to be relevant for $M_{Z'}>5.8\ \text{TeV}$.
 
@@
 \section{Anomaly cancellation}
-We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM.
+We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$).
 The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
@@
 The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos.
-For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
+For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
 \begin{align}
-  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
+  \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
 \end{align}
-There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
+There are many known solutions for the case in which $e-2l=1$, including the $N=3$ case $(-4,-4,+5)$~\cite{Appelquist:2002mw}. The full set of standard model charges in terms of $l$ is just
 \begin{align}
@@
 \end{align}
-The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.
+The same solution but in terms of $h$ () given in ~\cite{Jenkins:1987ue,1504.06291}.
 

### 2019-09-16 draft.tex
mc

@@
 %
-and by furhter assuming $m_{\chi}^{2} \gg (\kappa_\alpha v_S)^2$ one finds 
+and by further assuming $m_{\chi}^{2} \gg M_{\psi_{\alpha}}^2$ one finds 
 %
@@
 
-The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
+The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g_X$ are displayed in Fig.~\ref{fig:Neff}.
 It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
 % The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
-It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV.
+It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g_D \gtrsim 60$ TeV.
 %in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.

### 2019-09-16 draft.tex
mc

@@
 %A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for a general  Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,1504.06291,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
+In this case we can use the solutions to the anomaly cancellation conditions found for a general  Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Oda:2015gna,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 
@@
 The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
-In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{hep-ph/0408098,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{1611.02672}.
+In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{Okada:2016tci}.
 },
@@
 \end{align}
-The same solution but in terms of $h$ () given in ~\cite{Jenkins:1987ue,1504.06291}.
+The same solution but in terms of $h$ () given in ~\cite{Jenkins:1987ue,Oda:2015gna}.
 

### 2019-09-17 draft.tex
mc

@@
 It turns that the $Z'$ portal also allows to probe the model through modifications on the cosmological history of the Universe, namely, via additional contributions to the effective number of relativistic degrees of freedom $N_{\text{eff}}$~\cite{Dolgov:2002wy}.
-In this model, these contributions arise from the presence of the right-handed neutrinos and may be expected to be sizeable precisely due to the large $X$ charges of the $\nu_R$'s.
+In this model, these contributions arise from the presence of the right-handed neutrinos and may be expected to be sizeable precisely due to the large $\operatorname{U}(1)_{\mathcal{D}}$~charges of the $\nu_R$'s.
 Nevertheless, since the right-handed neutrinos do not couple directly to the rest of the SM particles (see Eq.~(\ref{eq:LagY}))  they  decouple early enough from the thermal bath and, therefore, do not modify the SM prediction for $N_{\text{eff}}$.
 
-With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing additional chiral SM singlet fields and assigning nonzero $\operatorname{U}(1)_X$ charges to the SM fields.
+With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing a general Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments for the SM fields.
+
+additional chiral SM singlet fields and assigning nonzero $\operatorname{U}(1)_X$ charges to the
 %A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for a general  Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Oda:2015gna,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
+In this case we can use the solutions to the anomaly cancellation conditions found for a general   in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Oda:2015gna,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 
@@
 Abelian gauge groups $X=B-L,R,D,G,$ defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.} as long as the set of Majorana mediators $\psi_{R\alpha}$ that  realize the
-dimension-6 operator at one-loop have vanishing $X$-charges. Otherwise, the anomaly cancellation conditions would be spoiled.
+dimension-6 operator at one-loop have vector-like $X$-charges with a new set of $\psi_{L\alpha}$ fermions. Otherwise, the anomaly cancellation conditions would be spoiled.
 In view of that $\psi_{R\alpha}$ have necessarily nonzero $X$-charges (see the Appendix), we further add an extra set of chiral fermions in 
@@
 \end{align}
-The same solution but in terms of $h$ () given in ~\cite{Jenkins:1987ue,Oda:2015gna}.
+The same solution but in terms of $h$ is given in ~\cite{Jenkins:1987ue,Oda:2015gna}.
 

### 2019-09-17 draft.tex
mc

@@
 With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing a general Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments for the SM fields.
-
-additional chiral SM singlet fields and assigning nonzero $\operatorname{U}(1)_X$ charges to the
-%A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
-In this case we can use the solutions to the anomaly cancellation conditions found for a general   in Refs.~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Oda:2015gna,Okada:2018tgy,Jana:2019mez}, where the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
+Extra chiral fields are required to cancel the anomalies for solutions beyond the one proportional to $\operatorname{U}(1)_Y$.
+In the appendix we show that the solutions to the anomaly cancellation conditions parameterized in terms
+of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc}, can be normalized to depend in just one parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy} that we choose to be the $X$-charge of the lepton doublet as displayed in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
+There, the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
 
 Since we are interested here in keeping the exotic set of $X$-charges
-charges $\{\mp 4$,~$\mp 4$,~$\pm 5\}$ in such a way that when assigned to the right-handed neutrinos the tree level Dirac and
-Majorana masses can be forbidden~\cite{Calle:2018ovc}, 
-it follows that this set is compatible with the
-Abelian gauge groups $X=B-L,R,D,G,$ defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.} as long as the set of Majorana mediators $\psi_{R\alpha}$ that  realize the
-dimension-6 operator at one-loop have vector-like $X$-charges with a new set of $\psi_{L\alpha}$ fermions. Otherwise, the anomaly cancellation conditions would be spoiled.
+charges $\{\mp 4$,~$\mp 4$,~$\pm 5\}$ in such a way that when assigned
+to the right-handed neutrinos the tree level Dirac and Majorana masses
+can be forbidden~\cite{Calle:2018ovc}, the set of Majorana mediators
+$\psi_{R\alpha}$ which realize the dimension-6 operator at one-loop
+have vector-like $X$-charges would spoil the anomaly cancellation
+condition.
 In view of that $\psi_{R\alpha}$ have necessarily nonzero $X$-charges (see the Appendix), we further add an extra set of chiral fermions in 
@@
 Moreover, because the $\operatorname{U}(1)_{X}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest $Z_2$-odd particle,  we have that the lightest of these Majorana fields may play the role of DM candidate.}.
+
+In order to analyse the phenomenology we fix $l$ to recover some already studied
+Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}.
 
@@
 We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$).
-The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
+The three linear anomalies in $\operatorname{U(1)_X}$~\cite{Campos:2017dgc}
+\begin{align}
+  \label{eq:anolin}
+  \left[\mathrm{SU}(3)_{c}\right]^{2} \mathrm{U}(1)_{X} :& &
+[3 u+3 d]-[3 \cdot 2 q]=&0 \nonumber\\
+\left[\mathrm{SU}(2)_{L}\right]^{2} \mathrm{U}(1)_{X} :&&
+-[2 l+3 \cdot 2 q]=&0 \nonumber\\
+\left[\mathrm{U}(1)_{Y}\right]^{2} \mathrm{U}(1)_{X} :&&
+{ \left[(-2)^{2} e+3\left(\tfrac{4}{3}\right)^{2} u+3\left(-\tfrac{2}{3}\right)^{2} d\right]-\left[2(-1)^{2} l+3 \cdot 2\left(\tfrac{1}{3}\right)^{2} q\right]}=&
+ 0
+  \end{align}
+allows to express three $X$-charges in terms of the other two
 \begin{align}
@@
 \begin{align}
-  \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
+  \left[\text{Grav}\right]^{2} \mathrm{U}(1)_{X}:\ \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &  \left[\mathrm{U}(1)_{X}\right]^{3}:\ \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
 \end{align}
-There are many known solutions for the case in which $e-2l=1$, including the $N=3$ case $(-4,-4,+5)$~\cite{Appelquist:2002mw}. The full set of standard model charges in terms of $l$ is just
+We choose the solutions for with $\lambda\equiv e-2l$, such that
 \begin{align}
-  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
+  \label{eq:anolam}
+  \sum_{\alpha=1}^{n} n_{\alpha}=&-3 \lambda\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3 \lambda^3\,, 
+\end{align}
+The full set of standard model charges in terms of $l$ and $\lambda$ is just
+\begin{align}
+  u=&-\lambda-\frac{4l}{3}\,,&d=&\lambda+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&\lambda+2l\,,&h=&-\lambda-l\,.
   \label{Eq:SMCharges}
 \end{align}
-The same solution but in terms of $h$ is given in ~\cite{Jenkins:1987ue,Oda:2015gna}.
+If we now change $f\to  f/\lambda$, such that $\lambda\to 1$, the first of anomaly cancellation~\eqref{eq:anolin} remain invariant, and whithout lost of generality
+always is possible to normalize the solutions such that the last set~\cite{eq:anolam} is just
+\begin{align}
+  \label{eq:anolamnor}
+   \sum_{\alpha=1}^{n} n_{\alpha}=&-3\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3\,.
+\end{align}
+For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} wiht $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{1607.04029}.
+We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
+In particular, this includes the solution  $n_{\alpha}=(-4,-4,+5)$~\cite{Appelquist:2002mw}.
 
-For this kind of solutions we have that
+For this normalized set of solutions we have that
 \begin{align}

### 2019-09-17 draft.tex
mc

@@
 \end{align}
-The full set of standard model charges in terms of $l$ and $\lambda$ is just
+The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we chhose as $l$ and $\lambda$, is just
 \begin{align}
@@
 \end{align}
-For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} wiht $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{1607.04029}.
-We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
+For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} wiht $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}.
+We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
 In particular, this includes the solution  $n_{\alpha}=(-4,-4,+5)$~\cite{Appelquist:2002mw}.

### 2019-09-17 draft.tex
mc

@@
 This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including
-the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g_D \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
+the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
 \end{abstract}
@@
 \label{eq:LagY}
-    \mathcal{L} \supset& -\,g_X\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g_X\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
+    \mathcal{L} \supset& -\,g^{\prime}\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g^{\prime}\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
     &-[ 
@@
 %
-In the first row $g_X$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
+In the first row $g^{\prime}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ ($\phi$) denote the new fermions (scalars), and $q_{F,\,\phi}$ their $X$ charges.
 In the second row
@@
 On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha\alpha}v_S/\sqrt{2}$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
-Finally, the mass of the new gauge boson is given by $M_{Z'}=q_Sg_X v_S$.
+Finally, the mass of the new gauge boson is given by $M_{Z'}=q_Sg^{\prime} v_S$.
 %\begin{pmatrix}
@@
 \begin{align*}
-    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g_X}{M_{Z^{\prime}}} \right)^{4} q^{2}_{\nu_R} (q^{2}_{f_L} + q^{2}_{f_R})\,,
+    \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} q^{2}_{\nu_R} (q^{2}_{f_L} + q^{2}_{f_R})\,,
 \end{align*}
@@
 \begin{align*}
-    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g_X}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} q^{2}_{f}\,.
+    \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} q^{2}_{f}\,.
 \end{align*}
@@
 
-The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g_X$ are displayed in Fig.~\ref{fig:Neff}.
+The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
 It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
 % The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
-It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g_D \gtrsim 60$ TeV.
+It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV.
 %in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
@@
 \includegraphics[scale=1]{D_Neff.pdf}
-\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g_X$.
+\caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
 The region above the gray line is excluded by the measurements at $2\sigma$ from PLANCK~\cite{Aghanim:2018eyx}.
@@
 in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
-The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$.
+The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g^{\prime}$.
 In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{Okada:2016tci}.
@@
 \begin{align}
-  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
+  M_{Z'}/g^{\prime}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }\,,
 \end{align}
@@
 \end{align}
-For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} wiht $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}.
+For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}.
 We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.

### 2019-09-17 draft.tex
mc

@@
 \end{align}
-We choose the solutions for with $\lambda\equiv e-2l$, such that
+We choose the solutions with $\lambda\equiv e-2l$, such that
 \begin{align}
@@
 \end{align}
-The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we chhose as $l$ and $\lambda$, is just
+The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $\lambda$, is just
 \begin{align}
@@
 \end{align}
-If we now change $f\to  f/\lambda$, such that $\lambda\to 1$, the first of anomaly cancellation~\eqref{eq:anolin} remain invariant, and whithout lost of generality
-always is possible to normalize the solutions such that the last set~\cite{eq:anolam} is just
+If we now change $f\to  f/\lambda$, such that $\lambda\to 1$, the first of anomaly cancellation~\eqref{eq:anolin} remain invariant, and without lost of generality
+always is possible to normalize the solutions such that the last set~\eqref{eq:anolam} is just
 \begin{align}
@@
 \end{align}
-For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}.
+For example, the solution with $\lambda=3$: $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}.
 We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.

### 2019-09-17 draft.tex
Updates from Overleaf

@@
 This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including
-the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 60\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
+the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
 \end{abstract}
@@
 
-\section{Beyond the minimal model: cosmological constraints}
+\section{Beyond the minimal model: cosmological and collider constraints}
 \label{sec:CosmoConstraints}
@@
 
-The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
-It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
-% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
-It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound implies that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV.
-%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
-On the other hand, it is remarkable the fact the future CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} have the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
-
 %
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 \end{figure}
+%
 
+The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
+It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
+% The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
+It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV.
+%in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
+On the other hand, it is remarkable the fact the future CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} have the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
 %Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
 
-\section{Collider constraints}
-The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
-in~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
-The green (upper) region in fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g^{\prime}$.
-In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa}\footnote{The constraint as function of $h=-1-l$ is given in~\cite{Okada:2016tci}.
-},
+%\section{Collider constraints}
+Regarding collider searches, the recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
+in Ref.~\cite{Chiang:2019ajm} for the $\operatorname{U}(1)_{B-L}$ model.
+The green (upper) region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g^{\prime}$.
+In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa}\footnote{The constraint as function of the $X$-charge $h=-1-l$ is given in Ref.~\cite{Okada:2016tci}.
+}
 \begin{align} 
@@
 which is obtained from the search for effective four-lepton operators and is valid for $M_{Z'}\gg 200\ \text{GeV}$.
-This constraint corresponds to the excluded magenta (lower) region of fig.~\ref{fig:u1blc} and start to be relevant for $M_{Z'}>5.8\ \text{TeV}$.
+This constraint corresponds to the excluded magenta (lower) region of Fig.~\ref{fig:u1blc} and start to be relevant for $M_{Z'}>5.8\ \text{TeV}$.
 
@@
     \centering
-    \includegraphics[scale=0.8]{u1blc}
-    \caption{Constraints in the $\operatorname{U}(1)_{B-L}$ model.}
+    \includegraphics[scale=1.0]{u1blc}
+    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model.}
     \label{fig:u1blc}
@@
 The constraint of $\Delta N_{\text{eff}}$ for $\operatorname{U}(1)_{B-L}$ is shown in the blue (middle) region and start to be better than current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$.
-Similar restrictions can be obtained for the other models quoted in fig.~\ref{fig:Neff}.
+Similar restrictions can be obtained for the other models quoted in Fig.~\ref{fig:Neff}.
 
-\section{Discussion and summary}
+\section{Summary}
 
+\section*{Acknowledgments}
+Work supported by Sostenibilidad-UdeA and the UdeA/CODI Grant 2017-16286, and by COLCIENCIAS through the Grant 111577657253. 
 \appendix
-\section{Anomaly cancellation}
+\section{$\operatorname{U}(1)_X$ anomaly cancellation }
 We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$).
@@
   \label{eq:anolin}
-  \left[\mathrm{SU}(3)_{c}\right]^{2} \mathrm{U}(1)_{X} :& &
-[3 u+3 d]-[3 \cdot 2 q]=&0 \nonumber\\
+  \left[\mathrm{SU}(3)_{C}\right]^{2} \mathrm{U}(1)_{X} :& &
+[3 u+3 d]-[3 \cdot 2 q]=&0, \nonumber\\
 \left[\mathrm{SU}(2)_{L}\right]^{2} \mathrm{U}(1)_{X} :&&
--[2 l+3 \cdot 2 q]=&0 \nonumber\\
+-[2 l+3 \cdot 2 q]=&0, \nonumber\\
 \left[\mathrm{U}(1)_{Y}\right]^{2} \mathrm{U}(1)_{X} :&&
 { \left[(-2)^{2} e+3\left(\tfrac{4}{3}\right)^{2} u+3\left(-\tfrac{2}{3}\right)^{2} d\right]-\left[2(-1)^{2} l+3 \cdot 2\left(\tfrac{1}{3}\right)^{2} q\right]}=&
- 0
+ 0,
   \end{align}
@@
   \label{eq:anolam}
-  \sum_{\alpha=1}^{n} n_{\alpha}=&-3 \lambda\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3 \lambda^3\,, 
+  \sum_{\alpha=1}^{n} n_{\alpha}=&-3 \lambda\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3 \lambda^3\,.
 \end{align}
@@
 \end{align}
-For example, the solution with $\lambda=3$: $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}.
+For example, the solution with $\lambda=3$: $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form in Eq.~\eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in Ref.~\cite{Patra:2016ofq}.
 We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.

### 2019-09-17 draft.tex
lc

@@
 In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
-In section~\ref{sec:LFV} we show the lepton flavor violation experimental  constraints.
+Also, we show the lepton flavor violation experimental  constraints.
 In section~\ref{sec:DM} we present the viable DM candidates.
@@
     % $H $  & 2  1/2  &  0 \\
-    $\eta$  & $\boldsymbol{2}$ & $1/2$  & $1$ \\
+    $\eta$  & $\boldsymbol{2}$ & $1$  & $1$ \\
     $S$ & $\boldsymbol{1}$ & $0$  & $2$ \\
@@
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{N}$ gauge symmetry. }
+  \caption{The new scalars and fermions with their respective charges. All the SM fields are neutral under the dark $\operatorname{U}(1)_{\cal {D}}$ gauge symmetry. }
     \label{tab:partcont}
@@
 \end{align}
-where $S$ is the singlet scalar field which spontaneously breaks the $\operatorname{U}(1)_X$ symmetry needed to forbid the Dirac and Majorana neutrino mass terms at tree level.
+where $S$ is the singlet scalar field which spontaneously breaks the $\operatorname{U}(1)_{\cal {D}}$ symmetry needed to forbid the Dirac and Majorana neutrino mass terms at tree level.
 
@@
 %
-\begin{align*}
+\begin{align}
 (\mathcal{M}_{\nu})_{ij} = \frac{\lambda_8 v_S v}{16 \pi^{2}} \sum_{\alpha=1}^{3} \frac{h_{i \alpha} M_{\psi_{\alpha}} y^{*}_{j\alpha}} {m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \left[1 - \frac{M_{\psi_{\alpha}}^{2}}{m_\chi^{2}-M_{\psi_{\alpha}}^{2}} \log \left( \frac{m_{\chi}^{2}}{M_{\psi_{\alpha}}^{2}} \right)\right]\,,
-\end{align*}
+\end{align}
 %
@@
 & \sim 0.04~\text{eV} \left( \frac{\lambda_8}{10^{-4}}\right) \left( \frac{v_{S}}{200\,  \text{GeV}}\right) \left( \frac{M_{\psi_\alpha}}{50\,\text{GeV}}\right) \left( \frac{2\, \text{TeV}}{m_{\chi}}\right)^{2} \left( \frac{h_{i \alpha} y_{j\alpha}}{10^{-4}}\right)\,.
-\nonumber
 \end{align}
@@
     Fields     & $\operatorname{SU}(2)_L$ &  $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$ & $\operatorname{U}(1)_{\mathcal{D}}$\\ \hline
-$L $     & $\boldsymbol{2}$ & $-1/2$ & $l$      &  $-1$&    $0$ &  $-3/2$&  $-1/2$ & $0$ \\    
-$d_R $   & $\boldsymbol{1}$ & $-1/2$ & $1+2l/3$ &  $1/3$&    $1$&  $0$&    $2/3$ & $0$\\
-$u_R $   & $\boldsymbol{1}$ & $+2/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&   $-1/3$ & $0$ \\
-$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ & $0$ \\
-$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ & $0$\\\hline
-$H $     & $\boldsymbol{2}$ & $1/2$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ & $0$ \\
-$\eta$   & $\boldsymbol{2}$ & $+1/2$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ & $0$ \\
+$L $     & $\boldsymbol{2}$ & $-1$ & $l$      &  $-1$&    $0$ &  $-3/2$&  $-1/2$ & $0$ \\    
+$d_R $   & $\boldsymbol{1}$ & $-2/3$ & $1+2l/3$ &  $1/3$&    $1$&  $0$&    $2/3$ & $0$\\
+$u_R $   & $\boldsymbol{1}$ & $+4/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&   $-1/3$ & $0$ \\
+$Q $     & $\boldsymbol{2}$ & $1/3$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ & $0$ \\
+$e_R $   & $\boldsymbol{1}$ & $-2$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ & $0$\\\hline
+$H $     & $\boldsymbol{2}$ & $1$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ & $0$ \\
+$\eta$   & $\boldsymbol{2}$ & $1$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ & $0$ \\
 $S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ & $0$\\
@@
 %
-\begin{align*}
+\begin{align}
     \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
-\end{align*}
+\end{align}
 %
@@
 %
-\begin{align*}
-    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \,, \\
+\begin{align}
+    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \,, \nonumber\\
     &= \frac{g^{2}_{\nu_R}}{n_{\nu_R}(T)} \int \frac{d^{3} p}{(2 \pi)^{3}} f_{\nu_R}(p) \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k) \sigma_{f}(s) \upsilon\,,
-\end{align*}
+\end{align}
 %
@@
 %
-\begin{align*}
+\begin{align}
     \sigma_{f}(s) \approx N^{C}_{f} \frac{s}{12 \pi} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} q^{2}_{\nu_R} (q^{2}_{f_L} + q^{2}_{f_R})\,,
-\end{align*}
+\end{align}
 %
@@
 %
-\begin{align*}
+\begin{align}
     \Gamma_{\nu_{R}}(T) = \frac{49 \pi^{5} T^{5}}{97200 \zeta(3)} \left( \frac{g^{\prime}}{M_{Z^{\prime}}} \right)^{4} \sum_{f} N^{C}_{f} q^{2}_{f}\,.
-\end{align*}
+\end{align}
 %
@@
 \end{align}
-We choose the solutions with $\lambda\equiv e-2l$, such that
+We choose the solutions with $r\equiv e-2l$, such that
 \begin{align}
   \label{eq:anolam}
-  \sum_{\alpha=1}^{n} n_{\alpha}=&-3 \lambda\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3 \lambda^3\,.
+  \sum_{\alpha=1}^{N} n_{\alpha}=&-3 r\,,   & \sum_{\alpha=1}^{N} n_{\alpha}^3=&-3 r^3\,.
 \end{align}
-The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $\lambda$, is just
+The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $r$, is just
 \begin{align}
-  u=&-\lambda-\frac{4l}{3}\,,&d=&\lambda+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&\lambda+2l\,,&h=&-\lambda-l\,.
+  u=&-r-\frac{4l}{3}\,,&d=&r+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&r+2l\,,&h=&-r-l\,.
   \label{Eq:SMCharges}
 \end{align}
-If we now change $f\to  f/\lambda$, such that $\lambda\to 1$, the first of anomaly cancellation~\eqref{eq:anolin} remain invariant, and without lost of generality
-always is possible to normalize the solutions such that the last set~\eqref{eq:anolam} is just
+If we define the Abelian symmetry in which only the right-handed charged fermions have non-vanishing $X$-charges as $\operatorname{U}(1)_R$, then the general anomaly free two-parameter solution can be written as
+\begin{align}
+  X=r R- l Y\,.
+\end{align}
+
+If we now change $f\to f'= f/r$ for all the charged fermion $X$-charges, the
+first set of anomaly cancellation condtions~\eqref{eq:anolin} remain
+invariant, and without lost of generality it is always possible to
+normalize the solutions such that the last set~\eqref{eq:anolam} is
+just
 \begin{align}
   \label{eq:anolamnor}
-   \sum_{\alpha=1}^{n} n_{\alpha}=&-3\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3\,.
+   \sum_{\alpha=1}^{N} n_{\alpha}^{\prime}=&-3\,,   & \sum_{\alpha=1}^{N} n_{\alpha}^{\prime\, 3}=&-3\,.
 \end{align}
-For example, the solution with $\lambda=3$: $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form in Eq.~\eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in Ref.~\cite{Patra:2016ofq}.
-We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
+For example, the solution with $r=3$: $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form in Eq.~\eqref{eq:anolamnor} with $f\to f/3$
+to $n_{\alpha}'=\left( -2/3,-2/3,-4/3,-1/3 \right)$
+as used in Ref.~\cite{Patra:2016ofq}.
+In this way, without lost of generality, we work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy} that we choose to be $l$, by setting $r=1$ as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}, which is just
+\begin{align}
+  X=R-l\, Y\,.
+\end{align}
 In particular, this includes the solution  $n_{\alpha}=(-4,-4,+5)$~\cite{Appelquist:2002mw}. 
-
-For this normalized set of solutions we have that
+In general, we have that for $\nu=n_1=n_2$, the extra fermion inside the one-loop neutrino mass diagram in fig.~\ref{fig:zee}, must have charges
 \begin{align}
@@
 \end{align}
+The case for $\nu=-4$ is also displayed in Table~\ref{tab:partcont3}.
 

### 2019-09-18 draft.tex
Updates from Overleaf
mc

--- 2019-09-17 draft.tex
@@
 
-The most general Lagrangian for some gauge $\operatorname{U}(1)_X$ symmetry, which includes $X=\mathcal{D}$, contains the following gauge, Yukawa and scalar interactions:
+The most general Lagrangian for some gauge $\operatorname{U}(1)_X$ symmetry, which includes the trivial case $X=\mathcal{D}$, must contains the following gauge, Yukawa and scalar interactions in
+order to realize $\mathcal{O}_{6D}$ at one-loop:
 %
@@
 \begin{align}
+  \label{eq:VHSetasigma}
     \mathcal{V}(H, S, \eta, \sigma) = & V(H) + V(S) + V(\eta) + V(\sigma) \nonumber\\
@@
 with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}$.
+It is worth to emphasize that $\operatorname{U}(1)_{\mathcal{D}}$ automatically allows for all the terms in eqs.~\eqref{eq:LagY} and~\eqref{eq:VHSetasigma} but other realizations will be checked later on.
 Note that after the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the $\lambda_8$ term gives rise to the mixing between the neutral parts of $\eta$ and $\sigma$, which is mandatory to generate non-zero radiative masses.
@@
 $\psi_{R\alpha}$ which realize the dimension-6 operator at one-loop
-have vector-like $X$-charges would spoil the anomaly cancellation
+ would spoil the anomaly cancellation
 condition.
@@
     \includegraphics[scale=1.0]{u1blc}
-    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model.}
+    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model, and contours of constant $g'$ in the plane of $q_s v_S$ as a function of $M_{Z'}$ with $q_S=2$.}
     \label{fig:u1blc}
@@
 The constraint of $\Delta N_{\text{eff}}$ for $\operatorname{U}(1)_{B-L}$ is shown in the blue (middle) region and start to be better than current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$.
+In the figure we also show contours of constant $g'$ at $0.01$, $0.1$ and $0.5$ with the solid, dashed and dot-dashed lines respectively.
+We can see that start to constraint $g'$ for values larger than $0.1$ in $\operatorname{U}(1)_{B-L}$.
 Similar restrictions can be obtained for the other models quoted in Fig.~\ref{fig:Neff}.
@@
 \end{align}
-The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $r$, is just
+The full set of anomaly free standard model $X$-charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $r$, is just
 \begin{align}
@@
 \end{align}
-If we define the Abelian symmetry in which only the right-handed charged fermions have non-vanishing $X$-charges as $\operatorname{U}(1)_R$, then the general anomaly free two-parameter solution can be written as
+By setting $l=0$ in the previous equations, we can define the Abelian symmetry in which only the right-handed charged fermions have non-vanishing $X$-charges as $\operatorname{U}(1)_R$.
+Then the general anomaly free two-parameter solution can be written as
 \begin{align}

### 2019-09-18 draft.tex
lc
jj

@@
 The interpretation of neutrino experimental data in terms of neutrino
-oscillations is compatible with both Majorana or Dirac neutrino masses
+oscillations is compatible with both Majorana and Dirac neutrino masses
 \cite{Tanabashi:2018oca}. The former possibility has received the most
@@
 In the figure we also show contours of constant $g'$ at $0.01$, $0.1$ and $0.5$ with the solid, dashed and dot-dashed lines respectively.
-We can see that start to constraint $g'$ for values larger than $0.1$ in $\operatorname{U}(1)_{B-L}$.
+We can see that $\Delta N_{\text{eff}}$ start to constraint $g'$ for values larger than $0.1$ in $\operatorname{U}(1)_{B-L}$.
 Similar restrictions can be obtained for the other models quoted in Fig.~\ref{fig:Neff}.

### 2019-09-18 draft.tex
lc

@@
 \begin{abstract}    
-We propose a model for one-loop Dirac neutrino masses with Majorana mediators which can be dark matter candidates if they are the lightest states circulating the loop.
+  The radiative type-I seesaw have been already implemented to explain the lightness of Majorana neutrinos with both Majorana and Dirac heavy fermions, and the lightness of Dirac    neutrinos with                   Dirac heavy fermions.
+In this work we present a minimal implementation of the radiative type-I seesaw with light Dirac neutrinos and heavy Majorana fermions.
+An inert doublet and a complex singlet scalar complete the dark sector which is protected by an Abelian fermiophobic gauge symmetry that also forbids three level mass contributions for the full set of light neutrinos.
+A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
+...
+%some results here
   This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
@@
 \label{sec:intro}
-%Dirac or Majorana
+
 The interpretation of neutrino experimental data in terms of neutrino
@@
 the latter cannot be dismissed.
-% Dirac case
 If neutrinos are Dirac particles, the Standard Model (SM) particle
 content must be extended with right-handed neutrinos,
-% with cosmology implications
 which can increase the effective number of light neutrinos,
@@
 
-%Smallness of neutrinos for both Dirac and Majorana
 On the other hand, to give small masses to at least two Majorana or
@@
 experiments~\cite{Ahmad:2002jz, Fukuda:1998mi},
-%focus in seesaw type I
 the seesaw mechanism with heavy fermions is usually invoked.
-%tree-level case
 For the tree-level type-I seesaw we can have either light Majorana
@@
 mediators~\cite{Roncadelli:1983ty,Roy:1983be,Gu:2007mc,Ma:2014qra}.
-%one-loop case
 The radiative type-I seesaw includes both~\cite{Ma:2006km}
 possibilities~\cite{Farzan:2012sa},
-%new possibility in radiative case
 but now it is also possible to have light Majorana neutrinos with
 heavy Dirac mediators~\cite{Ma:2013yga}.
-%New in this work
 In this work we want to explore the possibility to build a simple
 Dirac radiative type-I seesaw model with heavy Majorana mediators.
-%Old idea but first realized here
 It is worth noticing that this idea have been already illustrated in
@@
 
-%Features of the new propossed solution
 In general, solutions for light Dirac neutrino masses require a
@@
 neutrinos~\cite{Roncadelli:1983ty,Han:2018zcn,Wang:2017mcy}.
-%tree-level without adhoc symmetries
 However, tree-level Dirac type-I seesaw with proper choices for the
@@
 without require any extra ad-hoc discrete symmetries~\cite{Ma:2014qra}.
-%one-loop 
 In recent works, it has been shown that even for one-loop Dirac
@@
 the only extra symmetry beyond the SM~\cite{Calle:2018ovc,Bonilla:2018ynb,Saad:2019bqf}\footnote{
-%extra-loops
   For extensions with only extra scalars, minimal solutions have been found with two and three loops~\cite{Saad:2019bqf}}.
-%conexion with dark matter
+
 As a bonus in this case, the new scalars and fermions circulating the
@@
 of them guaranteed by the very same continuous symmetry.
-% remark
 We focus here in solutions for the radiative Dirac type-I seesaw with
@@
 
-%conexion with DM
 In fact, another evidence that the SM is not a complete theory is the
@@
 (DM).
-% DM as particle
 The main proposals that explain DM as a particle are given in
 Ref.~\cite{Bertone:2004pz}.
-%not found
 However, there have been only gravitational evidence for the existence
 of dark matter so far.
-% too many possibilities
 Without evidence of DM as a particle, there is not a clear path to pin
@@
 extended dark sector. 
-% connect with other phenomena
 Linking the dark sector to other specific phenomenology allows to
 reduce the arbitrariness in the model building.
-% loop
 In our construction, the dark sector is related to the heavy sector
@@
 responsible of the stability of the lightest dark particle (LDP).
-% new particle prediction
 Therefore, the number of specific models is quite restricted.
@@
 %%% End:
+
+% Dirac or Majorana
+% Dirac case
+% with cosmology implications
+
+% Smallness of neutrinos for both Dirac and Majorana
+% focus in seesaw type I
+%tree-level case
+%one-loop case
+%new possibility in radiative case
+%New in this work
+%Old idea but first realized here
+%Features of the new propossed solution
+%tree-level without adhoc symmetries
+%one-loop 
+%extra-loops
+%conexion with dark matter
+% remark
+% conexion with DM
+% DM as particle
+%not found
+% too many possibilities
+% connect with other phenomena
+% loop
+% new particle prediction

### 2019-09-18 draft.tex
Updates from Overleaf

@@
 %
-where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$, $\upsilon = 1-\cos{\theta}$ is the Moller velocity, $s = 2 p k (1-\cos{\theta})$, $p$ and $k$ are the momenta of the particle with $\theta$ the angle between them, and the number density of right-handed neutrinos is given by
+where $f_{\nu_R}(k)=1/(e^{k/T}+1)$ is the Fermi-Dirac distribution, $g_{\nu_R} = 2$, $\upsilon = 1-\cos{\varphi}$ is the Moller velocity, $s = 2 p k (1-\cos{\varphi})$, $p$ and $k$ are the momenta of the particle with $\varphi$ the angle between them, and the number density of right-handed neutrinos is given by
 \begin{align*}
@@
 \caption{Contribution to the number of extra relativistic degrees of freedom ($\Delta N_{\text{eff}}$) in function of $M_{Z^{\prime}}/g^{\prime}$.
-The region above the gray line is excluded by the measurements at $2\sigma$ from PLANCK~\cite{Aghanim:2018eyx}.
+The region above the solid gray line is excluded by the measurements at $2\sigma$ reported by the PLANCK Collaboration~\cite{Aghanim:2018eyx}.
+For comparison purposes  the upper bound at $2\sigma$ (black line) obtained from the BBN analysis~\cite{Pitrou:2018cgg} is also shown.
 The horizontal dashed lines show the projected sensitivity of the future experiments SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
+$\Delta N_{\text{eff}}=0.4$ represents the extra contribution  required to relieve the tension on the inferred $H_0$ values from  high- and low-redshift observations \cite{Bernal:2016gxb,Mortsell:2018mfj}.
 }
@@
 
-\begin{figure}
+\begin{figure}[t]
     \centering
     \includegraphics[scale=1.0]{u1blc}
-    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model, and contours of constant $g'$ in the plane of $q_s v_S$ as a function of $M_{Z'}$ with $q_S=2$.}
+    \caption{Collider and cosmological constraints for the $\operatorname{U}(1)_{B-L}$ model, and contours of constant $g'$ in the plane of $q_S v_S$ as a function of $M_{Z'}$ with $q_S=3/2$.}
     \label{fig:u1blc}
@@
 \section{Summary}
+The mechanism behind the neutrino mass generation and the Dirac/Majorana character of massive neutrinos still remain a conundrum despite the clear understanding of the neutrino oscillation pattern and the great experimental efforts behind the neutrinoless double-beta decay.
+Alongside this is the fact that there are no clues on the nature of the DM particle and the properties of the dark sector it belongs.
+
+In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
+The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators.
+The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram.
+In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
+
+We have illustrated our proposal by considering a specific
+model, where simple numerical estimates allow us to show the effectiveness of the scheme regarding neutrino masses, DM and lepton flavor violating processes. Furthermore,.
 

### 2019-09-18 draft.tex
lc

@@
 
-With the aim of thermalize the right-handed neutrinos we consider an extension of the previous setup by introducing a general Abelian gauge symmetry $\operatorname{U(1)}_X$ with generation-independent charge assignments for the SM fields.
-Extra chiral fields are required to cancel the anomalies for solutions beyond the one proportional to $\operatorname{U}(1)_Y$.
-In the appendix we show that the solutions to the anomaly cancellation conditions parameterized in terms
-of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc}, can be normalized to depend in just one parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy} that we choose to be the $X$-charge of the lepton doublet as displayed in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}.
-There, the previous dark symmetry denoted as $X=\mathcal{D}$ corresponds to the fermiophobic setup~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf}.
+With the aim of thermalize the right-handed neutrinos with the
+primordial plasma in the early universe, we consider an extension of
+the previous setup by introducing a general anomaly free Abelian gauge
+symmetry with generation-independent charge assignment for the
+standard model fermions, $\operatorname{U}(1)_{X}$.
+% 
+In the appendix we show that the solutions to the anomaly cancellation conditions
+allow us to write the $X$-charges of the SM fields in terms
+of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc}, that we choose as
+\begin{align}
+  X(r,l)=r R - l Y\,,
+\end{align}
+where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fields have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam}.
+In this way, if only extra vector-like fermions are allowed beyond the SM ($r=0$) the solution must be proportional to hypercharge.
+%
+Without lost of generality, we can write the solutions in terms of just one parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$  after fix $r=1$.
+Then, as shown in the Appendix, the full family of solutions for fixed $l$ can be obtained after  rescaling all the $X$-charges by a factor $r$.
+In particular, the fermiophobic~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf} solution used in the previous sections, $\operatorname{U}(1)_{\mathcal{D}}$, corresponds to the rescaling $r=0$ of the $\operatorname{U}(1)_R$ solution.
+
+The one parameter solution is shown in  column $\operatorname{U}(1)_X$
+of Table~\ref{tab:partcont3}.
+In order to analyse the phenomenology we fix $l$ to recover some already studied
+Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}.
+The last column can be obtained after a reescaling with $r=0$ of $\operatorname{U}(1)_R$.
 
@@
 Moreover, because the $\operatorname{U}(1)_{X}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest $Z_2$-odd particle,  we have that the lightest of these Majorana fields may play the role of DM candidate.}.
-
-In order to analyse the phenomenology we fix $l$ to recover some already studied
-Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}.
 

### 2019-09-18 draft.tex
lc

@@
 \end{align}
-where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fields have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam}.
+where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fields have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam} of the Appendix.
 In this way, if only extra vector-like fermions are allowed beyond the SM ($r=0$) the solution must be proportional to hypercharge.
@@
 Then, as shown in the Appendix, the full family of solutions for fixed $l$ can be obtained after  rescaling all the $X$-charges by a factor $r$.
-In particular, the fermiophobic~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf} solution used in the previous sections, $\operatorname{U}(1)_{\mathcal{D}}$, corresponds to the rescaling $r=0$ of the $\operatorname{U}(1)_R$ solution.
+In particular, the fermiophobic~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf} solution used in the previous sections, $\operatorname{U}(1)_{\mathcal{D}}$, corresponds to the rescaling $r=0$ of the $\operatorname{U}(1)_R$ solution: $\mathcal{D}=X(0,0)$.
 
@@
 In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
-
+We have showed that beyond the minimal model The new states required  may also lead to other phenomenological signals
+at future hadron collider as well as lepton flavour violation experiments
 We have illustrated our proposal by considering a specific

### 2019-09-18 draft.tex
Updates from Overleaf

--- 2019-09-18 draft.tex
@@
 In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
-
+We have showed that going beyond the minimal model other phenomenological signals
+at future hadron collider as well as lepton flavour violation experiments
 We have illustrated our proposal by considering a specific

### 2019-09-18 draft.tex

--- 2019-09-18 draft.tex
@@
 In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
-We have showed that beyond the minimal model The new states required  may also lead to other phenomenological signals
+We have showed that going beyond the minimal model other phenomenological signals
 at future hadron collider as well as lepton flavour violation experiments

### 2019-09-18 draft.tex
Updates from Overleaf

@@
 In this way the model offers in a non trivial way a the solution to both neutrino and DM puzzles.
-We have showed that going beyond the minimal model other phenomenological signals
-at future hadron collider as well as lepton flavour violation experiments
-We have illustrated our proposal by considering a specific
-model, where simple numerical estimates allow us to show the effectiveness of the scheme regarding neutrino masses, DM and lepton flavor violating processes. Furthermore,.
+Moreover, we have shown that going beyond the minimal model other interesting phenomenological aspects arise such that possible signals at colliders and new contributions to the number of extra relativistic species.
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}\gtrsim 40\ \text{TeV}$.
+Future cosmic microwave background experiments may probe all the no minimal models presented here.
 

### 2019-09-18 draft.tex
pt

@@
 }
+%%%%%%
+% \newcommand{\UPTC}{Escuela de Física, Universidad Pedagógica y Tecnológica de Colombia,\\
+% Avenida Central del Norte \# 39-115, Tunja, Colombia}
+\newcommand{\UdeA}{}
 %%%%%%%%%%%%%%%TITLE PAGE
@@
 
-\author{First Author\footnote{\href{mailto:first@author}{first@author}},
-Second Author\footnote{\href{mailto:second@author}{second@author}}\\
-\textit{\small  First Institute}\\
-[4mm]
-Third Author\footnote{\href{mailto:third@author }{third@author}}\\
-\textit{\small Second Institute}
+\author{Julian Calle${}^1$\footnote{\href{mailto:julian.callem@udea.edu.co}{julian.callem@udea.edu.co}},
+  Diego Restrepo${}^{1,2}$\footnote{\href{mailto:restrepo@udea.edu.co}{restrepo@udea.edu.co}}, and Óscar Zapata${}^1$\footnote{\href{mailto:oalberto.zapata@udea.edu.co }{oalberto.zapata@udea.edu.co}}\\
+[2mm]  
+\textit{\small ${}^1$Instituto de Física,
+  Universidad de Antioquia,
+}\\
+\textit{\small   Calle 70 \# 52-21, Apartado Aéreo 1226, Medellín, Colombia.}\\
+[2mm]
+\textit{\small ${}^2$
+International Institute of Physics, Universidade Federal do Rio Grande do Norte,
+}\\
+\textit{\small Campus Universitario, Lagoa Nova, Natal-RN 59078-970, Brazil. }
 }
-\date{\small Month NN, YYYY}
+\date{\small September DD, 2019}
 \begin{document}
 \maketitle
-\ReportNumbers{XXX-XXX}
+\ReportNumbers{IIPDM-2019}
 

### 2019-09-18 draft.tex
Updates from Overleaf
pt

@@
 %Higgs portal trough the Lagrangian term $\sigma^{2} H^{2}_{i}$.
+The rest of the paper is organized as follows.
+In the next section we present the model and the particle content.
+In the section~\ref{sec:Model} we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
+In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
+Also, we show the lepton flavor violation experimental  constraints.
+In s
+
 %This term generates interesting phenomenological consequences.
@@
 the previous setup by introducing a general anomaly free Abelian gauge
-symmetry with generation-independent charge assignment for the
+symmetry with generation-independent charge assignments for the
 standard model fermions, $\operatorname{U}(1)_{X}$.
@@
 \end{align}
-where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fields have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam} of the Appendix.
+where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fermions have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam} of the Appendix.
 In this way, if only extra vector-like fermions are allowed beyond the SM ($r=0$) the solution must be proportional to hypercharge.
@@
 Without lost of generality, we can write the solutions in terms of just one parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$  after fix $r=1$.
-Then, as shown in the Appendix, the full family of solutions for fixed $l$ can be obtained after  rescaling all the $X$-charges by a factor $r$.
+Then, as shown in the Appendix, the full family of solutions for a fixed $l$ can be obtained after  rescaling all the $X$-charges by a factor $r$.
 In particular, the fermiophobic~\cite{Campos:2017dgc,Bertuzzo:2018itn,Bertuzzo:2018ftf} solution used in the previous sections, $\operatorname{U}(1)_{\mathcal{D}}$, corresponds to the rescaling $r=0$ of the $\operatorname{U}(1)_R$ solution: $\mathcal{D}=X(0,0)$.
@@
 of Table~\ref{tab:partcont3}.
-In order to analyse the phenomenology we fix $l$ to recover some already studied
+In order to analyse the phenomenology, we fix $l$ to recover some already studied
 Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}.
-The last column can be obtained after a reescaling with $r=0$ of $\operatorname{U}(1)_R$.
+The last column corresponds to the reescaling with $r=0$ of $\operatorname{U}(1)_R$.
 
@@
 $H $     & $\boldsymbol{2}$ & $1$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ & $0$ \\
-$\eta$   & $\boldsymbol{2}$ & $1$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ & $0$ \\
-$S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ & $0$\\
-$\sigma$ & $\boldsymbol{1}$ & $0$    & $13/4$   & $13/4$&  $13/4$ & $13/4$& $13/4$ & $0$\\\hline
+$\eta$   & $\boldsymbol{2}$ & $1$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ & $1$ \\
+$S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ & $2$\\
+$\sigma$ & $\boldsymbol{1}$ & $0$    & $13/4$   & $13/4$&  $13/4$ & $13/4$& $13/4$ & $3$\\\hline
 $\nu_{Ri}$& $\boldsymbol{1}$ & $0$   & $-4$& $-4$&  $-4$ & $-4$& $-4$ & $-4$\\
@@
   \end{tabular}
-  \caption{The new scalars and fermions with their respective charges for the 6-dimensional operator.
-The SM fields have the usual $U(1)_{B-L}$ assignment.
-Now $\alpha=1,2$.
-The solution in Table~\ref{tab:partcont} is presented in the last column.}
+  \caption{General one-parameter solution with some examples of rational solutions
+    ($X=B-L,R,D,G$ and $\mathcal{D}$) for the radiative type-I seesaw realization
+    of the effective operator $\mathcal{O}_{6D}$ for Dirac neutrino masses. The
+    last column  corresponds to the solution in Table~\ref{tab:partcont}.}
     \label{tab:partcont3}
@@
 \section*{Acknowledgments}
-Work supported by Sostenibilidad-UdeA and the UdeA/CODI Grant 2017-16286, and by COLCIENCIAS through the Grant 111577657253. 
+Work supported by Sostenibilidad-UdeA and the UdeA/CODI Grant
+2017-16286, and by COLCIENCIAS through the Grant 111577657253. D.R
+would also like to thank the IIP-Natal, for its support,
+hospitality and the nice and stimulating atmosphere during the
+Visiting Professors program where part of this work was completed.
 \appendix

### 2019-09-18 draft.tex
pt

@@
 A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
-...
-%some results here
-  This model is restricted by  neutrino physics,  lepton flavor violation and cosmological constrains, including  
-the effective number light neutrinos $N_{\text{eff}}$. Here we find that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40\ \text{TeV}$ in order to satisfy the conditions of $N_{\text{eff}}$..
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$, while future cosmic microwave background experiments may probe all the no minimal models presented here.
 \end{abstract}
@@
 Moreover, we have shown that going beyond the minimal model other interesting phenomenological aspects arise such that possible signals at colliders and new contributions to the number of extra relativistic species.
-In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}\gtrsim 40\ \text{TeV}$.
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$.
 Future cosmic microwave background experiments may probe all the no minimal models presented here.

### 2019-09-18 draft.tex
pt

@@
 A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
-In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$, while future cosmic microwave background experiments may probe all the no minimal models presented here.
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competetive with collider constraint for $g'$ sufficiently large in the ballpark of the SM values , while future cosmic microwave background experiments may probe all the no minimal models presented here.
 \end{abstract}

### 2019-09-18 draft.tex
Updates from Overleaf

--- 2019-09-18 draft.tex
@@
 the only extra symmetry beyond the SM~\cite{Calle:2018ovc,Bonilla:2018ynb,Saad:2019bqf}\footnote{
-  For extensions with only extra scalars, minimal solutions have been found with two and three loops~\cite{Saad:2019bqf}}.
+  For extensions with only extra scalars, minimal solutions have been found with two and three loops~\cite{Saad:2019bqf}.}.
 
@@
 The rest of the paper is organized as follows.
-In the next section we present the model and the particle content.
-In the section~\ref{sec:Model} we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
-In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
-Also, we show the lepton flavor violation experimental  constraints.
+In the next section we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
+In section~\ref{sec:Neutrinos} we present the radiative mechanism to generate Dirac neutrino masses and establish  the lepton flavor violation experimental constraints.
 In section~\ref{sec:DM} we present the viable DM candidates.

### 2019-09-19 draft.tex
Updates from Overleaf

--- 2019-09-18 draft.tex
@@
 A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
-In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$, while future cosmic microwave background experiments may probe all the no minimal models presented here.
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competetive with collider constraint for $g'$ sufficiently large in the ballpark of the SM values, while future cosmic microwave background experiments may probe all the no minimal models presented here.
 \end{abstract}
@@
 The rest of the paper is organized as follows.
-In the next section we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
-In section~\ref{sec:Neutrinos} we present the radiative mechanism to generate Dirac neutrino masses and establish  the lepton flavor violation experimental constraints.
-In section~\ref{sec:DM} we present the viable DM candidates.
-Finally, In section~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{\text{eff}}$) in a nonminimum model for different extra abelian symmetries.
+In the next Section we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
+In Sec.~\ref{sec:Neutrinos} we present the radiative mechanism to generate Dirac neutrino masses and establish  the lepton flavor violation constraints.
+The different DM scenarios are discussed in Sec.~\ref{sec:DM}.
+Finally, in Sec.~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{\text{eff}}$) in a non-minimum model for different extra abelian symmetries.
 
@@
 %Higgs portal trough the Lagrangian term $\sigma^{2} H^{2}_{i}$.
-The rest of the paper is organized as follows.
-In the next section we present the model and the particle content.
-In the section~\ref{sec:Model} we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
-In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses.
-Also, we show the lepton flavor violation experimental  constraints.
-In s
 
@@
 \end{align}
-where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fermions have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in eq.~\eqref{eq:anolam} of the Appendix.
+where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fermions have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in Eq.~\eqref{eq:anolam} of the Appendix.
 In this way, if only extra vector-like fermions are allowed beyond the SM ($r=0$) the solution must be proportional to hypercharge.
@@
 
-\section{Summary}
+\section{Conclusions}
 The mechanism behind the neutrino mass generation and the Dirac/Majorana character of massive neutrinos still remain a conundrum despite the clear understanding of the neutrino oscillation pattern and the great experimental efforts behind the neutrinoless double-beta decay.
@@
 In view of this we have proposed a new mechanism for Dirac neutrino masses which making use of heavy Majorana mediators generate nonzero masses at one-loop level. 
-The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather Dirac mediators.
+The model presented in this paper is a one-loop realization of the dimension 6 operator $\overline{L} \tilde{H} \nu_R S^2\,$ and enters into the list of Dirac radiative type-I seesaw models with the novel feature that it involves Majorana mediators rather than Dirac mediators.
 The Diracness of the massive neutrinos is protected by only one extra $\operatorname{U}(1)_X$ gauge symmetry, which in turn ensures the stability of the lightest particle mediating the one-loop neutrino mass diagram.
@@
 \begin{align}
-  X=r R- l Y\,.
+  X(r,l)=r R- l Y\,.
 \end{align}
@@
 If we now change $f\to f'= f/r$ for all the charged fermion $X$-charges, the
-first set of anomaly cancellation condtions~\eqref{eq:anolin} remain
+first set of anomaly cancellation conditions Eq.~\eqref{eq:anolin} remains
 invariant, and without lost of generality it is always possible to
-normalize the solutions such that the last set~\eqref{eq:anolam} is
+normalize the solutions such that the last set Eq.~\eqref{eq:anolam} is
 just
@@
 as used in Ref.~\cite{Patra:2016ofq}.
-In this way, without lost of generality, we work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy} that we choose to be $l$, by setting $r=1$ as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}, which is just
+In this way, without lost of generality, we will work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy} that we choose to be $l$, by setting $r=1$ as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}, which is just
 \begin{align}
@@
 In particular, this includes the solution  $n_{\alpha}=(-4,-4,+5)$~\cite{Appelquist:2002mw}. 
-In general, we have that for $\nu=n_1=n_2$, the extra fermion inside the one-loop neutrino mass diagram in fig.~\ref{fig:zee}, must have charges
+In general, we have that for $\nu=n_1=n_2$, the extra fermion inside the one-loop neutrino mass diagram in Fig.~\ref{fig:zee}, must have charges
 \begin{align}
@@
 %%% End:
-
-% Dirac or Majorana
-% Dirac case
-% with cosmology implications
-
-% Smallness of neutrinos for both Dirac and Majorana
-% focus in seesaw type I
-%tree-level case
-%one-loop case
-%new possibility in radiative case
-%New in this work
-%Old idea but first realized here
-%Features of the new propossed solution
-%tree-level without adhoc symmetries
-%one-loop 
-%extra-loops
-%conexion with dark matter
-% remark
-% conexion with DM
-% DM as particle
-%not found
-% too many possibilities
-% connect with other phenomena
-% loop
-% new particle prediction

### 2019-09-20 draft.tex
Updates from Overleaf

@@
 In this work we present a minimal implementation of the radiative type-I seesaw with light Dirac neutrinos and heavy Majorana fermions.
-An inert doublet and a complex singlet scalar complete the dark sector which is protected by an Abelian fermiophobic gauge symmetry that also forbids three level mass contributions for the full set of light neutrinos.
+An inert doublet and a complex singlet scalar complete the dark sector which is protected by an Abelian fermiophobic gauge symmetry that also forbids tree level mass contributions for the full set of light neutrinos.
 A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
-In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competetive with collider constraint for $g'$ sufficiently large in the ballpark of the SM values, while future cosmic microwave background experiments may probe all the no minimal models presented here.
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competitive with collider constraint for $g'$ sufficiently large in the ballpark of the SM values, while future cosmic microwave background experiments may probe all the no minimal models presented here.
 \end{abstract}
@@
 In fact, another evidence that the SM is not a complete theory is the
-missing matter content of the universe, which is known as dark matter
+missing matter content of the Universe, which is known as dark matter
 (DM).
@@
 Ref.~\cite{Bertone:2004pz}.
-However, there have been only gravitational evidence for the existence
+However, there has been only gravitational evidence for the existence
 of dark matter so far.
@@
 responsible of the lightness of the neutrinos and the same symmetry
-which guarantees the lightness of the Dirac neutrinos is the
+that guarantees the lightness of the Dirac neutrinos is the
 responsible of the stability of the lightest dark particle (LDP).
@@
 %Conclusion:
-In this work we propose a radiative Dirac type-I seesaw with Majorana
-fermions as mediators in the loop, where the full set of mediators in the
-loop can include a DM candidate.
 
@@
 In the next Section we present the model and study the scalar mass spectrum after spontaneous symmetry breaking.
-In Sec.~\ref{sec:Neutrinos} we present the radiative mechanism to generate Dirac neutrino masses and establish  the lepton flavor violation constraints.
-The different DM scenarios are discussed in Sec.~\ref{sec:DM}.
-Finally, in Sec.~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{\text{eff}}$) in a non-minimum model for different extra abelian symmetries.
+In Sec.~\ref{sec:Neutrinos} we present the radiative mechanism that generates Dirac neutrino masses and establish  the lepton flavor violation constraints.
+The different resulting DM scenarios  are discussed in Sec.~\ref{sec:DM}, and in Sec.~\ref{sec:CosmoConstraints} we show the cosmological restrictions ($N_{\text{eff}}$) in a non-minimum model for different extra Abelian symmetries.
 
@@
 %
-We extend the standard model with a spontaneously broken Abelian gauge
+We extend the SM with a spontaneously broken Abelian gauge
 symmetry which guarantees the total lepton number ($L$)
-conservation. Only the new particles, including the light right-handed
+conservation. Only the new particles, including the  right-handed partners of the SM
 neutrinos, are charged under this new
@@
 with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}$.
-It is worth to emphasize that $\operatorname{U}(1)_{\mathcal{D}}$ automatically allows for all the terms in eqs.~\eqref{eq:LagY} and~\eqref{eq:VHSetasigma} but other realizations will be checked later on.
+It is worth to emphasize that $\operatorname{U}(1)_{\mathcal{D}}$ automatically allows for all the terms in Eqs.~\eqref{eq:LagY} and~\eqref{eq:VHSetasigma} but other realizations will be checked later on.
 Note that after the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the $\lambda_8$ term gives rise to the mixing between the neutral parts of $\eta$ and $\sigma$, which is mandatory to generate non-zero radiative masses.
@@
 On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha\alpha}v_S/\sqrt{2}$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
-Finally, the mass of the new gauge boson is given by $M_{Z'}=q_Sg^{\prime} v_S$.
+Finally, the mass of the new gauge boson is given by
+\begin{align}
+    M_{Z'}=q_Sg^{\prime} v_S.
+\end{align}
 %\begin{pmatrix}
@@
 %The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
-On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks or charged leptons
+On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couple to quarks and charged leptons
 (see~\cite{Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for phenomenological studies on $Z'$-mediated Majorana DM). 
@@
 With the aim of thermalize the right-handed neutrinos with the
-primordial plasma in the early universe, we consider an extension of
-the previous setup by introducing a general anomaly free Abelian gauge
+primordial plasma in the early Universe, we consider an modification of
+the previous setup by considering a general anomaly free Abelian gauge
 symmetry with generation-independent charge assignments for the
@@
 % 
-In the appendix we show that the solutions to the anomaly cancellation conditions
+In the Appendix we show that the solutions to the anomaly cancellation conditions
 allow us to write the $X$-charges of the SM fields in terms
@@
 \end{align}
-where $R$ is the generator of $\operatorname{U}(1)_R$: the gauge Abelian symmetry where only the right-handed SM fermions have non-vanishing $X$-charges, $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrize the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in Eq.~\eqref{eq:anolam} of the Appendix.
+where $R$ is the generator of $\operatorname{U}(1)_R$ (the gauge Abelian symmetry where only the right-handed SM fermions have non-vanishing $X$-charges), $Y$ is the hypercharge, $l$ is the $X$-charge of the lepton doublets, and $r$ parametrizes the contribution to the linear and mixed gauge-gravitational anomalies of any extra set of chiral fermions, as given in Eq.~\eqref{eq:anolam} of the Appendix.
 In this way, if only extra vector-like fermions are allowed beyond the SM ($r=0$) the solution must be proportional to hypercharge.
@@
 Abelian gauge groups $X=B-L,R,D,G,$ as defined in Ref.~\cite{Campos:2017dgc}\footnote{We change $\operatorname{U}(1)_B$ for the more suitable name of $\operatorname{U}(1)_R$~\cite{Jana:2019mez}.}.
-The last column corresponds to the reescaling with $r=0$ of $\operatorname{U}(1)_R$.
+The last column corresponds to the rescaling with $r=0$ of $\operatorname{U}(1)_R$.
 
@@
 \begin{align}
-    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4}
+    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4},
 \end{align}
 %
-where $N_{\nu_R}$ is the neutrino number with same charges and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
+where $N_{\nu_R}$ is the number of right-handed neutrinos with the same $X$ charge and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
 The decoupling temperature of the SM neutrinos is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4$ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq,Enqvist:1991gx}.
-The rate of interaction of the right-handed neutrinos with the SM is mediated by the gauge boson $Z^{\prime} $ and is given by~\cite{SolagurenBeascoa:2012cz}
+Since the interaction of the right-handed neutrinos with the SM is only mediated by the gauge boson $Z^{\prime} $, the corresponding rate can be cast as~\cite{SolagurenBeascoa:2012cz}
 %
 \begin{align}
-    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \,, \nonumber\\
+    \Gamma_{\nu_R} (T) &= n_{\nu_R}(T) \langle \sigma(\overline{\nu_{R}} \nu_{R} \to \overline{f} f) \upsilon \rangle \, \nonumber\\
     &= \frac{g^{2}_{\nu_R}}{n_{\nu_R}(T)} \int \frac{d^{3} p}{(2 \pi)^{3}} f_{\nu_R}(p) \int \frac{d^{3} k}{(2 \pi)^{3}} f_{\nu_R}(k) \sigma_{f}(s) \upsilon\,,
@@
 \end{align*}
-The cross section for the case of a heavy mediator ($T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$), with $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses in the final state is given by~\cite{Barger:2003zh}
+The cross section for the case of a heavy mediator ($T^{\nu_R}_{\text{dec}} \ll M_{Z^{\prime}}$), with $s \ll M_{Z^{\prime}}$ and neglecting the fermion masses in the final state reads~\cite{Barger:2003zh}
 %
@@
 
-The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}.
-It follows that for small rartios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
+The results for $\Delta N_{\text{eff}}$ as a function of $M_{Z^{\prime}}/g^{\prime}$ are displayed in Fig.~\ref{fig:Neff}, where it can be observed that for small ratios $M_{Z'}/g'$  the variation in the number of relativistic degrees of freedom of the new species is large ($\Delta N_{\text{eff}}\gtrsim0.3$ corresponds to decoupling temperatures $T^{\nu_R}_{\text{dec}}\lesssim2$ GeV) and vice versa.
 % The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
-It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV.
+It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound at $2\sigma$ (solid gray line) demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV (these bounds become slightly weaker once the Planck+BAO+$H_0$ combination~\cite{Aghanim:2018eyx} is considered, but in such a case the BBN bound from the primordial abundances of light elements would rule~\cite{Pitrou:2018cgg}).
 %in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
-On the other hand, it is remarkable the fact the future CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} have the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
+In other words, bearing in mind that $M_{Z'}/g'=3v_S/2$ we have that the energy scale of the $\operatorname{U}(1)_{B-L}$ symmetry breaking must be at least $\sim26$ TeV.      
+On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
 %Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}

### 2019-09-20 draft.tex
Updates from Overleaf

@@
 }
-\date{\small September DD, 2019}
+\date{\small September 23, 2019}
 \begin{document}
@@
 \end{align}
+where the condition in the charged lepton Yukawa couplings have been used to fix $h$, and is automatically consistent with the conditions in the quark Yukawa couplings.
 By setting $l=0$ in the previous equations, we can define the Abelian symmetry in which only the right-handed charged fermions have non-vanishing $X$-charges as $\operatorname{U}(1)_R$.

### 2019-09-20 draft.tex
Updates from Overleaf

@@
 %in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
-In other words, bearing in mind that $M_{Z'}/g'=3v_S/2$ we have that the energy scale of the $\operatorname{U}(1)_{B-L}$ symmetry breaking must be at least $\sim26$ TeV.      
+In other words, bearing in mind that $M_{Z'}/g'=3v_S/2$ we have that the energy scale of the $\operatorname{U}(1)_{X}$ symmetry breaking must be at least $\sim26$ TeV.      
 On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
@@
 2017-16286, and by COLCIENCIAS through the Grant 111577657253. D.R
-would also like to thank the IIP-Natal, for its support,
+would also like to thank the IIP-UFRN, for its support,
 hospitality and the nice and stimulating atmosphere during the

### 2019-09-22 draft.tex
Updates from Overleaf

@@
 \begin{abstract}    
-  The radiative type-I seesaw have been already implemented to explain the lightness of Majorana neutrinos with both Majorana and Dirac heavy fermions, and the lightness of Dirac    neutrinos with                   Dirac heavy fermions.
+  The radiative type-I seesaw has been already implemented to explain the lightness of Majorana neutrinos with both Majorana and Dirac heavy fermions, and the lightness of Dirac    neutrinos with                   Dirac heavy fermions.
 In this work we present a minimal implementation of the radiative type-I seesaw with light Dirac neutrinos and heavy Majorana fermions.
@@
 A fermion vector-like extension of the model is also proposed where the light right-handed neutrinos can thermalize in the primordial plasma and the extra gauge boson can be directly produced at colliders.
-In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competitive with collider constraint for $g'$ sufficiently large in the ballpark of the SM values, while future cosmic microwave background experiments may probe all the no minimal models presented here.
+In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competitive with collider constraint for $g'$ sufficiently large in the ballpark of the Standard Model values, while future cosmic microwave background experiments may probe all the no minimal models presented here.
 \end{abstract}
@@
 symmetry with generation-independent charge assignments for the
-standard model fermions, $\operatorname{U}(1)_{X}$.
+SM fermions, $\operatorname{U}(1)_{X}$.
 % 
@@
 allow us to write the $X$-charges of the SM fields in terms
-of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc}, that we choose as
+of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc,Allanach:2018vjg}, that we choose as
 \begin{align}
@@
 On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
-%Prospect on $N_{\text{eff}}$~\cite{Abazajian:2019oqj}
+The same constraint would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}
 
@@
 \end{align}
-The full set of anomaly free standard model $X$-charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $r$, is just
+The full set of anomaly free SM $X$-charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc,Allanach:2018vjg} that we choose as $l$ and $r$, is just
 \begin{align}
@@
 
-If we now change $f\to f'= f/r$ for all the charged fermion $X$-charges, the
+If we now change $f\to f'= f/r$ for all the charged fermion $X$-charges~\cite{Allanach:2018vjg}, the
 first set of anomaly cancellation conditions Eq.~\eqref{eq:anolin} remains

### 2019-09-23 draft.tex
Updates from Overleaf

@@
 On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
-The same constraint would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}
+The same constraint would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}.
 

### 2019-09-25 draft.tex
Updates from Overleaf

@@
 
-% We will make use of the scotogenic model~\cite{Ma:2006km}. In
-% scotogenic model the neutrino masses and the DM have common
-% explanation. The neutrino masses are generated by one-loop effects,
-% where the candidates for DM are mediators in the loop.
-%Conclusion:
-
 The rest of the paper is organized as follows.
@@
 $\nu_{Rj}$ ($j=1,2$) and $\nu_{R3}$, and another set of three heavy Majorana fermions, $\psi_{R\alpha}$ ($\alpha=1,2,3$).  
-%The model also includes an additional $\operatorname{U}(1)_X$ gauge
-%symmetry which is used to forbid the Dirac and Majorana neutrino mass
-%terms at tree level.
-%Additionally, we add three right neutrinos, one scalar doublet, two scalar singlets and three Majorana fermion singlet under $\operatorname{SU}(2)_L$.
 The $\operatorname{U}(1)_{\mathcal{D}}$ charges for the new particles are defined by the anomaly cancellation conditions and the gauge invariance in Yukawa and scalar interactions.
-%In this model the neutrinos are Dirac fermions. Particle content and their respective charges are show in Tab.~\ref{tab:partcont}.
 
@@
 \end{align}
-%
-%
-%\begin{align*}
-%    \mathcal{V}(H, S, \eta, \sigma) = & \sum_{i} %V(\omega_i)+\sum_{i<j}|\omega_i|^2|\omega_j|^2+ \lambda_{7} (\eta^{\dagger} H ) %(H^{\dagger} \eta) +\lambda_{8} (\eta^{\dagger} H S^{*} \sigma + \text{h.c.})\,,
-%\end{align*}
-%
 with $V(\omega) = \mu^{2}_{\omega} \omega^{\dagger} \omega + \lambda_{\omega} (\omega^{\dagger} \omega)^{2}$.
@@
 Note that after the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the $\lambda_8$ term gives rise to the mixing between the neutral parts of $\eta$ and $\sigma$, which is mandatory to generate non-zero radiative masses.
-%Note that after the spontaneous symmetry breaking of $\operatorname{U}(1)_X$ the last term gives rise to the soft trilinear coupling
-%\begin{align}
-%  \mu=\lambda_8 \langle S \rangle\,,
-%\end{align}
 We assume $\lambda_8$ and $\langle S\rangle$ reals to preserve CP symmetry in the scalar sector, and $\mu^2_\eta,\mu^2_\sigma>0$ to avoid tree-level mixing terms among the fermions. 
 Moreover, we also assume $\lambda_1\ll1$  such that the scalar $S$ and $H$ do not mix allowing us to identify the CP even scalar particle in $H$ as the SM Higgs boson. 
-% \subsection{Scalar mass spectrum}
-%\label{sec:ScaMassSpect}
 To establish the scalar spectrum we expand the scalar fields as
@@
 with $v_H= 246.22$ GeV.  
-%By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
-%
-%\begin{align*}
-%    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  v^2 + \lambda_{1}  v_S\right)\,,  &
-%    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  v^{2}_{S} + \lambda_{1}  v^2\right)\,.
-%\end{align*}
-%
 Of the original twelve scalar degrees of freedom in the model, the gauge bosons $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorb four of them (the Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$).
 Thus, the scalar spectrum contains two sets of two neutral CP-even states ($h$ and $S_{R}$,  and $\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar states ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar ($\eta^{\pm}$).
-%We assume that $\lambda_{1} \ll 1$, such that the scalar $S$ and $H$ do not mix. 
 The mass spectrum for the unmixed scalars reads
@@
 
-%The other neutral mass eigenstates are defined as
-%
-%\begin{align*}
-%    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} %c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} %\begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
-%\end{align*}
-%
-%where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$, with $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} %\upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} %\upsilon^{2}_{S})$ and $c = \frac{1}{2}\lambda_8 v_{H} v_{S}$\,.
-%The corresponding mass eigenvalues are
-%\begin{align*}
-%   m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c^{2}} \right)\,, \\
-%     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c^{2}} \right)\,,
-%\end{align*}
-
 On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis in such a way their masses are $M_{\psi_\alpha}=\kappa_{\alpha\alpha}v_S/\sqrt{2}$, with $M_{\psi_1}<M_{\psi_2}<M_{\psi_3}$.
@@
 \end{align}
-%\begin{pmatrix}
-  %\psi_1 &
-  %\psi_2 &
-  %\psi_3
-%\end{pmatrix}^{\operatorname{T}}$$
 
@@
 %
-%Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac
 Neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
@@
 (\mathcal{M}_{\nu})_{ij} = \frac{1}{32 \pi^{2}}  \frac{\lambda_8 v_S v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} M_{\psi_\alpha} y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
-%(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} %{m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} %M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( %\frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( %\frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
 \end{align}
 %
-%check the following formula:
 where $F(x) =x \log x/(x-1)$. 
-%, $M_{\psi_{a}}$ is
-%the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
-%two CP-even (CP-odd) mass eigenstates.
-%It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 %v_S \neq 0$. 
 Note that the structure of the effective neutrino mass matrix, given by the
@@
 
-%The mass matrix for Dirac neutrinos is diagonalized by
-%\begin{align*}
-%(U^{\nu}_R)^{\dagger} \mathcal{M}_{\nu} U^{\nu}_L = \mathcal{M}_{\nu}^{\text{diag}} = %\text{diag}(m_1, m_2, m_3)\,,
-%\end{align*}
-%where $U^{(\nu)}_R$ and $U^{(\nu)}_L$ are the unitary $3 \times 3$
-%matrices associated to the right-handed and left-handed neutrino sectors. The leptonic %charged currents with non-massless neutrinos
-%are parametrized in terms of the unitary mass
-%\begin{align*}
-%U_{\text{PMNS}} = \left( U^{\ell}_L \right)^{\dagger} U^{\nu}_L\,,
-%\end{align*}
-%where is the left diagonalization matrix of the charged leptons.
-%As we already are in the diagonal basis after the calculation of the
-%one-loop neutrino masses, we can set
-%$U_{L}^{\ell} = \mathds{1}$. Moreover, we assume that $U_{R}^{\nu} = \mathds{1}$.
-%Therefore, we can express the Dirac neutrino mass matrix in the
-%following way
-%\begin{align}
-%(\mathcal{M}_{\nu})_{ij} = (U_{\text{PMNS}})_{ij} (\mathcal{M}_{\nu}^{\text{diag}})_{j}\,,
-%\end{align}
-%where the matrix $U_{\text{PMNS}}$ is expressed in the standard parameterization as
-%\begin{align*}
-%U_{\text{PMNS}} = \begin{pmatrix}
-%    1 & 0		& 0 \\
-%    0 & c_{23}  & s_{23} \\
-%    0 & -s_{23} & c_{23}
-%\end{pmatrix}
-%\begin{pmatrix}
-%    c_{13}  &  0 & s_{13}e^{-i\delta} \\
-%    0 		&  1 & 0 \\
-%    -s_{13}e^{i\delta} &  0 & c_{13}
-%\end{pmatrix}
-%\begin{pmatrix}
-%    c_{12}  & s_{12} & 0 \\
-%    -s_{12} & c_{12} & 0 \\
-%    0		& 0		 & 1
-%\end{pmatrix}\,,
-%\end{align*}
-%where $s_{ij} = \sin \theta_{ij}$ and $c_{ij} = \cos \theta_{ij}$ and $\theta_{ij}$ are %neutrino mixing angles and $\delta$ is CP-violating phase.
-
-%\section{Lepton flavor violation}
-%\label{sec:LFV}
-
 On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$ as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type.
@@
 
-%
-%which leads to a very slight requirement,
-
-%The most common search for CLFV focuses on the $l^{-}_{i} \to l^{-}_{j} \gamma$ process. This process is described by the effective Lagrangian
-%
-%\begin{align}
-%    \mathcal{L} = \frac{\mu_{m}^{\alpha \beta}}{2} l^{-}_{\beta} \sigma^{\mu \nu} l^{-}_{\alpha} F_{\mu \nu}
-%\end{align}
-%
-%where $\mu_{m}^{\alpha \beta}$ is a transition magnetic moment~\cite{Toma:2013zsa}.
-%The decay rate is given by~\cite{Lavoura:2003xp}
-%
-%\begin{align}
-% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
-%\end{align}
-%
-%where $t_{\alpha} = M^{2}_{\psi_{\alpha}}/M^{2}_{\eta^{-}}$ and
-%
-%\begin{align}
-%    K(t_{\alpha}) = \frac{2t_{\alpha}^{2}+5t_{\alpha}-1}{12(t_{\alpha}-1)^{3}} - %\frac{t_{\alpha}^{2}\log t_{\alpha}}{2(t_{\alpha}-1)^{4}}\,.
-%\end{align}
-%
-%If we assume that $t_{\alpha} \to 0$, $t_{\alpha} \to 1$ and $t_{\alpha} \to \infty$, we have that $K(t_{\alpha}) = 1/12$, $K(t_{\alpha}) = 1/24$ and $K(t_{\alpha}) = 1/(6t)$, respectively.
-
-%For $i \neq j$ we have CLFV processes, these processes are severely restricted by the current bounds , which set limits to the Yukawas.
-The most restrictive experimental bounds is decay $\mu \to e \gamma$, which is several orders of magnitude greater than radiative decays $\tau \to~l\gamma$, with $l = e, \mu$.
-These restrictions are given by Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn}, Br$(\tau \to e\gamma) $\textless$ 3.3 \times 10^{-8}$ and Br$(\tau \to~\mu\gamma) $\textless$ 4.4 \times 10^{-8}$~\cite{Aubert:2009ag, Bona:2007qt, Miyazaki:2012mx}.
-
-%In the limit $m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$, $t_{\alpha} \to 0$ the decay width reads
-%
-%\begin{align}
-% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} \left[ \frac{1}{12} \right] \right|^{2}\,, 
-%\end{align}
-%
-%using the current experimental constraint to Br$(\mu \to e\gamma)$, can be fullfilled provided
-%
-%\begin{align*}
-%    \left( \sum_{\alpha} \frac{h^{}_{i \alpha} h_{\alpha j}^{*}}{M^{2}_{\eta^{-}}} \right)^{2} \leq 5.7 \times 10^{-13} \frac{768 \pi G_{F}^{2}}{\alpha_{EM}}
-%\end{align*}
-%
-%which leads to a very slight requirement,
-%\begin{align*}
-%    \left| \sum_{\alpha}h^{}_{i \alpha} h_{\alpha j}^{*}\left(\frac{50\text{TeV}}{M^{2}_{\eta^{-}}} \right)^{2} \right| \leq 12.65
-%\end{align*}
-%
-%For $i = j$ we have processes that contribute to the leptonic magnetic dipole moment.
-In the case of the anomalous muon magnetic dipole moment, the experimental measurements does not agree with the values predicted by the SM~\cite{Lindner:2016bgg}.
-This can be a proof of the veracity of the model, in addition to giving restrictions on the Yukawas.
-
 \section{Dark matter}
@@
 
-%\subsection{Fermion dark matter}
 Since $\psi_{1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa couplings and $\operatorname{U}(1)_{\mathcal{D}}$ gauge interactions. 
@@
 where sizable $h_{i\alpha}$ are required to reproduce the correct DM abundance, which in turn leads to a mild tension with experimental upper bounds on the rates for rare charged lepton decays~\cite{Kubo:2006yx,Sierra:2008wj,Ibarra:2016dlb}.
-%The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
 On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couple to quarks and charged leptons
 (see~\cite{Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for phenomenological studies on $Z'$-mediated Majorana DM).
-% check Ibarra papers
-%also through the annihilation
-%$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via 
-%Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
-%CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
-%In the case where the mass of the other fermions and scalars is nearly
-%degenerated to $\psi_{1} $, the processes of coannihilation can be
-%relevant for the relic density calculation~\cite{Klasen:2013jpa}.
 
-%   Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.
-
-% In the case that the mass of the lightest fermion $\psi$ is smaller
-% than the mass of the scalars, the DM will be fermionic. For this DM it
-% is possible to have the following observable decay of the scalar
-% $\eta^{\pm} \to l^{\pm} \psi_{1}$, therefore, the other fermions decay
-% as $ \psi \to l^{\pm} l^{\mp} \psi_{1}$ and
-% $\psi \to l^{\pm} l^{\mp} \psi_{1,2} $, through $\eta^{\pm}$.
-
-%\subsection{Scalar dark matter}
 In contrast to fermion DM, the scalar DM candidate has additional interaction terms to the Yukawa and gauge interactions.
@@
 It follows that for negligible Yukawa and gauge interactions there are two DM mass regions that allow us to properly reproduce the relic abundance, one corresponds the Higgs funnel region and the second one demands masses above $100$ GeV~\cite{Kakizaki:2016dza}.
-
-%This corresponds to the simplified dark matter model of scalar singlet-doublet dark matter, which have been studied in detail in~\cite{Restrepo:2019soi}
-
-%When the lightest scalar  is mainly a scalar doublet, the phenomenology will be similar inert doublet model~\cite{Honorez:2010re}.
-For this kind of DM model  inert doublet model there are two mass regions for DM which can to reproduce adequately the relic density ($50$GeV \textless $m_{DM}$ \textless $70$GeV and $535$GeV \textless $m_{DM}$ \textless $20$TeV)~\cite{Garcia-Cely:2015khw}.
-
-% In recent studies, these two regions are connected through use of a
-% second doublet~\cite{Borah:2019aeq}. How we have in the model the
-% Yukawa coupling, the decay $\psi_{i} \to l^{\pm} \eta^{\mp}$ is
-% possible. In addition, decay is given via scalar interactions
-% $\eta^{\pm} \to \eta^{0} + {W^{\pm}}$, where $W^{\pm}$ can be real or
-% virtual and decay to leptons or quarks.
-
-%Now, if the lightest scalar is mainly a singlet, the DM will be similar to Singlet %Scalar Dark Matter Model~\cite{Athron:2017kgt}\todo{change for the original ref by Ma et al. etc}.
-%The mass range for the scalar singlet that produces the adequate relic
-%density is around the Higgs resonance and for masses above $1$TeV. For
-%this model~\cite{}, the relevant coupling for DM phenomenology is the
-%Higgs portal trough the Lagrangian term $\sigma^{2} H^{2}_{i}$.
-
-%This term generates interesting phenomenological consequences.
-%Such as, thermal production of DM in the early
-%universe~\cite{Yaguna:2008hd}, direct detection and invisible decay of
-%SM Higgs through $h \to \sigma \sigma$~\cite{Mambrini:2011ik}.
-%In addition, this model has important contributions for cosmology, in
-%phenomena such as inflation~\cite{Lerner:2009xg} and
-%baryogenesis~\cite{Cline:2012hg}.
 
@@
 allow us to write the $X$-charges of the SM fields in terms
-of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc,Allanach:2018vjg}, that we choose as
+of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc,Allanach:2018vjg,Das:2019pua}, that we choose as
 \begin{align}
@@
 
-%Note that if $r$ is a fraction with denominator $4$, let say $r=3/4$, 
-%The $\operatorname{U}(1)_{B-L}$ left out a remnant $Z_2$ discrete symmetry which guarantees the stability of the lightest odd-particle.
-
-%the charges for the SM particles are in equations~\ref{Eq:SMCharges}. Since these are determined by the anomaly cancellation equations.
-%For this operator we have that the charges for the new particles are given by
-%\begin{align}
-%    \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
-%\end{align}
-%As we are interested here in the case of the exotic set of X-charges charges:$\mp 4$,$\mp 4$,$\pm 5$, the charges for the model particles are shown in the table~\ref{tab:partcont3}.
-%Because the charges of the SM fermions are the same for both operators ($5d$ and $6d$), the $N_{eff}$ restrictions shown in the figure~\ref{fig:Neff} apply to both operators.
 %
@@
 
-% \footnote{Check 2r+2nu: -2,6,7,-9,-3  3r+2nu: -(5/2),7/2,-7,6,9/2}
-
 Accordingly, we may expect that 
@@
 contribute to the radiation energy density of the Universe, since now   the interaction between the $Z'$ with the SM fermions  opens up the possibility to thermalize them with the primordial plasma.
-%These new contributions can modify the cosmological observables in the cosmic microwave background (CMB). 
-%These new neutrinos contribute to the
-%existence of dark radiation, which affects the expansion processes of
-%the universe and the number of relativistic degrees of freedom for
-%neutrinos.
-%In the case of our model, the new gauge symmetry introduces  new gauge boson that mediates interaction of the right neutrinos and the SM. 
 In other words, this leads to a modification in the relativistic degrees of freedom as~\cite{Anchordoqui:2012qu,Anchordoqui:2011nh}
@@
 \begin{align}
-    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4},
+    \Delta N_{\text{eff}} = N_{\text{eff}} - N^{\text{SM}}_{\text{eff}} = N_{\nu_R} \left( \frac{T_{\nu_{R}}}{T_{\nu_{L}}} \right)^{4} = N_{\nu_R} \left( \frac{g(T^{\nu_{L}}_{\text{dec}})}{g(T^{\nu_{R}}_{\text{dec}})} \right)^{4/3},
 \end{align}
@@
 %
-%\begin{align*}
-%\Gamma(T^{\nu_R}_{\text{dec}}) = H(T^{\nu_R}_{\text{dec}})\,, 
-%\end{align*}
-%
-% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
-%
 with $H(T)= [4 \pi^{3} G_{N}(g(T) + 21/4)/45]^{1/2} T^{2}\,.$
-% \Gamma(l^{-}_{i} \to l^{-}_{j} \gamma) = \frac{m^{3}_{i}}{16 \pi} \left| \sum_{\alpha} h_{i \alpha} m_{i} h_{\alpha j} \frac{i e}{16 \pi M^{2}_{\eta^{-}}} K(t_{k}) \right|^{2}\,, 
-%
-%\begin{align*}
-%    H(T) = \sqrt{\frac{8 \pi G_{N} \rho(T)}{3}} = \sqrt{\frac{4 %\pi^{3} G_{N}}{45} \left( g(T) + \frac{21}{4} \right)} T^{2}\,,
-%\end{align*}
 %
 Note that the factor $21/4$ corresponds to the contribution of the right-handed neutrinos to the relativistic degrees of freedom.
-%By finding the decoupling temperature of the right neutrinos $T^{\nu_R}_{\text{dec}} $ by a root finding method, it is possible to calculate $\Delta N_{\text{eff}}$.
 
@@
 
-%\section{Collider constraints}
 Regarding collider searches, the recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{Aad:2019fac} was done
@@
 The green (upper) region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$ To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g^{\prime}$.
-In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa}\footnote{The constraint as function of the $X$-charge $h=-1-l$ is given in Ref.~\cite{Okada:2016tci}.
+In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{Carena:2004xs,Heeck:2014zfa,Das:2015nwk}\footnote{The constraint as function of the $X$-charge $h=-1-l$ is given in Ref.~\cite{Okada:2016tci}.
 }

### 2019-09-26 draft.tex
Updates from Overleaf

@@
 \usepackage[colorinlistoftodos]{todonotes}
-
+\usepackage{fontawesome}
 \usepackage{comment}
@@
 In particular, the  current upper bound on $\Delta N_{\text{eff}}$ reported by PLANCK points to large ratios $M_{Z'}/g'\gtrsim 40\ \text{TeV}$ which can be competitive with collider constraint for $g'$ sufficiently large in the ballpark of the Standard Model values, while future cosmic microwave background experiments may probe all the no minimal models presented here.
+\href{https://github.com/restrepo/DiracMajorana}{\faGithub}
 \end{abstract}
@@
 %
-where $N_{\nu_R}$ is the number of right-handed neutrinos with the same $X$ charge and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Aghanim:2018eyx}.
+where $N_{\nu_R}$ is the number of right-handed neutrinos with the same $X$ charge and $g(T)$ is the number of relativistic degrees of freedom at a temperature $T$ in the SM~\cite{Borsanyi:2016ksw}.
 The decoupling temperature of the SM neutrinos is $ T^{\nu_{L}}_{\text{dec}} \approx 2.3 $ MeV, when $g(T^{\nu_{L}}_{ \text{dec}}) = 43/4$ corresponding to the three $\nu_{L}$, $e^{\pm} $ and the photon~\cite{Kolb:1990vq,Enqvist:1991gx}.
@@
 For comparison purposes  the upper bound at $2\sigma$ (black line) obtained from the BBN analysis~\cite{Pitrou:2018cgg} is also shown.
-The horizontal dashed lines show the projected sensitivity of the future experiments SPT-3G/SO~\cite{Benson:2014qhw} and CMB-S4~\cite{Abitbol:2019nhf}.
+The horizontal dashed lines show the projected sensitivity of the future experiments SPT-3G/SO~\cite{Benson:2014qhw,Ade:2018sbj} and CMB-S4~\cite{Abitbol:2019nhf}.
 $\Delta N_{\text{eff}}=0.4$ represents the extra contribution  required to relieve the tension on the inferred $H_0$ values from  high- and low-redshift observations \cite{Bernal:2016gxb,Mortsell:2018mfj}.
@@
 % The bound that come from Planck~\cite{Aghanim:2018eyx} is stronger than the bound of LEP~\cite{Heeck:2014zfa}. and even LHC, see below
-It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound at $2\sigma$ (solid gray line) demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 40$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV (these bounds become slightly weaker once the Planck+BAO+$H_0$ combination~\cite{Aghanim:2018eyx} is considered, but in such a case the BBN bound from the primordial abundances of light elements would rule~\cite{Pitrou:2018cgg}).
+It follows that for the $\operatorname{U}(1)_{G}$ model the Planck+BAO upper bound at $2\sigma$ (solid gray line) demands that $M_{Z^{\prime}}/g^{\prime} \gtrsim 36$ TeV while for the $\operatorname{U}(1)_{R}$ model a more stringent lower bound applies $M_{Z^{\prime}}/g^{\prime} \gtrsim 60$ TeV (these bounds become slightly weaker once the Planck+BAO+$H_0$ combination~\cite{Aghanim:2018eyx} is considered, but in such a case the BBN bound from the primordial abundances of light elements would rule~\cite{Pitrou:2018cgg}).
 %in order to satisfy the conditions of $N_{\text{eff}}$ for all the symmetries studied here.
-In other words, bearing in mind that $M_{Z'}/g'=3v_S/2$ we have that the energy scale of the $\operatorname{U}(1)_{X}$ symmetry breaking must be at least $\sim26$ TeV.      
-On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Abazajian:2019oqj}.
-The same constraint would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}.
+In other words, bearing in mind that $M_{Z'}/g'\approx 3v_S/2$\footnote{Because of the LEP constraint (see below) the mixing between the $Z'$ and the SM $Z$ boson is negligible~\cite{Carena:2004xs}.} we have that the energy scale of the $\operatorname{U}(1)_{X}$ symmetry breaking must be at least $\sim24$ TeV
+(note that the  $\operatorname{U}(1)_X$ having the lowest  $M_{Z'}/g'$ ratio features a X charge $l=-6/11\approx-1/2$). 
+Similar constraints would apply to all gauged and anomaly free  $\operatorname{U}(1)_X$ extensions of the SM with Dirac neutrino masses, where light right handed neutrinos are associated  to the solution $(-4,-4,+5)$~\cite{Ma:2014qra,Ma:2015mjd,Ma:2015raa,Bonilla:2018ynb,Calle:2018ovc,Bonilla:2019hfb}.
+On the other hand, it is remarkable the fact the next generation of CMB experiments~\cite{Benson:2014qhw,Ade:2018sbj,Abitbol:2019nhf} has the potential to entirely probe all the not-so minimal models~\cite{Baumann:2017gkg,Abazajian:2019oqj}.
 
@@
 \begin{align}
-  X=R-l\, Y\,.
+  X(l)=R-l\, Y\,.
 \end{align}

### 2019-10-07 draft.tex
Updates from Overleaf

@@
 \appendix
-\section{$\operatorname{U}(1)_X$ anomaly cancellation }
+\section{$\operatorname{U}(1)_X$ anomaly cancellation}
+
 We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$).
